---
title: "Process OLIS spectral data and Jaz data; create final PUR/PAR ratio and pigments plot"
author: "Douglas A. Campbell, Sylwia Sliwinska-Wilczewska"
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
---

```{r setup, include = FALSE}
# knitr::opts_chunk$set(echo = TRUE, message = FALSE)
# knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "CleanData")
DataIn <- file.path("..", "Data", "ProcessedData", fsep = .Platform$file.sep)

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

```{r load libraries} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggspectra)
library(ggpubr)
library(caret)
library(photobiologyWavebands)
library(reshape2)
library(photobiology)
library(gcookbook)
library(RColorBrewer)
library(viridis)
library(scales)
```

```{r Exported Rmd only first time in session}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```
```{r Read processed Olis and jaz file}
OLISSpectraMetaAllPURFile <- "../Data/ProcessedData/Baltic_Photoperiod_Processed_OlisSpectraAll.Rds"
OLISSpectraMetaAllPURFileName <- str_split(string = OLISSpectraMetaAllPURFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
OLISSpectraMetaAllPUR <- readRDS(OLISSpectraMetaAllPURFile)  %>%
  ungroup()
```

```{r Clean df, without absorbance and all nm - smaller df}
OLISAllPURShort<-OLISSpectraMetaAllPUR %>% 
  select(-c(Absorbance, nm, Abs440, AbsNorm440, EmJaz439, EmNormJaz439, PURNorm, CountsMean, SumAbNorm, PURNormSum, SumEmNormJaz439)) %>% 
  unique()

OLISAllPURShort<-OLISAllPURShort %>% 
  
  group_by(Strain, Par_ue, Photoperiod, E_days, MC, Run) %>%
  mutate(PURPARRatio = PUR/Par_ue) %>% 
ungroup()

OLISAllPURShort <- OLISAllPURShort %>% 
  mutate(E_hours = E_days*24) 
  
OLISAllPURShort <- OLISAllPURShort %>% 
  filter(PURPARRatio<=1) %>% 
  filter(PURPARRatio>0)
```

```{r Create facets for plot}
OLISAllPURShort <- OLISAllPURShort %>%
      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))

OLISAllPURShort$facetsPar_ue = factor(OLISAllPURShort$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
OLISAllPURShort$facetsPhotoperiod = factor(OLISAllPURShort$WL, labels = c("Photoperiod~(h)"))
OLISAllPURShort$facetsStrain = factor(OLISAllPURShort$WL, labels = c("Strain"))
OLISAllPURShort$facetsPhase = factor(OLISAllPURShort$WL, labels = c("Phase~of~growth"))
```


PUR/PAR ratio - photoperiod and PAR
```{r fig.height = 8, fig.width = 8}


lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))

lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

Plot <- OLISAllPURShort %>%
  ggplot() +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  # geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  # ggh4x::facet_nested(cols = vars(facets2, Photoperiod), rows = vars(facets, Par_ue), labeller = labeller(Photoperiod = Photoperiod.labs,  Strain = label_value, Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs)) +
  theme_bw() 
Plot


```

Load tmaxAG
```{r}
gs4_deauth()

tmaxAG<- read_sheet("https://docs.google.com/spreadsheets/d/1WyB4jonJGW9uFzKHp1Z6DnkMv-CP1PerwQ6sSLK7O8I/edit#gid=0")

as.data.frame(tmaxAG)
tmaxAG <- tmaxAG

tmaxAG<-tmaxAG %>% 

  mutate(Par_ue = as.numeric(Par_ue)) %>%
  mutate(Photoperiod = as.numeric(Photoperiod)) %>%
  mutate(dayRound_tmaxAG = as.numeric(dayRound_tmaxAG)) %>%
  mutate(hRound_tmaxAG = as.numeric(hRound_tmaxAG)) %>% 
  mutate(day_tmaxAG = as.numeric(day_tmaxAG)) %>% 
  mutate(h_tmaxAG = as.numeric(h_tmaxAG)) %>%

  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))

```
Combine OLISAllPURShort with tmaxAG data from google sheet

OLISAllPURShortPhase -> Divided PAR, PUR and PUR/PAR Ratio data to Exponential and Pre-stationary phase according to tmaxAG from google sheet
```{r}
OLISAllPURShortPhase <- OLISAllPURShort %>%
  left_join(., tmaxAG, by = c("Strain"="Strain","Par_ue"="Par_ue","Photoperiod"="Photoperiod")) 

OLISAllPURShortPhase <- OLISAllPURShortPhase %>%
  mutate(Phase = O2) %>% 
  mutate(Phase=case_when(E_days<=dayRound_tmaxAG~"Exponential",
         E_days>dayRound_tmaxAG~"Pre-stationary"))
```


Plot -> PUR/PAR ratio - photoperiod and PAR or PAR PhotonDose
```{r fig.height = 8, fig.width = 8}

lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

OLISAllPURShortPhase %>%
  filter(PURPARRatio<=1) %>%
  filter(PARPhotonDose == 432000|
  PARPhotonDose == 864000|
  PARPhotonDose == 1944000|
  PARPhotonDose == 3888000|
  PARPhotonDose == 6480000|
  PARPhotonDose == 8640000|
  PARPhotonDose == 77760000) %>%
  ggplot() +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  # geom_vline(data = data_vline5, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline6, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline7, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline8, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.5)) +
  ggh4x::facet_nested(cols = vars(PARPhotonDose), labeller = label_parsed) +
  theme_bw() 
```


df for choosen PAR photondose data
```{r}

# data_vline5 <- data.frame(PARPhotonDose= c(432000, 1944000, 3888000, 6480000, 864000, 8640000, 77760000),facets3=c("PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})"), value = c(347, 245.39,189.48,162.62, 347, 111.56,110))
# 
# 
# data_vline6 <- data.frame(PARPhotonDose= c(432000, 1944000, 3888000, 6480000, 864000, 8640000, 77760000),facets3=c("PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})"), value = c(346, 216.33,163.44,136.03, 299.38,111.28,94.23))
# 
# data_vline7 <- data.frame(PARPhotonDose= c(432000, 1944000, 3888000, 6480000, 864000, 8640000, 77760000),facets3=c("PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})"), value = c(345, 296.45,217.80,191.03, 345,112.75,79.66))
# 
# data_vline8 <- data.frame(PARPhotonDose= c(432000, 1944000, 3888000, 6480000, 864000, 8640000, 77760000),facets3=c("PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})","PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})"), value = c(344, 244.38,190.39,163.62, 299.57, 112.29, 107))

```




#Growth rate

MultiCulti Assesment
```{r}
Project <- "PicoBaltic"
DataIn <- file.path("..","GrowthAssessData", fsep = .Platform$file.sep)
FileEncode <- "UTF-8" 
Delimiter <- ","
HeaderRows <- 0
```


MultiCulti Assesment
Exported only first time in session
```{r}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

GrowthAssessData/PICO_MultiAssesment_CCA contain WWPhotoperiod data!!! Genius - fix this Sylwia!!!!

MultiCulti Assesment
```{r read ProcessFile}
MultiCultiGrowthFile <- "../GrowthAssessData/PicoBaltic_MultiAssesment_CCA.Rds"

MultiCultiGrowthFileName <- str_split(string = MultiCultiGrowthFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 

MultiCultiGrowth <- readRDS(MultiCultiGrowthFile)  %>%
  ungroup()


MultiCultiGrowth121File <- "../GrowthAssessData/PicoBaltic_MultiAssesment_RUN121trunc.Rds"

MultiCultiGrowth121FileName <- str_split(string = MultiCultiGrowth121File, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 

MultiCultiGrowth121 <- readRDS(MultiCultiGrowth121File)  %>%
  ungroup()

#colnames(MultiCultiData)


```

clean MultiCulti data for WWPhotoperiod manuscript

Because I have a few growth data as replica I made mean to get one value of deltaOD_Lmu_corr
```{r}
MultiCultiGrowthClean <- MultiCultiGrowth %>%
  summarize(Filename, Run, ID, Strain, MC, Tube, Par_ue, Photoperiod, O2, WL, InnocDate, ExpDate, LightShape, OD720_Lmu_corr, deltaOD_Lmu_corr, OD720_LseGrowthFlag, deltaOD_LseGrowthFlag, GrowthAmpOD720Flag_14days, GrowthAmpdeltaODFlag_14days, OD720_Lmu_se, deltaOD_Lmu_se)

MultiCultiGrowthClean <- MultiCultiGrowthClean %>%
  filter(WL == "WW") %>% 
  #filter(Par_ue != 600) %>% 
  filter(O2 == 21) %>% 
  filter(Strain == "BA127R" | Strain == "BA48R" | Strain == "BA56G" | Strain == "BA77G") %>% 
  filter(Run != "61") %>% 
  filter(MC!= "MCMIX004" | MC!= "MCMIX006")
#OD720_Lmu_se, deltaOD_Lmu_se


MultiCultiGrowth121Clean <- MultiCultiGrowth121 %>%
  summarize(Filename, Run, ID, Strain, MC, Tube, Par_ue, Photoperiod, O2, WL, InnocDate, ExpDate, LightShape, OD720_Lmu_corr, deltaOD_Lmu_corr, OD720_LseGrowthFlag, deltaOD_LseGrowthFlag, GrowthAmpOD720Flag_14days, GrowthAmpdeltaODFlag_14days, OD720_Lmu_se, deltaOD_Lmu_se)

MultiCultiGrowthAll<-rbind(MultiCultiGrowthClean, MultiCultiGrowth121Clean)

MultiCultiGrowthAll<-MultiCultiGrowthAll %>% 
  group_by(Strain,Photoperiod,Par_ue) %>% 
    summarize(Filename, Run, ID, Strain, MC, Tube, Par_ue, Photoperiod, O2, WL, InnocDate, ExpDate, LightShape, OD720_Lmu_corr, deltaOD_Lmu_corr, OD720_LseGrowthFlag, deltaOD_LseGrowthFlag, GrowthAmpOD720Flag_14days, GrowthAmpdeltaODFlag_14days, OD720_Lmu_se, deltaOD_Lmu_se,
              meandeltaOD_Lmu_corr=mean(deltaOD_Lmu_corr),
              sddeltaOD_Lmu_corr=sd(deltaOD_Lmu_corr)) %>% 
  ungroup()


rm(MultiCultiGrowthClean, MultiCultiGrowth121Clean)
```

Add PAR PhotonDose and correct name of strains
```{r}

MultiCultiGrowthAll<-MultiCultiGrowthAll %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))

  MultiCultiDataCleanAll1 <- MultiCultiGrowthAll %>%
  filter(Photoperiod != "24") %>% 
  mutate(PARPhotonDose =(Par_ue/2)*Photoperiod*3600)
  
  MultiCultiDataCleanAll2 <- MultiCultiGrowthAll %>%
  filter(Photoperiod == "24") %>% 
  mutate(PARPhotonDose = Par_ue*Photoperiod*3600) 
  
  MultiCultiGrowthAll <-rbind(MultiCultiDataCleanAll1, MultiCultiDataCleanAll2)
  rm(MultiCultiDataCleanAll1, MultiCultiDataCleanAll2)
  
```


Combine growth rate and all PUR
```{r}
#colnames(OLISSpectraMetaAllPURPARRatioCleanExpPUR)

#All PUR (divided to Phase) and growth rate
MultiCultiGrowthRate <- OLISAllPURShortPhase %>% 
  left_join(., MultiCultiGrowthAll, by = c("Run" = "Run", "ID" = "ID","Strain" = "Strain", "Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod",  "O2" = "O2", "WL" = "WL",  "MC" = "MC", "Tube" = "Tube", "InnocDate" =  "InnocDate", "ExpDate" = "ExpDate", "LightShape" = "LightShape", "PARPhotonDose" = "PARPhotonDose")) 


```



Combine growth rate and exp PUR
```{r}
MultiCultiDataCleanGrowthAll2<-MultiCultiGrowthRate 
  
O1 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 30 | Par_ue == 300 | Par_ue == 90 | Par_ue == 180) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days < 4)

O2 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 4)

O3 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 6)

O4 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 12)

O5 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 900 | Par_ue == 600) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 4)

O6 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days == 12| E_days == 13)
  
O7 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days == 12 | E_days ==13)

O8 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 8 | E_days ==9)

O9 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PC-rich_056") %>% 
  filter(E_days == 11)

O10 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 180) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days == 8 | E_days == 9)

O11 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 180) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days == 6 | E_days == 7)

O12 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 8) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 6 | E_days ==7)

O13 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 8) %>% 
  filter(Strain == "PC-rich_056") %>% 
  filter(E_days == 9)

O14 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 4 | E_days ==5)

O15 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PC-rich_056") %>%  
  filter(E_days == 7)

O16 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12)

O17 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 900 | Par_ue == 600) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_hours < 100 & E_hours > 48)

MultiCultiDataCleanGrowthAll3 <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10, O11, O12, O13, O14, O15, O16, O17)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10, O11, O12, O13, O14, O15, O16, O17)

  
```

Because I have replica in growt rate - I combine one choosen PUR exp to all growth rate data
```{r}
#colnames(MultiCultiDataCleanGrowthAll4)
MultiCultiDataCleanGrowthAll4<-MultiCultiDataCleanGrowthAll3 %>% 
  mutate(PURExp = PUR) %>% 
  mutate(PURPhotonDoseExp = PURPhotonDose) %>% 
  mutate(PURPARRatioExp = PURPARRatio) %>% 
  mutate(E_hoursExp = E_hours) %>% 
  mutate(E_daysExp = E_days) %>% 
  select(c(Strain, Par_ue, Photoperiod, PURExp, PURPhotonDoseExp, PURPARRatioExp, E_hoursExp, E_daysExp))
  
MultiCultiGrowthRatePURExp <- MultiCultiGrowthRate %>%
  full_join(., MultiCultiDataCleanGrowthAll4, by = c("Strain"="Strain", "Par_ue"="Par_ue","Photoperiod"="Photoperiod"))


```



PUR/PAR ratio - all data and only exp
```{r fig.height = 8, fig.width = 8}


lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))

Plot <- MultiCultiGrowthRatePURExp %>%
  filter(Par_ue!=600) %>% 
  ggplot() +
  # geom_smooth(aes(x = Time_h, y = PURPARRatio, colour = as.factor(Strain)),  alpha = 0, size = 0.2, linetype = "solid", show.legend = T) +
  geom_point(aes(x = E_hoursExp, y = PURPARRatioExp, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  # geom_errorbar(aes(x = Photoperiod, ymin = OD720_Lmu_corr - OD720_Lmu_se, ymax = OD720_Lmu_corr + OD720_Lmu_se), size = 0.3, width=3, color = '#3C3B53', data = . %>% filter(GrowthAmpOD720Flag_14days  == 1)) +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot





lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))

Plot <- MultiCultiGrowthRatePURExp %>%
  filter(Par_ue!=600) %>% 
  filter(PURPARRatio>0.05) %>% 
  ggplot() +
  # geom_smooth(aes(x = Time_h, y = PURPARRatio, colour = as.factor(Strain)),  alpha = 0, size = 0.2, linetype = "solid", show.legend = T) +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  # geom_errorbar(aes(x = Photoperiod, ymin = OD720_Lmu_corr - OD720_Lmu_se, ymax = OD720_Lmu_corr + OD720_Lmu_se), size = 0.3, width=3, color = '#3C3B53', data = . %>% filter(GrowthAmpOD720Flag_14days  == 1)) +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  # ggh4x::facet_nested(cols = vars(facets2, Photoperiod), rows = vars(facets, Par_ue), labeller = labeller(Photoperiod = Photoperiod.labs,  Strain = label_value, Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs)) +
  theme_bw() 
Plot


```


```{r fig.height = 5.5, fig.width = 8, warning = FALSE}

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))


O2.labs <- c("Strain")
names(O2.labs) <- c(21)
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

Plot <- MultiCultiGrowthRatePURExp %>%
  filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PARPhotonDose, y = deltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # labs(shape="Photoperiod (h)", colour="Strain") +
   geom_errorbar(aes(x = PARPhotonDose, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  #geom_text(data=data_textA, aes(x=78000000, y=0.25, label=label), size=5) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), labeller = labeller(O2 = O2.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw() 
Plot



Plot <- MultiCultiGrowthRate %>%
  filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDose, y = deltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "PUR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # labs(shape="Photoperiod (h)", colour="Strain") +
   geom_errorbar(aes(x = PURPhotonDose, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), labeller = labeller(O2 = O2.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw() 
Plot

Plot <- MultiCultiGrowthRatePURExp %>%
  filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDoseExp, y = deltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "PUR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # labs(shape="Photoperiod (h)", colour="Strain") +
   geom_errorbar(aes(x = PURPhotonDoseExp, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), labeller = labeller(O2 = O2.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw()
Plot

Plot <- MultiCultiGrowthRatePURExp %>%
  #filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDoseExp, y = meandeltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "PUR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # labs(shape="Photoperiod (h)", colour="Strain") +
   geom_errorbar(aes(x = PURPhotonDoseExp, ymin = meandeltaOD_Lmu_corr - sddeltaOD_Lmu_corr, ymax = meandeltaOD_Lmu_corr + sddeltaOD_Lmu_corr), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), labeller = labeller(O2 = O2.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw()
Plot



```



Added column PhotonDose_value and combine data to to PAR and PUR - long format (MultiCultiGrowthRatePURExpFit)
```{r}
MultiCultiGrowthRatePURExpFitPAR<-MultiCultiGrowthRatePURExp %>% 
  select(-c(PURPhotonDose)) %>% 
  mutate(PhotonDose_value = PARPhotonDose) %>% 
  mutate(PhotonDose = O2) %>% 
  mutate(PhotonDose = case_when(PhotonDose==21~"PAR")) %>% 
  select(-c(PARPhotonDose, PURPhotonDoseExp))
  
MultiCultiGrowthRatePURExpFitPUR<-MultiCultiGrowthRatePURExp %>% 
  select(-c(PARPhotonDose)) %>% 
  mutate(PhotonDose_value = PURPhotonDoseExp) %>% 
  mutate(PhotonDose = O2) %>% 
  mutate(PhotonDose = case_when(PhotonDose==21~"PUR")) %>% 
  select(-c(PURPhotonDose, PURPhotonDoseExp))

MultiCultiGrowthRatePURExpFit<-rbind(MultiCultiGrowthRatePURExpFitPAR, MultiCultiGrowthRatePURExpFitPUR)
rm(MultiCultiGrowthRatePURExpFitPAR, MultiCultiGrowthRatePURExpFitPUR)

```


```{r fig.height = 8, fig.width = 8, warning = FALSE}

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))


O2.labs <- c("Strain")
names(O2.labs) <- c(21)
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

Plot <- MultiCultiGrowthRatePURExpFit %>%
  filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PhotonDose_value, y = deltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
   # geom_errorbar(aes(x = PARPhotonDose, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(PhotonDose), labeller = labeller(O2 = O2.labs)) +
    # ggh4x::facet_nested(cols = vars(Strain), labeller = labeller(Photoperiod = Photoperiod.labs,  Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs, Strain = Strain.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12, angle = 45, vjust = 1, hjust = 1),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.91,0.88),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        # legend.spacing.x = unit(0.01, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=9))
Plot


Plot <- MultiCultiGrowthRatePURExpFit %>%
  #filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PhotonDose_value, y = meandeltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
   # geom_errorbar(aes(x = PARPhotonDose, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(PhotonDose), labeller = labeller(O2 = O2.labs)) +
    # ggh4x::facet_nested(cols = vars(Strain), labeller = labeller(Photoperiod = Photoperiod.labs,  Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs, Strain = Strain.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12, angle = 45, vjust = 1, hjust = 1),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.91,0.88),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        # legend.spacing.x = unit(0.01, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=9))
Plot

```

FIT curve

```{r test inhibition plot}

#Harrison & Platt, 1986
grcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}

```



Harrison & Platt, 1986 
```{r platt fit}

CleanGrowthPARPURfit <- MultiCultiGrowthRatePURExpFit |>   
  filter(Par_ue !=900 & Par_ue !=600) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth <- CleanGrowthPARPURfit |>
  unnest(GRCplatt_Predict)

```


Harrison & Platt, 1986 
```{r platt fit}


CleanGrowthPARPURfit900 <- MultiCultiGrowthRatePURExpFit |>   
  filter(Par_ue !=30 & Par_ue !=90 & Par_ue !=180 & Par_ue !=300) |> 
  # filter(Par_ue == 900) |>
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth900 <- CleanGrowthPARPURfit900 |>
  unnest(GRCplatt_Predict)

```


add columns to get nice facet
```{r}

GRCplatt_PredictGrowth$facetsStrain = factor(GRCplatt_PredictGrowth$PhotonDose, labels = c("Strain", "Strain"))

GRCplatt_PredictGrowth900$facetsStrain = factor(GRCplatt_PredictGrowth900$PhotonDose, labels = c("Strain", "Strain"))

```


```{r}
# CleanGrowthPARPURfitbez900 <- CleanGrowthPARPUR %>%    
#   filter(Par_ue !=900) 
# 
# CleanGrowthPARPURfittylko900 <- CleanGrowthPARPUR %>%    
#   filter(Par_ue ==900) %>% 
#   filter(deltaOD_Lmu_se<8.057558e-03)
```



```{r fig.height = 8, fig.width = 8, warning = FALSE}

# O2.labs <- c("Strain")
# names(O2.labs) <- c(21)

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


ggplot(MultiCultiGrowthRatePURExpFit, aes(PhotonDose_value, meandeltaOD_Lmu_corr)) +
  geom_point(aes(PhotonDose_value, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
# 
#   geom_errorbar(aes(x = PhotonDose_value, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Par_ue)), width=4000000, data = . %>% filter(deltaOD_Lmu_se<8.057558e-03), show.legend = F) +
  geom_line(aes(PhotonDose_value, .fitted), show.legend = F, GRCplatt_PredictGrowth) +
  geom_line(aes(PhotonDose_value, .fitted), show.legend = F, GRCplatt_PredictGrowth900) +
  scale_y_continuous(breaks=seq(0, 0.25, by = 0.1)) +
  coord_cartesian(ylim = c(0, 0.25)) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "600", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  #geom_hline(aes(yintercept = 0), linetype = 2) +
    ggh4x::facet_nested(cols = vars(PhotonDose), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  #ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(PhotonDose), labeller = labeller(O2 = O2.labs)) +
  # ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Photoperiod), labeller = labeller(Photoperiod = Photoperiod.labs,  Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs)) +
  theme_bw() 

```


Fit for every Par_ue

Harrison & Platt, 1986 
```{r platt fit}

#Harrison & Platt, 1986
grcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}

MultiCultiGrowthRatePURExpFitok<-MultiCultiGrowthRatePURExpFit %>% 
  #filter(deltaOD_Lmu_corr<0.21) %>% 
  filter(Par_ue !=600)

MultiCultiGrowthRatePURExpFit30 <- MultiCultiGrowthRatePURExpFitok |>   
  filter(Par_ue ==30) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth30 <- MultiCultiGrowthRatePURExpFit30 |>
  unnest(GRCplatt_Predict)




MultiCultiGrowthRatePURExpFit90 <- MultiCultiGrowthRatePURExpFitok |>   
  filter(Par_ue ==90) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth90 <- MultiCultiGrowthRatePURExpFit90 |>
  unnest(GRCplatt_Predict)


MultiCultiGrowthRatePURExpFit180 <- MultiCultiGrowthRatePURExpFitok |>   
  filter(Par_ue ==180) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth180 <- MultiCultiGrowthRatePURExpFit180 |>
  unnest(GRCplatt_Predict)



MultiCultiGrowthRatePURExpFit300 <- MultiCultiGrowthRatePURExpFitok |>   
  filter(Par_ue ==300) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth300 <- MultiCultiGrowthRatePURExpFit300 |>
  unnest(GRCplatt_Predict)


MultiCultiGrowthRatePURExpFit900 <- MultiCultiGrowthRatePURExpFitok |>   
  filter(Par_ue ==900) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth900 <- MultiCultiGrowthRatePURExpFit900 |>
  unnest(GRCplatt_Predict)


```


add columns to get nice facet
```{r}

GRCplatt_PredictGrowth30$facetsStrain = factor(GRCplatt_PredictGrowth30$PhotonDose, labels = c("Strain", "Strain"))
GRCplatt_PredictGrowth90$facetsStrain = factor(GRCplatt_PredictGrowth90$PhotonDose, labels = c("Strain", "Strain"))
GRCplatt_PredictGrowth180$facetsStrain = factor(GRCplatt_PredictGrowth180$PhotonDose, labels = c("Strain", "Strain"))
GRCplatt_PredictGrowth300$facetsStrain = factor(GRCplatt_PredictGrowth300$PhotonDose, labels = c("Strain", "Strain"))
GRCplatt_PredictGrowth900$facetsStrain = factor(GRCplatt_PredictGrowth900$PhotonDose, labels = c("Strain", "Strain"))
```


Nice plot
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# O2.labs <- c("Strain")
# names(O2.labs) <- c(21)

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


ggplot(MultiCultiGrowthRatePURExpFitok, aes(PhotonDose_value, deltaOD_Lmu_corr)) +
  geom_point(aes(PhotonDose_value, deltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
# 
#   geom_errorbar(aes(x = PhotonDose_value, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Par_ue)), width=4000000, data = . %>% filter(deltaOD_Lmu_se<8.057558e-03), show.legend = F) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "darkslategray", show.legend = F, GRCplatt_PredictGrowth30) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "lightblue4", show.legend = F, GRCplatt_PredictGrowth90) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "hotpink4", show.legend = F, GRCplatt_PredictGrowth180) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "indianred3", show.legend = F, GRCplatt_PredictGrowth300) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "orange1", show.legend = F, GRCplatt_PredictGrowth900) +
  scale_y_continuous(breaks=seq(0, 0.25, by = 0.1)) +
  coord_cartesian(ylim = c(0, 0.25)) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  #geom_hline(aes(yintercept = 0), linetype = 2) +
    ggh4x::facet_nested(cols = vars(PhotonDose), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  #ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(PhotonDose), labeller = labeller(O2 = O2.labs)) +
  # ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Photoperiod), labeller = labeller(Photoperiod = Photoperiod.labs,  Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12, angle = 45, vjust = 1, hjust = 1),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.92,0.88),
        #legend.position = c(0.06,0.85),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.15, "cm"),
        # legend.spacing.x = unit(0.01, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=10))



ggplot(MultiCultiGrowthRatePURExpFitok, aes(PhotonDose_value, meandeltaOD_Lmu_corr)) +
  geom_point(aes(PhotonDose_value, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
# 
#   geom_errorbar(aes(x = PhotonDose_value, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Par_ue)), width=4000000, data = . %>% filter(deltaOD_Lmu_se<8.057558e-03), show.legend = F) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "darkslategray", show.legend = F, GRCplatt_PredictGrowth30) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "lightblue4", show.legend = F, GRCplatt_PredictGrowth90) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "hotpink4", show.legend = F, GRCplatt_PredictGrowth180) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "indianred3", show.legend = F, GRCplatt_PredictGrowth300) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "orange1", show.legend = F, GRCplatt_PredictGrowth900) +
  scale_y_continuous(breaks=seq(0, 0.25, by = 0.1)) +
  coord_cartesian(ylim = c(0, 0.25)) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  #geom_hline(aes(yintercept = 0), linetype = 2) +
    ggh4x::facet_nested(cols = vars(PhotonDose), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  #ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(PhotonDose), labeller = labeller(O2 = O2.labs)) +
  # ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Photoperiod), labeller = labeller(Photoperiod = Photoperiod.labs,  Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12, angle = 45, vjust = 1, hjust = 1),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.92,0.88),
        #legend.position = c(0.06,0.85),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.15, "cm"),
        # legend.spacing.x = unit(0.01, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=10))

```

```{r}
rm(MultiCultiGrowthRatePURExpFit30, MultiCultiGrowthRatePURExpFit90, MultiCultiGrowthRatePURExpFit180, MultiCultiGrowthRatePURExpFit300, MultiCultiGrowthRatePURExpFit900)
```




PIGMENTS

There are a few negative value of pigments (based on correlation) - I replaced them by 0

Growth file
```{r}
Project <- "PicoBaltic"
DataIn <- file.path("..", "ImportedData", "SySlmanuscriptWWPhotoperiod", fsep = .Platform$file.sep)
FileEncode <- "UTF-8"
Delimiter <- ","
HeaderRows <- 0
```

Growth file
Exported Rmd only first time in session
```{r}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

Growth file
```{r read ProcessFile}

#contained mean OD per day from Multiculti and based on this OD calculated pigments per mL and per cell (pg/cell)
MultiCultiPigmentMaxFile <- "../ImportedData/SySlmanuscriptWWPhotoperiod/PicoBaltic_MultiCultiPigmentMax.Rds"
MultiCultiPigmentMaxFileName <- str_split(string = MultiCultiPigmentMaxFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
MultiCultiPigmentMax <- readRDS(MultiCultiPigmentMaxFile)  %>%
  ungroup()

```

combine pigments data (for Solisense) and number of cells (based on MultiCulti OD) with PUR and Growth rate
```{r}
#colnames(MultiCultiGrowthRatePURExp)

MultiCultiPigmentMax<-MultiCultiPigmentMax %>% 
  mutate(MultiDay=E_days) %>% 
  mutate(OlisDate = Date) %>% 
  select(-c(FilenameMultiCulti,Filename,E_days,Date)) %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) %>% 
  select(-c(InnocDate,Abs440, Abs480, Abs565, Abs620, Abs650, Abs665))

MultiCultiGrowthRatePURExp<-MultiCultiGrowthRatePURExp %>% 
  select(-c(Filename, OD720_Lmu_corr, OD720_Lmu_se, OD720_LseGrowthFlag, GrowthAmpOD720Flag_14days))

MultiCultiPigmentMaxAll <- MultiCultiGrowthRatePURExp %>%
  left_join(., MultiCultiPigmentMax, by = c("Run"="Run","ID"="ID", "Tube"="Tube", "Strain"="Strain", "ExpDate"="ExpDate","Par_ue"="Par_ue","Photoperiod"="Photoperiod","O2"="O2","WL"="WL","LightShape"="LightShape","ExpEndDate"="ExpEndDate", "E_days"="MultiDay", "E_hours"="Time_h", "PARPhotonDose"="PARPhotonDose", "MC"="MC")) 

MultiCultiPigmentMaxAll <- MultiCultiPigmentMaxAll %>%
  mutate(cellL=cellml*1000) %>% 
  mutate(ChlaugL = ChlaugmL*1000) %>% 
  mutate(PhycougL = (PCugmL+PEugmL+APCugmL)*1000) 

```


Replace negative values in data frame by zero
```{r}
MultiCultiPigmentMaxAll <- MultiCultiPigmentMaxAll                     # Duplicate data frame
MultiCultiPigmentMaxAll[MultiCultiPigmentMaxAll < 0] <- 0     # Set negative values to 0

```
Combine Chla and phyco in one column for nice plot
```{r}
MultiCultiPigmentMaxAllChlaPhyco1<-MultiCultiPigmentMaxAll %>% 
  select(-c(Chlapgcell, Carpgcell)) %>% 
  mutate(Pigmentspgcell=Phycopgcell*1) %>% 
  select(-c(Phycopgcell))
# MultiCultiPigmentMaxAllChlaPhyco1$PigmentsName = factor(MultiCultiPigmentMaxAllChlaPhyco1$O2, labels = c("Total~Phyco~(pg~cell^{-1})"))
MultiCultiPigmentMaxAllChlaPhyco1$PigmentsName = "Phyco"

MultiCultiPigmentMaxAllChlaPhyco2<-MultiCultiPigmentMaxAll %>% 
  select(-c(Phycopgcell, Carpgcell)) %>% 
  mutate(Pigmentspgcell=Chlapgcell*1) %>% 
  select(-c(Chlapgcell))
# MultiCultiPigmentMaxAllChlaPhyco2$PigmentsName = factor(MultiCultiPigmentMaxAllChlaPhyco2$O2, labels = c("Chl~a~(pg~cell^{-1})"))
MultiCultiPigmentMaxAllChlaPhyco2$PigmentsName = "Chla"

MultiCultiPigmentMaxAllChlaPhyco3<-MultiCultiPigmentMaxAll %>% 
  select(-c(Chlapgcell, Phycopgcell)) %>% 
  mutate(Pigmentspgcell=Carpgcell*1) %>% 
  select(-c(Carpgcell))
# MultiCultiPigmentMaxAllChlaPhyco3$PigmentsName = factor(MultiCultiPigmentMaxAllChlaPhyco3$O2, labels = c("Car~(pg~cell^{-1})"))
MultiCultiPigmentMaxAllChlaPhyco3$PigmentsName = "Car"
  
MultiCultiPigmentMaxAllChlaPhyco<-rbind(MultiCultiPigmentMaxAllChlaPhyco1, MultiCultiPigmentMaxAllChlaPhyco2, MultiCultiPigmentMaxAllChlaPhyco3)

rm(MultiCultiPigmentMaxAllChlaPhyco1, MultiCultiPigmentMaxAllChlaPhyco2, MultiCultiPigmentMaxAllChlaPhyco3)
```


Plot -> pigments per cell - PAR PhotonDose and time
```{r fig.height = 8, fig.width = 8}

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))

lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


# Plot <- MultiCultiPigmentMaxAll %>%
#   filter(Par_ue!= 600) %>% 
#   ggplot() +
#   geom_point(aes(x = E_hours, y = Chlapgcell, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3, show.legend = T) +
#   scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab2) +
#   scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab3) +
#   labs(y = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")", x = "Elapsed time (h)") +
#   ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
#   theme_bw() 
# Plot


Plot <- MultiCultiPigmentMaxAllChlaPhyco %>%
  filter(Par_ue!= 600) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose, y = Pigmentspgcell, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab2) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab3) +
  # scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  #labs(y = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")", x = "PARPhotonDOse") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c(0, 1.2)) +
  ggh4x::facet_nested(rows = vars(facetsStrain, Strain), cols = vars(PigmentsName), labeller = label_parsed) +
  theme_bw() 
Plot



Plot <- MultiCultiPigmentMaxAll %>%
  filter(Par_ue!=600) %>% 
  ggplot() +
  # geom_smooth(aes(x = Time_h, y = PURPARRatio, colour = as.factor(Strain)),  alpha = 0, size = 0.2, linetype = "solid", show.legend = T) +
  geom_point(aes(x = E_hours, y = Phycopgcell, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  labs(y = "Total phycobilins content ( pg  " ~ cell^-1~")", x = "Elapsed time (h)") +
  # geom_errorbar(aes(x = Photoperiod, ymin = OD720_Lmu_corr - OD720_Lmu_se, ymax = OD720_Lmu_corr + OD720_Lmu_se), size = 0.3, width=3, color = '#3C3B53', data = . %>% filter(GrowthAmpOD720Flag_14days  == 1)) +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw()
Plot


Plot <- MultiCultiPigmentMaxAllChlaPhyco %>%
  filter(PURPARRatio<=1) %>%
  filter(PARPhotonDose == 432000|
  PARPhotonDose == 864000|
  PARPhotonDose == 1944000|
  PARPhotonDose == 3888000|
  PARPhotonDose == 6480000|
  PARPhotonDose == 8640000|
  PARPhotonDose == 77760000) %>%
  ggplot() +
  geom_point(aes(x = E_hours, y = Pigmentspgcell, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  # geom_vline(data = data_vline5, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline6, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline7, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline8, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "Pigments content ( pg  " ~ cell^-1~")", x = "Elapsed time (h)") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c(0, 1.5)) +
  ggh4x::facet_nested(cols = vars(PARPhotonDose), rows = vars(PigmentsName), labeller = label_parsed) +
  # ggh4x::facet_nested(cols = vars(facets, PhotonDose), labeller = labeller(Photoperiod = Photoperiod.labs,  Strain = label_value, Par_ue = Par_ue.labs, WL = label_parsed, O2 = O2.labs)) +
  theme_bw()
Plot


Plot <- MultiCultiPigmentMaxAllChlaPhyco %>%
  filter(PURPARRatio<=1) %>%
  filter(PARPhotonDose == 432000|
  PARPhotonDose == 864000|
  PARPhotonDose == 1944000|
  PARPhotonDose == 3888000|
  PARPhotonDose == 6480000|
  PARPhotonDose == 8640000|
  PARPhotonDose == 77760000) %>%
  ggplot() +
  geom_point(aes(x = E_hours, y = Pigmentspgcell, colour = as.factor(PigmentsName)), alpha = 0.9, size = 3, show.legend = T) +
  labs(y = "Pigments content ( pg  " ~ cell^-1~")", x = "Elapsed time (h)") +
  ggh4x::facet_nested(cols = vars(PARPhotonDose), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
Plot

```

Combine phyco/Chla ratio and car/chla ratio in one column for nice plot
```{r}
MultiCultiPigmentMaxAllChlaPhycoratio1<-MultiCultiPigmentMaxAll %>% 
  select(-c(PhycoChlaRatio)) %>% 
  mutate(PigmentsRatio=CarChlaRatio*1) %>% 
  select(-c(CarChlaRatio))
# MultiCultiPigmentMaxAllChlaPhyco1$PigmentsName = factor(MultiCultiPigmentMaxAllChlaPhyco1$O2, labels = c("Total~Phyco~(pg~cell^{-1})"))
MultiCultiPigmentMaxAllChlaPhycoratio1$PigmentsRatioName = "CarChlaRatio"

MultiCultiPigmentMaxAllChlaPhycoratio2<-MultiCultiPigmentMaxAll %>% 
  select(-c(CarChlaRatio)) %>% 
  mutate(PigmentsRatio=PhycoChlaRatio*1) %>% 
  select(-c(PhycoChlaRatio))
# MultiCultiPigmentMaxAllChlaPhyco2$PigmentsName = factor(MultiCultiPigmentMaxAllChlaPhyco2$O2, labels = c("Chl~a~(pg~cell^{-1})"))
MultiCultiPigmentMaxAllChlaPhycoratio2$PigmentsRatioName = "PhycoChlaRatio"


  
MultiCultiPigmentMaxAllChlaPhycoratio<-rbind(MultiCultiPigmentMaxAllChlaPhycoratio1, MultiCultiPigmentMaxAllChlaPhycoratio2)

rm(MultiCultiPigmentMaxAllChlaPhycoratio1, MultiCultiPigmentMaxAllChlaPhycoratio2)
```



Plot -> pigments ratio - PAR PhotonDose and time
```{r fig.height = 8, fig.width = 8}


lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))

lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


# Plot <- MultiCultiPigmentMaxAll %>%
#   filter(Par_ue!= 600) %>% 
#   ggplot() +
#   geom_point(aes(x = E_hours, y = PhycoChlaRatio, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3, show.legend = T) +
#   scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab2) +
#   scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab3) +
#   labs(y = "Total Phyco/Chl " ~italic(a)~ "ratio", x = "Elapsed time (h)") +
#   ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
#   theme_bw() 
# Plot

Plot <- MultiCultiPigmentMaxAllChlaPhycoratio %>%
  filter(Par_ue!= 600) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose, y = PigmentsRatio, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab2) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab3) +
  # scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  #labs(y = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")", x = "PARPhotonDOse") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c(0, 1.2)) +
  ggh4x::facet_nested(rows = vars(facetsStrain, Strain), cols = vars(PigmentsRatioName), labeller = label_parsed) +
  theme_bw() 
Plot


Plot <- MultiCultiPigmentMaxAll %>%
  filter(Par_ue!=600) %>% 
  ggplot() +
  geom_point(aes(x = E_hours, y = PhycoChlaRatio, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  labs(y = "Total Phyco/Chl " ~italic(a)~ "ratio", x = "Elapsed time (h)") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw()
Plot



Plot <- MultiCultiPigmentMaxAllChlaPhycoratio %>%
  filter(PURPARRatio<=1) %>%
  filter(PARPhotonDose == 432000|
  PARPhotonDose == 864000|
  PARPhotonDose == 1944000|
  PARPhotonDose == 3888000|
  PARPhotonDose == 6480000|
  PARPhotonDose == 8640000|
  PARPhotonDose == 77760000) %>%
  ggplot() +
  geom_point(aes(x = E_hours, y = PigmentsRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  # geom_vline(data = data_vline5, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline6, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline7, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline8, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Total Phyco/Chl " ~italic(a)~ "ratio", x = "Elapsed time (h)") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c(0, 1.5)) +
  ggh4x::facet_nested(cols = vars(PARPhotonDose), rows = vars(PigmentsRatioName), labeller = label_parsed) +
  # ggh4x::facet_nested(cols = vars(facets, PhotonDose), labeller = labeller(Photoperiod = Photoperiod.labs,  Strain = label_value, Par_ue = Par_ue.labs, WL = label_parsed, O2 = O2.labs)) +
  theme_bw() 
Plot



Plot <- MultiCultiPigmentMaxAllChlaPhycoratio %>%
  filter(PURPARRatio<=1) %>%
  filter(PARPhotonDose == 432000|
  PARPhotonDose == 864000|
  PARPhotonDose == 1944000|
  PARPhotonDose == 3888000|
  PARPhotonDose == 6480000|
  PARPhotonDose == 8640000|
  PARPhotonDose == 77760000) %>%
  ggplot() +
  geom_point(aes(x = E_hours, y = PigmentsRatio, colour = as.factor(PigmentsRatioName)), alpha = 0.9, size = 3, show.legend = T) +
  #labs(y = "Pigments content ( pg  " ~ cell^-1~")", x = "Elapsed time (h)") +
  ggh4x::facet_nested(cols = vars(PARPhotonDose), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
Plot


```


Create only one pigment in exp - for Solisense data
Combine growth rate and exp pigments
```{r}
MultiCultiPigmentMaxAllExp<-MultiCultiPigmentMaxAll 
  
O1 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 30 | Par_ue == 300 | Par_ue == 90 | Par_ue == 180) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days < 4)

O2 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 4)

O3 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 6)

O4 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 12)

O5 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 900 | Par_ue == 600) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 4)

O6 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days == 12| E_days == 13)
  
O7 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days == 12 | E_days ==13)

O8 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 8 | E_days ==9)

O9 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PC-rich_056") %>% 
  filter(E_days == 11)

O10 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 180) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days == 8 | E_days == 9)

O11 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 180) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days == 6 | E_days == 7)

O12 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 8) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 6 | E_days ==7)

O13 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 8) %>% 
  filter(Strain == "PC-rich_056") %>% 
  filter(E_days == 9)

O14 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 4 | E_days ==5)

O15 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PC-rich_056") %>%  
  filter(E_days == 7)

O16 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12)

O17 <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue == 900 | Par_ue == 600) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_hours < 100 & E_hours > 48)

MultiCultiPigmentMaxAllExp2 <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10, O11, O12, O13, O14, O15, O16, O17)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10, O11, O12, O13, O14, O15, O16, O17)

  
```

Because I have replica in growt rate - I combine one choosen pigmen exp to all growth rate data
```{r}
#colnames(MultiCultiDataCleanGrowthAll4)
MultiCultiPigmentMaxAllExp4<-MultiCultiPigmentMaxAllExp2 %>% 
  # mutate(cellL=cellml*1000) %>% 
  # mutate(ChlaugL = ChlaugmL*1000) %>% 
  # mutate(PhycougL = (PCugmL+PEugmL+APCugmL)*1000) %>% 
  mutate(cellLExp = cellL) %>%
  mutate(ChlapgcellExp = Chlapgcell) %>% 
  mutate(PhycopgcellExp = Phycopgcell) %>% 
  mutate(ChlaugLExp = ChlaugL) %>% 
  mutate(PhycougLExp = PhycougL) %>% 
  mutate(PhycoChlaRatioExp = PhycopgcellExp/ChlapgcellExp) %>% 
  select(c(Strain, Par_ue, Photoperiod, ChlapgcellExp, PhycopgcellExp, ChlaugLExp, PhycougLExp, PhycoChlaRatioExp, cellLExp))
  
MultiCultiPigmentMaxAllExp <- MultiCultiPigmentMaxAll %>%
  full_join(., MultiCultiPigmentMaxAllExp4, by = c("Strain"="Strain", "Par_ue"="Par_ue","Photoperiod"="Photoperiod"))


```


Plot -> only exp Phyco, Chla, and Phyco/chla ratio
```{r fig.height = 8, fig.width = 8}


lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))

lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))



Plot <- MultiCultiPigmentMaxAllExp %>%
   filter(Par_ue!=600) %>% 
  ggplot() +
  geom_point(aes(x = E_hoursExp, y = PhycopgcellExp, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  #labs(y = "Total Phyco/Chl " ~italic(a)~ "ratio", x = "Elapsed time (h)") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw()
Plot



Plot <- MultiCultiPigmentMaxAllExp %>%
   filter(Par_ue!=600) %>% 
  ggplot() +
  geom_point(aes(x = E_hoursExp, y = ChlapgcellExp, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  #labs(y = "Total Phyco/Chl " ~italic(a)~ "ratio", x = "Elapsed time (h)") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot <- MultiCultiPigmentMaxAllExp %>%
  filter(Par_ue!=600) %>% 
  ggplot() +
  geom_point(aes(x = E_hoursExp, y = PhycoChlaRatioExp, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  #labs(y = "Total Phyco/Chl " ~italic(a)~ "ratio", x = "Elapsed time (h)") +
  # scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  # coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


```

Create df with only exp data for PUR, PUR/PAR ratio, pigments and cell/L
```{r}
#colnames(MultiCultiPigmentMaxAllExp)
GrowthPigmentPURonlyExp<-MultiCultiPigmentMaxAllExp %>% 
  select(-c(SpectraDate, E_days, PUR, PURPhotonDose, PURPARRatio, E_hours, meanActinic_parDay, meanOD680Day, meanOD720Day, cellml, ChlaugmL, CarugmL, PEugmL, PCugmL, APCugmL, Chlapgcell, Carpgcell, PEpgcell, OlisDate, cellL, ChlaugL, PhycougL, PCpgcell, APCpgcell, Phycopgcell, CarChlaRatio, PhycoChlaRatio, PEPCRatio)) %>% 
  unique()
  
```


rm additional df
```{r}
rm(MultiCultiGrowthAll, MultiCultiGrowth, MultiCultiGrowth121, MultiCultiDataCleanGrowthAll2, MultiCultiDataCleanGrowthAll4)
```
















GROWTH CURVE

Load previos Growth curve 
```{r read ProcessFile}

#data necessary for plot growth curve (round time) for all runs - contained od750, od680 and Actinic Par data
GrowthCurveFile <- "../ImportedData/SySlmanuscriptWWPhotoperiod/PicoBaltic_MultiCultiDataAllStrainsokAll.Rds"
GrowthCurveFileName <- str_split(string = GrowthCurveFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
GrowthCurve <- readRDS(GrowthCurveFile)  %>%
  ungroup()

```

Only for nice plot - lines for tmaxAG 
#I will fix this - take data from existed df!
```{r}

data_vline1 <- data.frame(Par_ue= c(30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900),Photoperiod= c(8,8,8,8,8,12,12,12,12,12,16,16,16,16,16,24,24,24,24,24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(347,321.02,240.90,187.92,168,347,245.39,189.48,162.62,168,347,168.39,113.76,111.56,110,154.64,114.68,93.32,93.78,110))

data_vline2 <- data.frame(Par_ue= c(30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900),Photoperiod= c(8,8,8,8,8,12,12,12,12,12,16,16,16,16,16,24,24,24,24,24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(346,319.92,240.81,214.41,168,346,216.33,163.44,136.03,168,299.38,166.28,137.32,111.28,109.45,119.35,103.77,100.38,79.20,94.23))

data_vline3 <- data.frame(Par_ue= c(30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900),Photoperiod= c(8,8,8,8,8,12,12,12,12,12,16,16,16,16,16,24,24,24,24,24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(345,347,266.84,240.72,168,345,296.45,217.80,191.03,168,345,191.49,114.95,112.75,108,157.85,120.27,110.28,95.79,79.66))

data_vline4 <- data.frame(Par_ue= c(30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900),Photoperiod= c(8,8,8,8,8,12,12,12,12,12,16,16,16,16,16,24,24,24,24,24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(344, 345, 266.93, 215.42, 168,344, 244.38,190.39,163.62,168,299.57, 168.85, 137.50, 112.29, 107,138.78, 120.18, 108.08, 98.36, 107))

```


Choose growth curve, remove unused stuff, add facets and change strain name for nice plot
```{r}

GrowthCurveSmall <- GrowthCurve %>% 
  group_by(ID, timeRound) %>% 
  mutate(DeltaOD = meanOD680-meanOD720) %>% 
  ungroup()

GrowthCurveSmall <- GrowthCurveSmall %>%
  filter(Par_ue != 600) 

MultiCultiData1 <- GrowthCurveSmall %>%
  filter(Par_ue==900 & Photoperiod == 24) %>%
  filter(Run == 121)

MultiCultiData2 <- GrowthCurveSmall %>%
  filter(Par_ue==900 & Photoperiod == 8 | Photoperiod == 12| Photoperiod == 16) 

MultiCultiData3 <- GrowthCurveSmall %>%
  filter(Photoperiod==24 & Par_ue == 30 | Par_ue == 90 | Par_ue == 180 | Par_ue == 300) 

MultiCultiData4 <- GrowthCurveSmall %>% 
  filter(Photoperiod!=24) %>% 
  filter(Par_ue!=900)

GrowthCurveAll<- rbind(MultiCultiData1, MultiCultiData2, MultiCultiData3, MultiCultiData4)

rm(MultiCultiData1, MultiCultiData2, MultiCultiData3, MultiCultiData4, GrowthCurveSmall, GrowthCurve)


GrowthCurveAll$facetsPar_ue = factor(GrowthCurveAll$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))

GrowthCurveAll$facetsPhotoperiod = factor(GrowthCurveAll$WL, labels = c("Photoperiod~(h)"))

GrowthCurveAll <- GrowthCurveAll %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 

```


GrowthCurveAll - contained Growth curve - per strain combine with max growth
Growth curve plot
```{r fig.height = 8, fig.width = 8, warning = FALSE}


Plot <- GrowthCurveAll %>%
  #filter(timeRound <= 110) %>%
  ggplot() +
  geom_area(aes(x = timeRound, y = meanActinic_par), size = 0.1, fill = "tan1", alpha = 0.6) +
  geom_line(aes(x = timeRound, y = meanOD680, colour = as.factor(Strain)), size = 0.7, show.legend = T) +

  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +

  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="") +
  labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +

    # ggh4x::facet_nested(rows = vars(WL, Photoperiod), cols = vars(O2, Par_ue), labeller = labeller(Photoperiod = Photoperiod.labs,  Strain = label_value, Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs), scale="free_x") +
  
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed, scale="free_x") +

  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.085,0.96),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        #plot.background = element_rect(colour = "dodgerblue4", size = 3),
        legend.text = element_text(size=10))

Plot




Plot <- GrowthCurveAll %>%
  #filter(timeRound <= 110) %>%
  ggplot() +
  geom_area(aes(x = timeRound, y = meanActinic_par), size = 0.1, fill = "tan1", alpha = 0.6) +
  geom_line(aes(x = timeRound, y = meanOD680, colour = as.factor(Strain)), size = 0.7, show.legend = T) +

  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +

  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="") +
  labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +

    # ggh4x::facet_nested(rows = vars(WL, Photoperiod), cols = vars(O2, Par_ue), labeller = labeller(Photoperiod = Photoperiod.labs,  Strain = label_value, Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs), scale="free_x") +
  
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +

  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.085,0.96),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        #plot.background = element_rect(colour = "dodgerblue4", size = 3),
        legend.text = element_text(size=10))

Plot
```





