---
title: "Process Solisense Doubletap data"
author: "Douglas A. Campbell, Sylwia Sliwinska-Wilczewska"
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
---

```{r setup, include = FALSE}
# knitr::opts_chunk$set(echo = TRUE, message = FALSE)
# knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ProcessedData")
DataIn <- file.path("..", "Data", "ImportedData", fsep = .Platform$file.sep)

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

```{r load libraries} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggspectra)
library(ggpubr)
library(caret)
library(photobiologyWavebands)
library(reshape2)
library(photobiology)
library(gcookbook)
library(RColorBrewer)
library(viridis)
library(scales)
library(googledrive)
library(googlesheets4)
library(readxl)
library(Cairo) #for greek symbols
```

```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")

names(Colours_nm) <- Wavelengths_nm
Colours_nm

```

```{r load local multiculticatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

MetaData <- read_sheet("https://docs.google.com/spreadsheets/d/1y144Qjs1pxO2vYU4G6of69qX1TVlA8WTwnhfVwaSU0U/edit#gid=0") %>%
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

as.data.frame(MetaData)
MetaData <- MetaData %>%
   mutate(ExpDate = ymd(ExpDate),
          ExpEndDate = ymd_hms(`ExpEndDate`))
```

```{r Exported Rmd only first time in session}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```


RDS already contained only data from corresponding growth light 
Also, conteined mean for sig and JVPSII - for replica measured on the same day
Also, contained mean for chla (ug/L) and cell per L based on Turner and MD Pico


```{r read ProcessFile}
#Solisense file
SolisenseFile <- "../Data/ImportedData/Baltic_Photoperiod_Imported_Solisense_OldComp.Rds"  

SolisenseFileName <- str_split(string = SolisenseFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

SolFits <- readRDS(SolisenseFile)  %>%
  ungroup()


#Solisense file -> data from a new Solisense computer
Solisense2File <- "../Data/ImportedData/Baltic_Photoperiod_Imported_Solisense_NewComp.Rds"

Solisense2FileName <- str_split(string = Solisense2File, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

SolFits2 <- readRDS(Solisense2File)  %>%
  ungroup()

SolFits3<-rbind(SolFits,SolFits2)
rm(SolFits,SolFits2)
```


These dfs contained only sigma in 1s of dark after corresponding light (it caused problems when I tried to combain them with sig in the light)


```{r read ProcessFile}
#Solisense file sigma 1s
Solisense1sFile <- "../Data/ImportedData/Baltic_Photoperiod_Imported_Solisense1s_OldComp.Rds"

Solisense1sFileName <- str_split(string = Solisense1sFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

SolFits1s <- readRDS(Solisense1sFile)  %>%
  ungroup()


#Solisense file -> sigma 1s from a new Solisense computer
Solisense21sFile <- "../Data/ImportedData/Baltic_Photoperiod_Imported_Solisense1s_NewComp.Rds"

Solisense21sFileName <- str_split(string = Solisense21sFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

SolFits21s <- readRDS(Solisense21sFile)  %>%
  ungroup()

SolFits31s<-rbind(SolFits1s,SolFits21s)
rm(SolFits1s,SolFits21s)
```





```{r}
SolFitsAll <-SolFits3 %>% 
  filter(Strain=="BA127R"| Strain=="BA48R"| Strain=="BA56G"| Strain=="BA77G") %>% 
  filter(WL=="WW") %>% 
  filter(O2==21) %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 

SolFitsAll$facetsPhotonDose = factor(SolFitsAll$WL, labels = c("PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})"))

SolFitsAll$facetsExcitation = factor(SolFitsAll$WL, labels = c("Excitation~(nm)"))

SolFitsAll$facetsStrain = factor(SolFitsAll$WL, labels = c("Strain"))


# the same for second df contained sigma 1s
SolFits31s <-SolFits31s %>% 
  filter(Strain=="BA127R"| Strain=="BA48R"| Strain=="BA56G"| Strain=="BA77G") %>% 
  filter(WL=="WW") %>% 
  filter(O2==21) %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 

```

Filter one weird data point 445nm, 16h, 900uE
```{r}
SolFitsAll445<-SolFitsAll %>% 
  filter(Ex_WL == 445) %>% 
  filter(Sig<250)  %>% 
  filter(meanSig_nm2psii<2.5) 

SolFitsAll590<-SolFitsAll %>% 
  filter(Ex_WL == 590) 
  
SolFitsAllChoosen<-rbind(SolFitsAll445,SolFitsAll590)
  rm(SolFitsAll445,SolFitsAll590)
  

```


choose only exp data for sigma and JVPSII in the corresponding light
```{r}
SolFitsAllChoosen2<- SolFitsAllChoosen 
  
O1 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 30 | Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 900) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days <= 4)

O2 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 90 | Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days < 9)

O3 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 4)

O4 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 14)

O5 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=14)
  
O6 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days <=14)

O7 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days <=10)

O8 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=10)

O9 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=7)


SolFitsAllChoosenExp <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, SolFitsAllChoosen2)


```



choose only exp data for Sig 1s
```{r}
SolFitsAllChoosen2<- SolFits31s 
  
O1 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 30 | Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 900) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days <= 4)

O2 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 90 | Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days < 9)

O3 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 4)

O4 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 14)

O5 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=14)
  
O6 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days <=14)

O7 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days <=10)

O8 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=10)

O9 <- SolFitsAllChoosen2 %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=7)


SolFitsAllChoosenExp1s <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, SolFitsAllChoosen2)


```


SolFitsAllChoosenExp and SolFitsAllChoosenExp1s - contained only exp data

Plot
```{r fig.height = 8, fig.width = 8, warning = FALSE}


Plot <- SolFitsAllChoosen %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  # geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot <- SolFitsAllChoosenExp %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  # geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot <- SolFitsAllChoosenExp %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = meanSig, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  # geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
 # scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  #labs(y = "Total Phyco/Chl " ~italic(a)~ "ratio", x = "Elapsed time (h)") +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot
```




Make "one big" mean to combine all days (only from exp) and all replica when samples were measured 
(This give me only one value of JVPSII for further growth vs JVPSII plot and nice sig plot as well)

I select only data from exp phase here

Step_s, Dark1s, ActPAR, ActPARCorr, ActPARCorr_photonsm2s, LR_s, ETRCtauav, ETRqpOxbo,
```{r}
#colnames(SolFitsAllChoosenExp)
#SolFitsAllChoosen<-SolFitsAllChoosen %>% -contained all solisense data 

SolFitsAllChoosenExp<-SolFitsAllChoosenExp %>% 

  group_by(Strain, Ex_WL, Par_ue, Photoperiod) %>%

  summarize(CultureID, Ex_WL, Par_ue, Photoperiod, WL, O2, Filename, Run, Strain, InnocDate, ExpDate, PARPhotonDose, DATE, MDcellsL, meanMDcellsL, sdMDcellsL, TurnerChl_ugL, meanTurnerChl_ugL, sdTurnerChl_ugL, ObsDate, ObsDateTime, FvFm, Sig, meanSig, sdSig, Sig_nm2psii, meanSig_nm2psii, sdSig_nm2psii, Sigdark, meanSigdark_nm2psii, sdSigdark_nm2psii, Sigmax, FoOxbo, Fm, Fo, Fodark, Fomin, 
            
JVPSII_aLHIIOxbomax, JVPSII_ETRtauav_FoSig, JVPSII_ETRqpOxbo_FoSig, JVPSII_ETRtauav_aLHII_Sig, JVPSII_ETRqpOxbo_aLHII_Sig,

meanJVPSII_aLHIIOxbomax, sdJVPSII_aLHIIOxbomax, meanJVPSII_ETRtauav_FoSig, sdJVPSII_ETRtauav_FoSig, meanJVPSII_ETRqpOxbo_FoSig, sdJVPSII_ETRqpOxbo_FoSig, meanJVPSII_ETRtauav_aLHII_Sig, sdJVPSII_ETRtauav_aLHII_Sig, meanJVPSII_ETRqpOxbo_aLHII_Sig, sdJVPSII_ETRqpOxbo_aLHII_Sig, E_days, Time_h, facetsPhotonDose, facetsExcitation, facetsStrain, 

             AllmeanJVPSII_aLHIIOxbomax= mean(JVPSII_aLHIIOxbomax),
             AllmeanJVPSII_ETRtauav_FoSig= mean(JVPSII_ETRtauav_FoSig),
             AllmeanJVPSII_ETRqpOxbo_FoSig= mean(JVPSII_ETRqpOxbo_FoSig),
            AllmeanJVPSII_ETRtauav_aLHII_Sig = mean(JVPSII_ETRtauav_aLHII_Sig),
             AllmeanJVPSII_ETRqpOxbo_aLHII_Sig= mean(JVPSII_ETRqpOxbo_aLHII_Sig),
            AllmeanTurnerChl_ugL = mean(TurnerChl_ugL),
            AllsdTurnerChl_ugL = sd(TurnerChl_ugL),
            AllmeanMDcellsL= mean(MDcellsL),
            AllsdMDcellsL= sd(MDcellsL),
            AllmeanSig_nm2psii = mean(Sig_nm2psii),
            AllsdSig_nm2psii = sd(Sig_nm2psii),
            AllmeanSigdark_nm2psii = mean(Sigdark_nm2psii),
            AllsdSigdark_nm2psii = sd(Sigdark_nm2psii)) %>%
  ungroup()



```
Plot-> sigma vs time and sigma vs photon dose 
```{r fig.height = 8, fig.width = 8, warning = FALSE}


scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


Plot<-SolFitsAllChoosenExp %>% 
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "Sigma", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1000, by = 200)) +
  coord_cartesian(ylim = c(0, 1000)) +
  ggh4x::facet_nested(cols = vars(facetsExcitation,Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 
Plot



Plot<-SolFitsAllChoosenExp %>% 
  filter(Ex_WL==590) %>% 
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "Sigma", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1000, by = 200)) +
  coord_cartesian(ylim = c(0, 1000)) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot



Plot<-SolFitsAllChoosenExp %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose, y = meanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PARPhotonDose, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y=expression(paste(sigma,""["PSII"]*"'(nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # scale_y_continuous(breaks=seq(0, 1000, by = 200)) +
  # coord_cartesian(ylim = c(0, 1000)) +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(cols = vars(facetsExcitation,Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllChoosenExp %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose, y = meanSigdark_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PARPhotonDose, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # scale_y_continuous(breaks=seq(0, 1000, by = 200)) +
  # coord_cartesian(ylim = c(0, 1000)) +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(cols = vars(facetsExcitation,Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllChoosenExp1s %>% # data from second df contained sig 1s
  filter(Par_ue !=600) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose, y = meanSig1s_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  # geom_errorbar(aes(x = PARPhotonDose, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  # labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # scale_y_continuous(breaks=seq(0, 1000, by = 200)) +
  # coord_cartesian(ylim = c(0, 1000)) +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
Plot
```




"We recalculated all the half-life values (T 1/2 ) by using the following equation for one phase decay: Y = (Y0 -Plateau)*exp(-K*X) + Plateau, where X = Time, Y = RNA levels, starting at Y0 and decaying (with one phase) down to plateau; Y0 and plateau have same units as Y; K = Rate constant equal to the recip-
rocal of the X-axis units"

k= the rate constant for Sigma decay (i.e., percent change over time), 

https://www.researchgate.net/figure/The-one-phase-decay-curve-A-and-the-mRNA-quantification-curve-B-from-the-pulse-chase_fig1_235381210

Y = (Y0 -Plateau)*exp(-K*X) + Plateau,
Y - Sigma levels
Y0 - max Sigma
Plateau - min Sigma
X - photon dose


https://stackoverflow.com/questions/50510797/exponential-decay-fit-in-r
https://douglas-watson.github.io/post/2018-09_exponential_curve_fitting/

one phase decay

multiple curves PAR photon Dose 590 ->sin in the light
```{r}

SolFitsAllfit590 <-SolFitsAllChoosen %>% 
  filter(Ex_WL == 590) %>% 
  # filter(E_days<10) %>% 
  filter(E_days !=2) %>%
  #filter(E_days !=3) %>%
  select(c(meanSig_nm2psii, PARPhotonDose, Photoperiod, Par_ue, Strain, Ex_WL)) %>% 
  mutate(y=meanSig_nm2psii) %>% 
  mutate(t=PARPhotonDose) 
  


# Fit the data
fitted <- SolFitsAllfit590 %>% 
  nest(-Strain) %>%
  mutate(
    fit = map(data, ~nls(y ~ SSasymp(t, yf, y0, log_alpha), data = .)),
    tidied = map(fit, tidy),
    augmented590 = map(fit, augment),
  )  

# Produce a table of fit parameters: y0, yf, alpha - doesnt work for now - fix this later!
# fitted %>% 
#   unnest(tidied) %>% 
#   select(term, estimate) %>% 
#   spread(term, estimate) %>% 
#   mutate(alpha = exp(log_alpha))

#Plotting with gglot2
augmented590 <- fitted %>% 
  unnest(augmented590)
# qplot(t, y, data = augmented590, geom = 'point', colour = Strain) +
#   geom_line(aes(y=.fitted))
```

multiple curves PAR photon Dose 590 ->sig dark
```{r}

SolFitsAllfit590dark <-SolFitsAllChoosen %>% 
  filter(Ex_WL == 590) %>% 
  # filter(E_days<10) %>% 
  filter(E_days !=2) %>%
  #filter(E_days !=3) %>%
  select(c(meanSigdark_nm2psii, PARPhotonDose, Photoperiod, Par_ue, Strain, Ex_WL)) %>% 
  mutate(y=meanSigdark_nm2psii) %>% 
  mutate(t=PARPhotonDose) 
  


# Fit the data
fittedark <- SolFitsAllfit590dark %>% 
  nest(-Strain) %>%
  mutate(
    fit = map(data, ~nls(y ~ SSasymp(t, yf, y0, log_alpha), data = .)),
    tidied = map(fit, tidy),
    augmented590dark = map(fit, augment),
  )  


augmented590dark <- fittedark %>% 
  unnest(augmented590dark)
```



mutate for nice plot PAR photon Dose 590 and 445
```{r}
augmented590 <- augmented590 %>% 
  mutate(Ex_WL=Strain) %>% 
      mutate(Ex_WL=case_when(Ex_WL=="PE-rich_127"~590,
         Ex_WL=="PE-rich_048"~590,
        Ex_WL=="PC-rich_056"~590,
         Ex_WL=="PC-rich_077"~590)) %>% 
  mutate(Ex_WL = as.factor(Ex_WL)) %>% 
  mutate(O2=Ex_WL) %>% 
  mutate(O2=case_when(O2==590~21)) %>% 
  mutate(WL=Ex_WL) %>% 
  mutate(WL=case_when(WL==590~"WW")) 

augmented590dark <- augmented590dark %>% 
  mutate(Ex_WL=Strain) %>% 
      mutate(Ex_WL=case_when(Ex_WL=="PE-rich_127"~590,
         Ex_WL=="PE-rich_048"~590,
        Ex_WL=="PC-rich_056"~590,
         Ex_WL=="PC-rich_077"~590)) %>% 
  mutate(Ex_WL = as.factor(Ex_WL)) %>% 
  mutate(O2=Ex_WL) %>% 
  mutate(O2=case_when(O2==590~21)) %>% 
  mutate(WL=Ex_WL) %>% 
  mutate(WL=case_when(WL==590~"WW")) 



```



Delete unused df
```{r}
rm(SolFitsAllfit445, SolFitsAllfit590)
```


Plot sigma vs photondose - mean only replica (shows different days from exp phase)
```{r fig.height = 8, fig.width = 8, warning = FALSE}


WL.labs <- c("Excitation (nm)")
names(WL.labs) <- c("WW")
O2.labs <- c("Strain")
names(O2.labs) <- c(21)


scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))



  ggplot(SolFitsAllChoosenExp, aes(x = PARPhotonDose, y = meanSig_nm2psii)) +
  geom_point(aes(x = PARPhotonDose, y = meanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PARPhotonDose, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Par_ue))) +
  geom_line(aes(t, .fitted), show.legend = F, augmented590) +
  #geom_line(aes(t, .fitted), show.legend = F, augmented445) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*"'(nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # scale_y_continuous(breaks=seq(0, 1000, by = 200)) +
  # coord_cartesian(ylim = c(0, 1000)) +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(rows = vars(O2,Strain), cols = vars(WL,Ex_WL), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.44,0.89),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=9))
  
  
  
  ggplot(SolFitsAllChoosenExp, aes(x = PARPhotonDose, y = meanSigdark_nm2psii)) +
  geom_point(aes(x = PARPhotonDose, y = meanSigdark_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PARPhotonDose, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Par_ue))) +
  geom_line(aes(t, .fitted), show.legend = F, augmented590dark) +
  #geom_line(aes(t, .fitted), show.legend = F, augmented445) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(rows = vars(O2,Strain), cols = vars(WL,Ex_WL), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.44,0.89),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=9))
  
  
    ggplot(SolFitsAllChoosenExp1s, aes(x = PARPhotonDose, y = meanSig1s_nm2psii)) +
  geom_point(aes(x = PARPhotonDose, y = meanSig1s_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PARPhotonDose, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Par_ue))) +
  # geom_line(aes(t, .fitted), show.legend = F, augmented590dark) +
  #geom_line(aes(t, .fitted), show.legend = F, augmented445) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(rows = vars(O2,Strain), cols = vars(WL,Ex_WL), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.44,0.89),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=9))
    
    
    
```





















https://www.r-bloggers.com/2020/02/a-collection-of-self-starters-for-nonlinear-regression-in-r/


sigma vs pigments

Issue - not always pigment based on Olis correspond to Solisense data-> I combine these two df with only selected exp data

Later - come back to OD680data from Multiculti and choose cell/ml (based on pamas corr) corresponding with the same day of sigma and JVPSII!!! Before calculations! Fix this Sylwia!!!!!
```{r}

SolFitsAllPigment <- SolFitsAllChoosenExp %>% 
  left_join(., GrowthPigmentPURonlyExp, by = c("Run"="Run","CultureID"="ID","Strain"="Strain","InnocDate"="InnocDate","ExpDate"="ExpDate","Par_ue"="Par_ue","Photoperiod"="Photoperiod","O2"="O2","WL"="WL","PARPhotonDose"="PARPhotonDose", "facetsStrain" = "facetsStrain")) 


SolFitsAllPigment1s <- SolFitsAllChoosenExp1s %>% 
  left_join(., GrowthPigmentPURonlyExp, by = c("Run"="Run","CultureID"="ID","Strain"="Strain","InnocDate"="InnocDate","ExpDate"="ExpDate","Par_ue"="Par_ue","Photoperiod"="Photoperiod","O2"="O2","WL"="WL","PARPhotonDose"="PARPhotonDose")) 
```




plot - one value of exp sigma and one value of exp pigment
```{r fig.height = 8, fig.width = 8, warning = FALSE}


scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
    geom_smooth(aes(x = PhycoChlaRatioExp, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, alpha =0, show.legend = F, method="lm") +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()


SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSig_nm2psii, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
    geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Strain))) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSigdark_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigdark_nm2psii - AllsdSigdark_nm2psii, ymax = AllmeanSigdark_nm2psii + AllsdSigdark_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSigdark_nm2psii, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
    geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigdark_nm2psii - AllsdSigdark_nm2psii, ymax = AllmeanSigdark_nm2psii + AllsdSigdark_nm2psii, colour=as.factor(Strain))) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 




SolFitsAllPigment1s %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigment1s %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
    geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Strain))) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 



```



Soisense fit -> sig vs Phycobilins and chla
```{r test inhibition plot}

# #Harrison & Platt, 1986 
# grcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)} 

```




Combine PC and PE-rich strains together and filter day 2 and 3 b/c they caused problems
```{r}
SolFitsAllPigmentPC<-SolFitsAllPigment %>% 
  filter(E_days!=2) %>% 
  filter(E_days!=3) %>% 
  filter(Strain == "PC-rich_056" | Strain == "PC-rich_077") 
SolFitsAllPigmentPC$StrainGroup = "PC-rich"

SolFitsAllPigmentPE<-SolFitsAllPigment %>% 
  filter(E_days!=2) %>% 
  filter(E_days!=3) %>% 
  filter(Strain == "PE-rich_048" | Strain == "PE-rich_127")  
SolFitsAllPigmentPE$StrainGroup = "PE-rich"
  
SolFitsAllPigmentPCPE<-rbind(SolFitsAllPigmentPC, SolFitsAllPigmentPE)



SolFitsAllPigmentPC1s<-SolFitsAllPigment1s %>% 
  filter(E_days!=2) %>% 
  filter(E_days!=3) %>% 
  filter(Strain == "PC-rich_056" | Strain == "PC-rich_077") 
SolFitsAllPigmentPC1s$StrainGroup = "PC-rich"

SolFitsAllPigmentPE1s<-SolFitsAllPigment1s %>% 
  filter(E_days!=2) %>% 
  filter(E_days!=3) %>% 
  filter(Strain == "PE-rich_048" | Strain == "PE-rich_127")  
SolFitsAllPigmentPE1s$StrainGroup = "PE-rich"
  
SolFitsAllPigmentPCPE1s<-rbind(SolFitsAllPigmentPC1s, SolFitsAllPigmentPE1s)
```



Linear fit per par_ue
```{r linear fit}
SolFitsAllPigmentfitPhycoChlalinear <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  nest(data = -c("Par_ue", "Ex_WL")) |>  
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
                                                    # start = list(a = 1/10, b = 2/10, Pmax = 8),
                                                    # lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )

# Linear_Model_PredictPhycoChla <- SolFitsAllPigmentfitPhycoChlalinear |>
#   unnest(Linear_Model_Predict)


SolFitsAllPigmentfitPhycoChlalineardark <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  nest(data = -c("Par_ue", "Ex_WL")) |>  
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
                                                    # start = list(a = 1/10, b = 2/10, Pmax = 8),
                                                    # lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )



SolFitsAllPigmentfitPhycoChlalinear1s <- SolFitsAllPigmentPCPE1s |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  nest(data = -c("Par_ue", "Ex_WL")) |>  
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
                                                    # start = list(a = 1/10, b = 2/10, Pmax = 8),
                                                    # lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )




SolFitsAllPigmentfitPhycoChlalinearPCPE1s <- SolFitsAllPigmentPCPE1s |>  
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  nest(data = -c("Par_ue", "Ex_WL", "StrainGroup")) |>  
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
                                                    # start = list(a = 1/10, b = 2/10, Pmax = 8),
                                                    # lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )

```

Plot sig vs phyco/Chla ratio -> linear fit
```{r fig.height = 8, fig.width = 8, warning = FALSE}


scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAllPigmentfitPhycoChlalinear |>
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  # scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  # scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Total phycobilin content ( pg "~cell^-1~")") +
  #labs(y=expression(paste(sigma,""["PSII"]*"'(nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


  SolFitsAllPigmentfitPhycoChlalineardark |>
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


  SolFitsAllPigmentfitPhycoChlalinear1s |>
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE1s) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE1s) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
  
  
```



Linear fit Strain
```{r linear fit}
SolFitsAllPigmentfitPhycoChlalinearStrain <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
                                                    # start = list(a = 1/10, b = 2/10, Pmax = 8),
                                                    # lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )




SolFitsAllPigmentfitPhycoChlalineardarkStrain <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |> 
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
                                                    # start = list(a = 1/10, b = 2/10, Pmax = 8),
                                                    # lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )



SolFitsAllPigmentfitPhycoChlalinearStrain1s <- SolFitsAllPigmentPCPE1s |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
                                                    # start = list(a = 1/10, b = 2/10, Pmax = 8),
                                                    # lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )

#xxxxxx


SolFitsAllPigmentfitPhycoChlalinearStrainGroup <- SolFitsAllPigmentPCPE |>  
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("StrainGroup", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )


SolFitsAllPigmentfitPhycoChlalineardarkStrainGroup <- SolFitsAllPigmentPCPE |>  
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("StrainGroup", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |> 
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )


SolFitsAllPigmentfitPhycoChlalinearStrainGroup1s <- SolFitsAllPigmentPCPE1s |>  
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("StrainGroup", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )
```

Plot sig vs phyco/Chla ratio -> linear fit
```{r fig.height = 8, fig.width = 8, warning = FALSE}

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


SolFitsAllPigmentfitPhycoChlalinearStrain |>
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  # scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  # scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


  SolFitsAllPigmentfitPhycoChlalineardarkStrain |>
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain),labeller = label_parsed) +
  theme_bw() 
  
  
  SolFitsAllPigmentfitPhycoChlalinearStrain1s |>
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE1s) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE1s) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
  
  #xxxxxxxx
  
  SolFitsAllPigmentfitPhycoChlalineardarkStrainGroup |>
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(StrainGroup),labeller = label_parsed) +
  theme_bw() 
  
```

Linear fit Ex_WL
```{r linear fit}
SolFitsAllPigmentfitPhycoChlalinearExWL <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
                                                    # start = list(a = 1/10, b = 2/10, Pmax = 8),
                                                    # lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )



SolFitsAllPigmentfitPhycoChlalineardarkExWL <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |> 
  nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
                                                    # start = list(a = 1/10, b = 2/10, Pmax = 8),
                                                    # lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )



SolFitsAllPigmentfitPhycoChlalinearExWL1s <- SolFitsAllPigmentPCPE1s |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
                                                    # start = list(a = 1/10, b = 2/10, Pmax = 8),
                                                    # lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )

```

Plot sig vs phyco/Chla ratio -> linear fit
```{r fig.height = 8, fig.width = 8, warning = FALSE}

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


SolFitsAllPigmentfitPhycoChlalinearExWL |>
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  # geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigdark_nm2psii - AllsdSigdark_nm2psii, ymax = AllmeanSigdark_nm2psii + AllsdSigdark_nm2psii, colour=as.factor(Par_ue))) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  ggh4x::facet_nested(cols = vars(Ex_WL), labeller = label_parsed) +
  theme_bw() 



  SolFitsAllPigmentfitPhycoChlalineardarkExWL |>
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +  
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), labeller = label_parsed) +
  theme_bw() 

  
  SolFitsAllPigmentfitPhycoChlalinearExWL1s |>
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE1s) + 
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), labeller = label_parsed) +
  theme_bw() 
```



JVPSII

JVPSII vs Chl Turner (ug/L) and JVPSII vs photonDose
I also have data for ChlaugLExp based on Olis corr, but Chla Turner is better
```{r fig.height = 8, fig.width = 8, warning = FALSE}
#colnames(SolFitsAllPigment)

SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = AllmeanTurnerChl_ugL, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  # geom_errorbar(aes(x = ChlapgcellExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #labs(y=expression(paste(sigma,""["PSII"]*"'(nm"^"2"*")")), x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()


SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = cellLExp, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 



SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = AllmeanMDcellsL, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()


SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()

```




Growth rate vs JVPSII
#meandeltaOD_Lmu_corr ->mean for real replica from MultiCulti
```{r fig.height = 8, fig.width = 8, warning = FALSE}
# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

Plot<-SolFitsAllPigment %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
#   geom_errorbar(aes(x = PhotonDose_value, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Par_ue)), width=4000000, data = . %>% filter(deltaOD_Lmu_se<8.057558e-03), show.legend = F) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  #labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = ""~italic(JV)~""["PSII"]*" ( µmol"~e^-~""~L^-1~""~s^-1~")") +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot
```



JVPSII per Turner Chl ug/L and per cell/L
```{r}
#colnames(SolFitsAllPigment)

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig

SolFitsAllPigmentTurner<-SolFitsAllPigment %>% 
  #Turner
  mutate(meanJVPSII_aLHIIOxbomax_Chl = meanJVPSII_aLHIIOxbomax/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Chl = meanJVPSII_ETRtauav_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Chl = meanJVPSII_ETRqpOxbo_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Chl = meanJVPSII_ETRtauav_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Chl = meanJVPSII_ETRqpOxbo_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  
  #cell per L based on MD Pico
  mutate(meanJVPSII_aLHIIOxbomax_MDcell = meanJVPSII_aLHIIOxbomax/AllmeanMDcellsL) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_MDcell = meanJVPSII_ETRtauav_FoSig/AllmeanMDcellsL) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_MDcell = meanJVPSII_ETRqpOxbo_FoSig/AllmeanMDcellsL) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_MDcell = meanJVPSII_ETRtauav_aLHII_Sig/AllmeanMDcellsL) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_MDcell = meanJVPSII_ETRqpOxbo_aLHII_Sig/AllmeanMDcellsL) %>% 
  
  #cell per L based on pamas corr
  mutate(meanJVPSII_aLHIIOxbomax_Corrcell = meanJVPSII_aLHIIOxbomax/cellLExp) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Corrcell = meanJVPSII_ETRtauav_FoSig/cellLExp) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Corrcell = meanJVPSII_ETRqpOxbo_FoSig/cellLExp) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Corrcell = meanJVPSII_ETRtauav_aLHII_Sig/cellLExp) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell = meanJVPSII_ETRqpOxbo_aLHII_Sig/cellLExp) %>% 
  
 
  #Turner - one value
  mutate(AllmeanJVPSII_aLHIIOxbomax_Chl = AllmeanJVPSII_aLHIIOxbomax/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Chl = AllmeanJVPSII_ETRtauav_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Chl = AllmeanJVPSII_ETRqpOxbo_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Chl = AllmeanJVPSII_ETRtauav_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Chl = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  
  #cell per L based on MD Pico - one value
  mutate(AllmeanJVPSII_aLHIIOxbomax_MDcell = AllmeanJVPSII_aLHIIOxbomax/AllmeanMDcellsL) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_MDcell = AllmeanJVPSII_ETRtauav_FoSig/AllmeanMDcellsL) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_MDcell = AllmeanJVPSII_ETRqpOxbo_FoSig/AllmeanMDcellsL) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_MDcell = AllmeanJVPSII_ETRtauav_aLHII_Sig/AllmeanMDcellsL) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_MDcell = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig/AllmeanMDcellsL) %>% 
  
  #cell per L based on pamas corr - one value
  mutate(AllmeanJVPSII_aLHIIOxbomax_Corrcell = AllmeanJVPSII_aLHIIOxbomax/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Corrcell = AllmeanJVPSII_ETRtauav_FoSig/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell = AllmeanJVPSII_ETRqpOxbo_FoSig/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell = AllmeanJVPSII_ETRtauav_aLHII_Sig/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig/cellLExp) 

```



Growth rate vs JVPSII per Chl Turner 

```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Chl, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Chl, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
Plot

```


Growth rate vs JVPSII per cell/L based on Pamas correlation

Growth rate vs JVPSII per cell
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
Plot

```


Growth rate vs JVPSII per cell/L based on MD Pico

Growth rate vs JVPSII per cell
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_MDcell, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_MDcell, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
Plot

```

Growt rate per day
```{r}
#colnames(SolFitsAllPigmentTurnerDay2)
SolFitsAllPigmentTurnerDay2<-SolFitsAllPigmentTurner %>% 
  # select(-c(Alp1QA, Tau1QA, Alp2QA, Tau2QA, Alp3QA, Tau3QA, WtTau, InvWtTau, C_WtTau, Fmdark, Fodark, Fomin, Fmmax, Sigdark, Sigmax, qp, aLHIIdark, aLHIIminmax, meanSig, sdSig, sdSig_m2psii, deltaOD_LseGrowthFlag, GrowthAmpdeltaODFlag_14days)) %>% 
  mutate(deltaOD_Lmu_corr_day=deltaOD_Lmu_corr*24) %>% 
  mutate(deltaOD_Lmu_se_day=deltaOD_Lmu_se*24) %>% 
  mutate(meandeltaOD_Lmu_corr_day=meandeltaOD_Lmu_corr*24) %>% 
  mutate(sddeltaOD_Lmu_corr_day=sddeltaOD_Lmu_corr*24)

```



calculate JVPSII per day
```{r}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


SolFitsAllPigmentTurnerDay81216<-SolFitsAllPigmentTurnerDay2 %>% 
  filter(Photoperiod !=24) %>% 
  mutate(AllmeanJVPSII_aLHIIOxbomax_Corrcell_day = AllmeanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Corrcell_day = AllmeanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*8/2) %>%
  mutate(meanJVPSII_aLHIIOxbomax_Corrcell_day = meanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Corrcell_day = meanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = meanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = meanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*Photoperiod/2) 
  
SolFitsAllPigmentTurnerDay900<-SolFitsAllPigmentTurnerDay2 %>% 
  filter(Photoperiod ==24) %>% 
  mutate(AllmeanJVPSII_aLHIIOxbomax_Corrcell_day = AllmeanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Corrcell_day = AllmeanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*Photoperiod) %>%
  mutate(meanJVPSII_aLHIIOxbomax_Corrcell_day = meanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Corrcell_day = meanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = meanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = meanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*Photoperiod) 
  

SolFitsAllPigmentTurnerDay<-rbind(SolFitsAllPigmentTurnerDay81216, SolFitsAllPigmentTurnerDay900)
  rm(SolFitsAllPigmentTurnerDay81216, SolFitsAllPigmentTurnerDay900)
```


Growth rate vs JVPSII per cell (pamas corr) per day
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_aLHIIOxbomax_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw()
Plot

Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRtauav_FoSig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot

Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot



Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Par_ue)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(labeller = label_parsed) +
  theme_bw() 
Plot

```



6.02 x 10^23 electrons per mole

6.02*10e23 = 6.02e+24
6.02e+24/1000000 = 6.02e+18 ->umol e



# Save assembled spectra data set
```{r save Olis}

# saveRDS(SolFitsAllPigmentTurnerDay, file.path(DataOut, paste(Project, "SolFitsAllPigmentTurnerNew.Rds", sep = "_"), fsep = .Platform$file.sep))


```





