---
title: "Process_PigmentsData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_PigmentsData.Rmd processes and combines pigment catalog from a google sheet and Baltic_Photoperiod_Processed_OlisSpectraTidy.Rds from Data/ProcessedData/ProcessedOlisJazData folder. This .Rmd generates Baltic_Photoperiod_Processed_PigmentAll.Rds and Baltic_Photoperiod_Processed_PigmentsExp.Rds (both stored in Data/ProcessedData/ProcessedPigmentsData folder) and two plots: Pigments_SupPlot.png and  PigRatioPUR_Plot.png (stored in Output/Plots folder).

# Load Libraries and set Project Variables

```{r load libraries} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggpubr)
library(caret)
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedPigmentsData")
DataIn <- file.path("..", "Data", "ImportedData", "ImportedPigmentsData", fsep = .Platform$file.sep)

PlotsPath <- file.path("..", "Output", "Plots")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read files

```{r Exported Rmd only first time in session}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

```{r read pigments File}
#df ontained mean OD per day from Multiculti and Abs from Olis spectra for selected nm. Based on this I calculated pigments per mL and per cell (pg/cell)

MCPigmentFile <- "../Data/ImportedData/ImportedPigmentsData/Baltic_Photoperiod_Imported_Pigments_OtherRepository.Rds"
MCPigmentFileName <- str_split(string = MCPigmentFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
MCPigment <- readRDS(MCPigmentFile)  %>%
  ungroup()

MCPigment <-MCPigment %>% 
  rename(PARPhotonDose_day=PARPhotonDose)
```

# Preparing df for further analysis

```{r Preparing df for further analysis}
MCPigment<-MCPigment %>% 
  drop_na(Date, MC) %>%
  mutate(OlisDate = Date) %>% 
  mutate(CultureID=ID) %>% 
  select(-c(FilenameMultiCulti,Filename,E_days,Date, ID)) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) %>% 
  select(-c(InnocDate,Abs440, Abs480, Abs565, Abs620, Abs650, Abs665)) %>% 
  mutate(E_days=Time_h/24) %>% 
  filter(Par_ue!= 600) 
```

# Replace negative values in df to zero

```{r Replace negative values}
MCPigment <- MCPigment
MCPigment[MCPigment < 0] <- 0

MCPigment<-MCPigment %>% 
  filter(PhycoChlaRatio<10)
```

# Calculate pigments content per L

```{r Calculate pigments per L}
MCPigment <- MCPigment %>%
  mutate(cellL=cellml*1000) %>% 
  mutate(ChlaugL = ChlaugmL*1000) %>% 
  mutate(PhycougL = (PCugmL+PEugmL+APCugmL)*1000) 
```

# Preparing df for plot

```{r Combine Chla, phyco, and Car in one column for final plot}
MCPigment1<-MCPigment %>% 
  select(-c(Chlapgcell, Carpgcell)) %>% 
  mutate(Pigmentspgcell=Phycopgcell*1) %>% 
  select(-c(Phycopgcell))
MCPigment1$PigmentsName = "Total~phycobilins"

MCPigment2<-MCPigment %>% 
  select(-c(Phycopgcell, Carpgcell)) %>% 
  mutate(Pigmentspgcell=Chlapgcell*1) %>% 
  select(-c(Chlapgcell))
MCPigment2$PigmentsName = "Chlorophyll~a"

MCPigment3<-MCPigment %>% 
  select(-c(Chlapgcell, Phycopgcell)) %>% 
  mutate(Pigmentspgcell=Carpgcell*1) %>% 
  select(-c(Carpgcell))
MCPigment3$PigmentsName = "Carotenoids"
  
MCPigmentPlot<-rbind(MCPigment1, MCPigment2, MCPigment3)

rm(MCPigment1, MCPigment2, MCPigment3)
```

# Create facets labels for plot

```{r Create tidy PAR photon dose column and facets for plot}
MCPigmentPlot <- MCPigmentPlot %>%
    mutate(PARPhotonDoseTidy=PARPhotonDose_day/100000)

MCPigmentPlot$facetsPARPhotonDose_day = factor(MCPigmentPlot$WL, labels = c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"))
```

# Load tmaxAG catalog 

```{r}
gs4_deauth()
tmaxAG<- read_sheet("https://docs.google.com/spreadsheets/d/1ksY7xlg9wOsICOBRmZkHPKdd9KOislNwPDzyuJ3UIUI/edit#gid=0")
as.data.frame(tmaxAG)
tmaxAG <- tmaxAG

tmaxAG<-tmaxAG %>% 
  mutate(Par_ue = as.numeric(Par_ue)) %>%
  mutate(Photoperiod = as.numeric(Photoperiod)) %>%
  mutate(tMaxAG = as.numeric(tMaxAG)) %>%
  mutate(dayRound_tmaxAG=tMaxAG/24) %>% 
  mutate(dayRound_tmaxAG = round(dayRound_tmaxAG, digits = 0)) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))

tmaxAG$facetsPar_ue = factor(tmaxAG$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
tmaxAG$facetsPhotoperiod = factor(tmaxAG$WL, labels = c("Photoperiod~(h)"))
tmaxAG$facetsStrain = factor(tmaxAG$O2, labels = c("Strain"))
tmaxAG$facetsPARPhotonDose_day = factor(tmaxAG$WL, labels = c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"))

tmaxAGno24<-tmaxAG %>% 
  filter(Photoperiod != "24") %>% 
  mutate(PARPhotonDose_day =(Par_ue/2)*Photoperiod*3600)
tmaxAG24<-tmaxAG %>% 
  filter(Photoperiod == "24") %>% 
  mutate(PARPhotonDose_day = Par_ue*Photoperiod*3600) 
tmaxAG <-rbind(tmaxAGno24, tmaxAG24)
  rm(tmaxAGno24, tmaxAG24)
```

# Select variable for choosen PARPhotonDose to create a plot

```{r select variable for choosen PARPhotonDose to create a plot}
tmaxAGSelect<-tmaxAG %>% 
  mutate(PARPhotonDoseTidy=PARPhotonDose_day/100000) %>% 
  filter(PARPhotonDoseTidy == 4.32000|
  PARPhotonDoseTidy == 6.48000|
  PARPhotonDoseTidy == 8.64000|
  PARPhotonDoseTidy == 43.20000|
  PARPhotonDoseTidy == 64.80000|
  PARPhotonDoseTidy == 86.40000) 

tmaxAGcar<-tmaxAGSelect  
tmaxAGcar$PigmentsName = "Carotenoids"
tmaxAGChla<-tmaxAGSelect  
tmaxAGChla$PigmentsName = "Chlorophyll~a"
tmaxAGPhyco<-tmaxAGSelect 
tmaxAGPhyco$PigmentsName = "Total~phycobilins"

tmaxAGSelect<-rbind(tmaxAGcar, tmaxAGChla, tmaxAGPhyco)
rm(tmaxAGcar, tmaxAGChla, tmaxAGPhyco)

tmaxAGcarRatio<-tmaxAGSelect
tmaxAGcarRatio$PigmentsRatioName = "Car/Chl~a~ratio"
tmaxAGPhycoRatio<-tmaxAGSelect
tmaxAGPhycoRatio$PigmentsRatioName = "Total~Phyco/Chl~a~ratio"

tmaxAGSelect<-rbind(tmaxAGcarRatio, tmaxAGPhycoRatio)
rm(tmaxAGcarRatio, tmaxAGPhycoRatio)
```

# Create 4 df for vertical lines (coloured as Strain) contained tMaxAG value

```{r select revelant columns}
tMaxAGLines_056Select<-tmaxAGSelect %>% 
  filter(Strain == "PC-rich_056") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PigmentsName, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_077Select<-tmaxAGSelect %>% 
  filter(Strain == "PC-rich_077") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PigmentsName, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_048Select<-tmaxAGSelect %>% 
  filter(Strain == "PE-rich_048") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PigmentsName, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_127Select<-tmaxAGSelect %>% 
  filter(Strain == "PE-rich_127") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PigmentsName, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
```

# Create pigments per cell plot

```{r Final pigments per cell plot, fig.height = 8, fig.width = 8}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

MCPigmentPlot %>%
  filter(PARPhotonDoseTidy == 4.32000|
  PARPhotonDoseTidy == 6.48000|
  PARPhotonDoseTidy == 8.64000|
  PARPhotonDoseTidy == 43.20000|
  PARPhotonDoseTidy == 64.80000|
  PARPhotonDoseTidy == 86.40000) %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Pigmentspgcell, colour = as.factor(Strain)), alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4", size=0.4) +
  geom_vline(data = tMaxAGLines_077Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3", size=0.4) +
  geom_vline(data = tMaxAGLines_048Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4", size=0.4) +
  geom_vline(data = tMaxAGLines_127Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1", size=0.4) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "Pigments content ( pg  " ~ cell^-1~")", x = "Elapsed time (h)") +
  ggh4x::facet_nested(cols = vars(facetsPARPhotonDose_day, PARPhotonDoseTidy), rows = vars(factor(PigmentsName, levels=c('Chlorophyll~a', 'Total~phycobilins', 'Carotenoids'))), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.087,0.95),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.005, "cm"),
        legend.spacing.x = unit(-0.005, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```

```{r}

MCPigmentPlot24<-MCPigmentPlot %>% 
  filter(Photoperiod==24)

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

MCPigmentPlot24 %>%
  filter(E_days!=3) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = Pigmentspgcell, colour = as.factor(Par_ue)), alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab3) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Pigments content ( pg  " ~ cell^-1~")", x = "Elapsed time (h)") +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(factor(PigmentsName, levels=c('Chlorophyll~a', 'Total~phycobilins', 'Carotenoids'))), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.9,0.95),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.005, "cm"),
        legend.spacing.x = unit(-0.005, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```




# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("Pigments_SupPlot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```

# Combine phyco/Chla ratio and car/chla ratio in one column for final plot

```{r Combine phyco/Chla ratio and car/chla ratio in one column for final plot}
MCPigmentRatio1<-MCPigment %>% 
  select(-c(PhycoChlaRatio)) %>% 
  mutate(PigmentsRatio=CarChlaRatio*1) %>% 
  select(-c(CarChlaRatio))
MCPigmentRatio1$PigmentsRatioName = "Car/Chl~a~ratio"

MCPigmentRatio2<-MCPigment %>% 
  select(-c(CarChlaRatio)) %>% 
  mutate(PigmentsRatio=PhycoChlaRatio*1) %>% 
  select(-c(PhycoChlaRatio))
MCPigmentRatio2$PigmentsRatioName = "Total~Phyco/Chl~a~ratio"

MCPigmentRatioPlot<-rbind(MCPigmentRatio1, MCPigmentRatio2)

rm(MCPigmentRatio1, MCPigmentRatio2)
```

# Create 4 df for vertical lines (coloured as Strain) contained tMaxAG value

```{r select revelant columns}
tMaxAGLines_056Select<-tmaxAGSelect %>% 
  filter(Strain == "PC-rich_056") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PigmentsRatioName, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_077Select<-tmaxAGSelect %>% 
  filter(Strain == "PC-rich_077") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PigmentsRatioName, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_048Select<-tmaxAGSelect %>% 
  filter(Strain == "PE-rich_048") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PigmentsRatioName, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_127Select<-tmaxAGSelect %>% 
  filter(Strain == "PE-rich_127") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PigmentsRatioName, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
```

```{r Create tidy PAR photon dose column and facets for plot}
MCPigmentRatioPlot <- MCPigmentRatioPlot %>%
    mutate(PARPhotonDoseTidy=PARPhotonDose_day/100000)

MCPigmentRatioPlot$facetsPARPhotonDose_day = factor(MCPigmentRatioPlot$WL, labels = c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"))
```

```{r Final pigments per cell plot, fig.height = 5, fig.width = 8}
data_textA <- data.frame(
  facetsPARPhotonDose_day=c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"),
  PARPhotonDoseTidy = c(86.40000),
  label = c("A"))

lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

Plot1<-MCPigmentRatioPlot %>%
  filter(PigmentsRatioName!="Car/Chl~a~ratio") %>% 
  filter(PARPhotonDoseTidy == 4.32000|
  PARPhotonDoseTidy == 6.48000|
  PARPhotonDoseTidy == 8.64000|
  PARPhotonDoseTidy == 43.20000|
  PARPhotonDoseTidy == 64.80000|
  PARPhotonDoseTidy == 86.40000) %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = PigmentsRatio, colour = as.factor(Strain)), alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4", size=0.4) +
  geom_vline(data = tMaxAGLines_077Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3", size=0.4) +
  geom_vline(data = tMaxAGLines_048Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4", size=0.4) +
  geom_vline(data = tMaxAGLines_127Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1", size=0.4) +
  geom_text(data=data_textA, aes(x=300, y=6.3, label=label), size=5) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "Total Phyco/Chl a ratio", x = "Elapsed time (h)") +
  #labs(y = "Total Phycobilins/Chl " ~italic(a)~ "ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 7.5, by = 1.5)) +
  coord_cartesian(ylim = c(0, 6.5)) +
  ggh4x::facet_nested(cols = vars(facetsPARPhotonDose_day, PARPhotonDoseTidy), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_blank(),
        axis.title = element_text(size=16),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.085,0.90),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.005, "cm"),
        legend.spacing.x = unit(-0.005, "cm"),
        legend.title = element_blank(),
        axis.ticks.x = element_blank(),
        legend.text = element_text(size=10))
Plot1
```
# Set project variables

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataIn <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData", fsep = .Platform$file.sep)
```

# List and read files

```{r Exported Rmd only first time in session}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

```{r Read processed Olis and jaz tidy file for PUR/PAR ratio plot}
OLISAllPURTidyFile <- "../Data/ProcessedData/ProcessedOlisJazData/Baltic_Photoperiod_Processed_OlisSpectraTidy.Rds"
OLISAllPURTidyFileName <- str_split(string = OLISAllPURTidyFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
OLISAllPURTidy <- readRDS(OLISAllPURTidyFile)  %>%
  ungroup()
```

# Create PUR/PAR ratio plot

```{r create PUR/PAR ratio plot, fig.height = 5, fig.width = 8}
data_textB <- data.frame(
  facetsPARPhotonDose_day=c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"),
  PARPhotonDoseTidy = c(86.40000),
  label = c("B"))

lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

Plot2<-OLISAllPURTidy %>%
  filter(PARPhotonDoseTidy == 4.32000|
  PARPhotonDoseTidy == 6.48000|
  PARPhotonDoseTidy == 8.64000|
  PARPhotonDoseTidy == 43.20000|
  PARPhotonDoseTidy == 64.80000|
  PARPhotonDoseTidy == 86.40000) %>%
  ggplot() +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.8, size = 3, show.legend = F) +
  geom_vline(data = tMaxAGLines_056Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4", size=0.4) +
  geom_vline(data = tMaxAGLines_077Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3", size=0.4) +
  geom_vline(data = tMaxAGLines_048Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4", size=0.4) +
  geom_vline(data = tMaxAGLines_127Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1", size=0.4) +
  geom_text(data=data_textB, aes(x=300, y=1.05, label=label), size=5) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1, by = 0.5)) +
  coord_cartesian(ylim = c(0, 1.1)) +
  ggh4x::facet_nested(cols = vars(facetsPARPhotonDose_day, PARPhotonDoseTidy), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.08,0.87),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.005, "cm"),
        legend.spacing.x = unit(-0.005, "cm"),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
Plot2
```

# Merge two plots into one with panel A and B

```{r Final Plot arrange, fig.height = 10, fig.width = 8, warning = FALSE}
ggarrange(Plot1,Plot2,
          ncol = 1, nrow = 2)
```


```{r}
OLISAllPURTidy24<-OLISAllPURTidy %>% 
  filter(Photoperiod==24)

lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

OLISAllPURTidy24 %>%

  ggplot() +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Par_ue)), alpha = 0.8, size = 3, show.legend = F) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab3) +
  # scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1, by = 0.5)) +
  coord_cartesian(ylim = c(0, 1.1)) +
  ggh4x::facet_nested(cols = vars(Strain), labeller = label_parsed) +
  theme_bw() 

```



# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("PigRatioPUR_Plot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```

# Save Plot RDS

```{r}
saveRDS(MCPigmentPlot, file.path(RDSPlotPath, paste(Project, "Plot_Pigment.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(MCPigmentRatioPlot, file.path(RDSPlotPath, paste(Project, "Plot_PigmentRatioA.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(OLISAllPURTidy, file.path(RDSPlotPath, paste(Project, "Plot_PigmentRatioB.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r Cleaning the environment}
rm(data_textA, data_textB, Plot1, Plot2, tMaxAGLines_056Select, tMaxAGLines_077Select, tMaxAGLines_048Select, tMaxAGLines_127Select, OLISAllPURTidy, MCPigmentPlot, MCPigmentRatioPlot)
```

# Merge Pigment data and tMaxAG to choose only pigments measured at exponential growth

```{r Combine pigment and tMaxAG df}
MCPigmenttMaxAG <- MCPigment %>%
  left_join(., tmaxAG, by = c("Strain"="Strain","Par_ue"="Par_ue","Photoperiod"="Photoperiod", "WL"="WL", "O2"="O2", "PARPhotonDose_day"="PARPhotonDose_day"))
```

# Divided pigments data to Exponential and Pre-stationary phase according to tmaxAG

```{r divided pigments data to Exponential and Pre-stationary}
MCPigmenttMaxAG <- MCPigmenttMaxAG %>%
  mutate(Phase = O2) %>%
  mutate(Phase=case_when(E_days<=dayRound_tmaxAG~"Exponential",
         E_days>dayRound_tmaxAG~"Pre-stationary"))
```

# Create df with only one exp pigment data for specific condition

```{r create df with only one exp pigment data for specific condition}
O1 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 30 | Par_ue == 300 | Par_ue == 90 | Par_ue == 180) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days < 4)

O2 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 4)

O3 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 6)

O4 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 12)

O5 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 900 | Par_ue == 600) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 4)

O6 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days == 12| E_days == 13)
  
O7 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days == 12 | E_days ==13)

O8 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 8 | E_days ==9)

O9 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PC-rich_056") %>% 
  filter(E_days == 11)

O10 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 180) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days == 8 | E_days == 9)

O11 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 180) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days == 6 | E_days == 7)

O12 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 8) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 6 | E_days ==7)

O13 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 8) %>% 
  filter(Strain == "PC-rich_056") %>% 
  filter(E_days == 9)

O14 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 4 | E_days ==5)

O15 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PC-rich_056") %>%  
  filter(E_days == 7)

O16 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12)

O17 <- MCPigmenttMaxAG %>%
  filter(Par_ue == 900 | Par_ue == 600) %>% 
  filter(Photoperiod == 24) %>% 
  filter(Time_h < 100 & Time_h > 48)

MCPigmenttMaxAGExp <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10, O11, O12, O13, O14, O15, O16, O17)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10, O11, O12, O13, O14, O15, O16, O17)
```

```{r}
MCPigmenttMaxAGExp<-MCPigmenttMaxAGExp %>%
  mutate(cellLExp = cellL) %>%
  mutate(ChlapgcellExp = Chlapgcell) %>%
  mutate(PhycopgcellExp = Phycopgcell) %>%
  mutate(ChlaugLExp = ChlaugL) %>%
  mutate(PhycougLExp = PhycougL) %>%
  mutate(E_daysExp = E_days) %>%
  mutate(Time_hExp = Time_h) %>%
  mutate(PhycoChlaRatioExp = PhycopgcellExp/ChlapgcellExp) %>%
  select(c(Strain, Par_ue, Photoperiod, ChlapgcellExp, PhycopgcellExp, ChlaugLExp, PhycougLExp, PhycoChlaRatioExp, cellLExp, E_daysExp, Time_hExp))
```

# Create 4 df for vertical lines (coloured as Strain) contained tMaxAG value

```{r select revelant columns}
tMaxAGLines_056<-tmaxAG %>% 
  filter(Strain == "PC-rich_056") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_077<-tmaxAG %>% 
  filter(Strain == "PC-rich_077") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_048<-tmaxAG %>% 
  filter(Strain == "PE-rich_048") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_127<-tmaxAG %>% 
  filter(Strain == "PE-rich_127") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
```

# Create preliminary plots

```{r preliminary plot}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

MCPigment %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Chlapgcell, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4") +
  geom_vline(data = tMaxAGLines_077, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1") +
  geom_vline(data = tMaxAGLines_048, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = tMaxAGLines_127, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw()


MCPigmenttMaxAGExp %>%
  ggplot() +
  geom_point(aes(x = Time_hExp, y = ChlapgcellExp, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4") +
  geom_vline(data = tMaxAGLines_077, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1") +
  geom_vline(data = tMaxAGLines_048, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = tMaxAGLines_127, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw()
```

# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r}
rm(tMaxAGLines_056, tMaxAGLines_077, tMaxAGLines_048, tMaxAGLines_127, MCPigment, tmaxAG, tmaxAGSelect)
```

# Save rds for further analysis

```{r save rds}
saveRDS(MCPigmenttMaxAG, file.path(DataOut, paste(Project, "Processed_PigmentAll.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(MCPigmenttMaxAGExp, file.path(DataOut, paste(Project, "Processed_PigmentsExp.Rds", sep = "_"), fsep = .Platform$file.sep))
```

# Variable names used in Data Dictionary

```{r}
colnames(MCPigmenttMaxAG)
```

# Variable names used in Data Dictionary

```{r}
colnames(MCPigmenttMaxAGExp)
```




