---
title: "Process_GrowthSymmetryData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

This RMD imports Growth Symmetry (GS) catalog from a google sheet.

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)
library(stringi)
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthSymmetryData")

PlotsPath <- file.path("..", "Output", "Plots")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS")

FileID <- "Smooth"
FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# Read MetaData

```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data","CultureCatalog.Rds"))

CultureCatalog<-CultureCatalog %>% 
  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, O2_Category, Optode, OptodeCh, OptodeMeasure))
```

# Read Growth Symmetry (GS) catalog

```{r load local GS catalog, results = "hide", message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
# this is the URL or ID of a Sheet readable by anyone (with a link)
GScatalog<- read_sheet("https://docs.google.com/spreadsheets/d/1zqH6iYlqMPigyloLKJPeVWugmcnmgJ-eMU3gLkR6FSU/edit#gid=0")

as.data.frame(GScatalog)
GScatalog <- GScatalog 
```

# Preparing df for further analysis

```{r prepare data - mutate as numeric, calculate AccLen, DecLen, GS (growth symmetry)}
GScatalog <- GScatalog %>% 
  mutate(Acc_perc = as.numeric(Acc_perc)) %>% 
  mutate(Dec_perc = as.numeric(Dec_perc)) %>% 
  mutate(AccDecRatio_perc = Acc_perc/Dec_perc) %>% 
  mutate(Par_ue = as.numeric(Par_ue)) %>% 
  mutate(Photoperiod = as.numeric(Photoperiod)) %>%
  mutate(tMaxAG = as.numeric(tMaxAG)) %>%
  mutate(tMaxDG = as.numeric(tMaxDG)) %>%
  mutate(PhotoperiodTstart_h=as.numeric(PhotoperiodTstart_h)) %>% 
  mutate(PhotoperiodTend_h=as.numeric(PhotoperiodTend_h)) %>% 
  mutate(AccLen = tMaxDG-PhotoperiodTstart_h) %>% 
  mutate(DecLen = PhotoperiodTend_h-tMaxDG) %>% 
  mutate(GS = AccLen/DecLen) %>% 
  mutate(TDG = as.numeric(TDG)) 
```

# Merge GS catalog with MetaData

```{r merge GS catalog with MetaData, warning = FALSE, echo=FALSE}
GScatalogMeta <- CultureCatalog %>%
  left_join(., GScatalog, by = c("Strain" = "Strain", "Photoperiod"="Photoperiod", "Par_ue"="Par_ue","WL"="WL", "O2"="O2")) 
```

# Filtering unrelated values and outliers

```{r cleaning unrelated values and outliers}
GScatalogMeta<-GScatalogMeta %>% 
  filter(Photoperiod!=24) %>% 
  filter(AccDecRatio_perc<10)
  
GScatalogMeta1 <-GScatalogMeta %>% 
  filter(PARPhotonDose_day>=19440000) %>% 
  filter(GS<=2)
GScatalogMeta2 <-GScatalogMeta %>% 
  filter(PARPhotonDose_day<19440000) %>% 
filter(GS<4)

GScatalogMeta<-rbind(GScatalogMeta1,GScatalogMeta2)
rm(GScatalogMeta1,GScatalogMeta2)
```

# Calculate mean of GS from every day (every peak in exp and pre-stationary phase)

```{r calculate mean of GS, warning = FALSE}
GScatalogMeta<-GScatalogMeta %>% 
  group_by(Strain, Photoperiod, Par_ue, Phase) %>%
  summarize(Run, SampleID, Strain, ExpDate, Par_ue, Photoperiod, PARPhotonDose_day, MC, Tube, O2, LightShape, ExpEndDate, PhotoperiodTstart_h, PhotoperiodTend_h,tMaxDG,tMaxAG, Phase, AchivePreStationary, MaxDG, MaxAG, Acc_perc, Dec_perc, Strain, Par_ue, Photoperiod, O2, WL, OD680start, OD680end, TDG, AccDecRatio_perc, AccLen, DecLen, GS, 
            meanAccLen = mean(AccLen), 
            sdAccLen = sd(AccLen),
            meanDecLen = mean(DecLen), 
            sdDecLen = sd(DecLen),
            meanGS = mean(GS), 
            sdGS = sd(GS)) %>%  
  ungroup() 
```
# Rename strain names, create facets labels, and create horizontal lines for plot

```{r rename strain names for plot}
GScatalogMeta<-GScatalogMeta %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))
```

```{r create facets labels for plot}
GScatalogMeta$facetsPar_ue = factor(GScatalogMeta$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
GScatalogMeta$facetsPhotoperiod = factor(GScatalogMeta$WL, labels = c("Photoperiod~(h)"))
GScatalogMeta$facetsStrain = factor(GScatalogMeta$O2, labels = c("Strain"))
GScatalogMeta$facetsPhase = factor(GScatalogMeta$WL, labels = c("Phase~of~growth"))
```

```{r create df to show hline}
data_hlineGS8 <- data.frame(Photoperiod= c(8),facets2= c("Photoperiod~(h)"),value = c(4))
data_hlineGS12 <- data.frame(Photoperiod= c(12),facets2= c("Photoperiod~(h)"),value = c(6))
data_hlineGS16 <- data.frame(Photoperiod= c(16),facets2= c("Photoperiod~(h)"),value = c(8))
```

# Fit the data to exponential decays

```{r fitting exponential decays, warning = FALSE}
GScatalogMetaExp <-GScatalogMeta %>% 
  drop_na(GS) %>%
  filter(Phase == "Exponential") %>% 
  select(c(GS, PARPhotonDose_day, Strain)) 

# Fit the data
fitted <- GScatalogMetaExp %>% 
  nest(-Strain) %>%
  mutate(
    fit = map(data, ~nls(GS ~ SSasymp(PARPhotonDose_day, yf, y0, log_alpha), data = .)),
    tidied = map(fit, tidy),
    augmented = map(fit, augment)) 

# Produce a table of fit parameters: y0, yf, alpha
fitted_GS_Param<-fitted %>% 
  unnest(tidied) %>% 
  select(Strain, term, estimate) %>% 
pivot_wider(., names_from = c(term), values_from = c(estimate)) %>% 
  mutate(alpha = exp(log_alpha)) 
```

```{r unnest, preparing df to preparing final plot, warning = FALSE}
augmented<-fitted  %>%
  unnest(augmented) %>%
  select(c(Strain, PARPhotonDose_day,GS, .fitted)) 

GSMetaExp <-GScatalogMeta %>% 
  filter(Phase == "Exponential") 

GSMetaExpPlot <- GSMetaExp %>%
  left_join(., augmented, by = c("Strain"="Strain", "PARPhotonDose_day"="PARPhotonDose_day", "GS"="GS"))

GSMetaSt <-GScatalogMeta %>% 
  filter(Phase == "Pre-stationary") %>% 
  mutate(.fitted=0)

GScatalogMetaFinalPlot<-rbind(GSMetaExpPlot, GSMetaSt)

rm(augmented, fitted, GSMetaSt)
```

# Create GS and AccLen plots

```{r create GS plot, fig.height = 8, fig.width = 8, warning = FALSE}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

  ggplot(GScatalogMetaFinalPlot, aes(x = PARPhotonDose_day, y = meanGS)) +
  geom_point(aes(x = PARPhotonDose_day, y = meanGS, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.8, show.legend = T, GScatalogMetaFinalPlot) +
  geom_errorbar(aes(x = PARPhotonDose_day, ymin = meanGS - sdGS, ymax = meanGS + sdGS, colour = as.factor(Par_ue)), show.legend = F, width=0, size=0.3, GScatalogMetaFinalPlot) +
  geom_line(aes(PARPhotonDose_day, .fitted), show.legend = F, GSMetaExpPlot) +
  geom_hline(yintercept = 1, linetype="dashed", size=0.4) +
   labs(y = "Diel growth symmetry (AccLen/DecLen)", x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  scale_shape_manual(values = c(15, 16, 17), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.92,0.88),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("GS_Plot",".png",sep = "")), height=8, width= 8,  dpi = 300, limitsize = TRUE)
```

```{r AccLen Plot, fig.height = 8, fig.width = 8, warning = FALSE}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

GScatalogMeta %>%
  filter(meanAccLen>0) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = meanAccLen, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.8, show.legend = T) +
    geom_line(aes(x = PARPhotonDose_day, y = meanAccLen, colour = as.factor(Par_ue)), size = 0.3, show.legend = F) +
  geom_errorbar(aes(x = PARPhotonDose_day, ymin = meanAccLen - sdAccLen, ymax = meanAccLen + sdAccLen, colour = as.factor(Par_ue)), show.legend = F, width=0, size=0.3) +
  geom_hline(data = data_hlineGS8, aes(yintercept = value), linetype="dotted", size=0.4) +
  geom_hline(data = data_hlineGS12, aes(yintercept = value), linetype="dotdash", size=0.4) +
  geom_hline(data = data_hlineGS16, aes(yintercept = value), linetype="dashed", size=0.4) +
  labs(y = "AccLen (h)", x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  scale_shape_manual(values = c(15, 16, 17), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  scale_x_continuous(label=scientific_10) +
  scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  coord_cartesian(ylim = c(0, 12)) +
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.912,0.88),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("AccLen_Plot",".png",sep = "")), height=8, width= 8,  dpi = 300, limitsize = TRUE)
```

```{r AccLen Plot, fig.height = 8, fig.width = 8, warning = FALSE}

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

GScatalogMeta %>%
  filter(meanAccLen>0) %>% 
  ggplot() +
  geom_point(aes(x = Photoperiod, y = meanAccLen, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.8, show.legend = T) +
  geom_errorbar(aes(x = Photoperiod, ymin = meanAccLen - sdAccLen, ymax = meanAccLen + sdAccLen, colour = as.factor(Par_ue)), show.legend = F, width=0) +
labs(y = "AccLen (h)", x = "Photoperiod (h)") +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  geom_abline(slope = 0.5, intercept = 0, linetype = "dashed") +
  scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  coord_cartesian(ylim = c(0, 14)) +
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        panel.spacing.x = unit(1,"lines"),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.575,0.91),
        #legend.margin = margin(0,-0.5,0,0, unit="cm"),
        legend.key.height= unit(0.0005, 'cm'),
        legend.spacing.y = unit(-0.2, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=9))
```

# Create 4 df for vertical lines (coloured as Strain) contained tMaxAG values

```{r create df for vertical lines}
#PC-rich_056
data_vline_056 <- data.frame(Par_ue= c(30, 30, 30, 90, 90, 90, 180, 180, 180, 300, 300, 300, 900, 900, 900),Photoperiod= c(8,12,16,8,12,16,8,12,16,8,12,16,8,12,16),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(293.8333, 321.0833, 323.0833, 317.2500, 269.5833, 174.1667, 242.6667, 198.0833, 104.5833, 218.9167, 173.7500, 102.5833, 147.5000, 148.41667, 148.66667))

#PC-rich_077
data_vline_077 <- data.frame(Par_ue= c(30, 30, 30, 90, 90, 90, 180, 180, 180, 300, 300, 300, 900, 900, 900),Photoperiod= c(8,12,16,8,12,16,8,12,16,8,12,16,8,12,16),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(244.2500, 318.0833, 272.4167, 316.6667, 222.2500, 153.5833, 242.7500, 173.1667, 125.0833, 195.9167, 148.8333, 102.1667, 146.0833, 161.08333, 147.33333))

#PE-rich_048
data_vline_048 <- data.frame(Par_ue= c(30, 30, 30, 90, 90, 90, 180, 180, 180, 300, 300, 300, 900, 900, 900),Photoperiod= c(8,12,16,8,12,16,8,12,16,8,12,16,8,12,16),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(315.6667, 318.4167, 272.2500, 290.9167, 196.7500, 151.2500, 219.0000, 148.6667, 124.9167, 195.0000, 123.7500, 101.2500, 146.0000, 123.16667, 99.58333))

#PE-rich_127
data_vline_127 <- data.frame(Par_ue= c(30, 30, 30, 90, 90, 90, 180, 180, 180, 300, 300, 300, 900, 900, 900),Photoperiod= c(8,12,16,8,12,16,8,12,16,8,12,16,8,12,16),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(315.1667, 319.0000, 321.0833, 291.9167, 223.1667, 153.1667, 219.0833, 172.3333, 103.5000, 170.9167, 147.9167, 101.5000, 145.83333, 147.08333, 123.50000))
```

# Create TDG plot

```{r Create TDG plot, fig.height = 8, fig.width = 8, warning = FALSE}
GScatalogMeta %>%
  filter(Photoperiod != 24) %>% 
  ggplot() +
  geom_point(aes(x = PhotoperiodTend_h, y = TDG, colour = as.factor(Strain)), size = 3, alpha = 0.8, show.legend = T) +
  geom_vline(data = data_vline_056, aes(xintercept = value), linetype="dotdash", colour = "seagreen4", size=0.4) +
  geom_vline(data = data_vline_077, aes(xintercept = value), linetype="dotdash", colour = "palegreen3", size=0.4) +
  geom_vline(data = data_vline_048, aes(xintercept = value), linetype="dotdash", colour = "brown4", size=0.4) +
  geom_vline(data = data_vline_127, aes(xintercept = value), linetype="dotdash", colour = "brown1", size=0.4) +
labs(y = "TDG ("~OD[680]~")", x = "Elapsed time (h)") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_x_continuous(breaks=seq(0, 300, by = 100)) +
  coord_cartesian(xlim = c(0, 350)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        legend.background = element_rect(fill="transparent"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #panel.spacing.x=unit(0.9, "lines"),
        legend.position = c(0.095,0.93),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("TDG_SupPlot",".png",sep = "")), height=8, width= 8,  dpi = 300, limitsize = TRUE)
```

# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r cleaning the environment}
rm(data_hlineGS8, data_hlineGS12, data_hlineGS16, GScatalog, GScatalogMetaExp,  CultureCatalog, data_vline_048, data_vline_127, data_vline_056, data_vline_077, GScatalogMetaFinalPlot, GSMetaExp, GSMetaExpPlot)
```

# Save rds for further analysis

```{r save rds}
saveRDS(GScatalogMeta, file.path(DataOut, paste(Project, "Processed_GrowthSymmetryData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(GScatalogMeta, file.path(RDSPlotPath, paste(Project, "Plot_GrowthSymmetry.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```



