---
title: "ProcessGrowthCurve"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

This RMD process MultiCulti files and generate growth curves plot.

# Load Libraries and set Project Variables

```{r load libraries} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggpubr)
library(reshape2)
library(photobiology)
library(gcookbook)
library(scales)
library(googledrive)
library(googlesheets4)
library(readxl)
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthCurveData")
DataIn <- file.path("..", "Data", "ImportedData", "ImportedMCData", fsep = .Platform$file.sep)

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read imported MC files

```{r Exported Rmd only first time in session}
list.files(path = DataIn, full.names = TRUE)
```

# Import selected Rds and calculate mean OD from every hour based on ToD

## Import Run39

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20211214_PICO_MC247_RUN39_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData39 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run40

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20211223_PICO_MC257_RUN40_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData40 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run43

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20211229_PICO_MC247_RUN43_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData43 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run44

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220107_PICO_MC257_RUN44_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData44 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run45

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220113_PICO_MC247_RUN45_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData45 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run46

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220122_PICO_MC257_RUN46_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData46 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run54

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220322_PICO_MC257_RUN54_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData54 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run55

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220322_PICO_MC247_RUN55_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData55 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run58

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220330_PICO_MC257_RUN58_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData58 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run60

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220405_PICO_MC247_RUN60_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData60 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run62

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220410_PICO_MC257_RUN62_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData62 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run65

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220420_PICO_MC257_RUN65_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData65 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run71

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220507_PICO_MC257_RUN71_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData71 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run74

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220607_PICO_MC257_RUN74_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData74 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run75

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220607_PICO_MC247_RUN75_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData75 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run77

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220615_PICO_MC257_RUN77_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData77 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run117

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20230625_PICO_MC247_RUN117_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData117 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```

## Import Run121

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20230816_PICO_MC257_RUN121_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time)
  
MultiCultiData121 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(time_h, Filename, Tube, ToD, Day, ExpDate, Actinic_par, OD680, OD720, Run, CultureID, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par = mean(Actinic_par), meanOD680 = mean(OD680), meanOD720 = mean(OD720)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720)) %>% 
  unique()
```


```{r}
MultiCultiDataAll<-rbind(MultiCultiData39, MultiCultiData40, MultiCultiData43, MultiCultiData44, MultiCultiData45, MultiCultiData46, MultiCultiData54, MultiCultiData55, MultiCultiData58, MultiCultiData60, MultiCultiData62, MultiCultiData65, MultiCultiData71, MultiCultiData74, MultiCultiData75, MultiCultiData77, MultiCultiData117, MultiCultiData121)

rm(MultiCultiData, MultiCultiData39, MultiCultiData40, MultiCultiData43, MultiCultiData44, MultiCultiData45, MultiCultiData46, MultiCultiData54, MultiCultiData55, MultiCultiData58, MultiCultiData60, MultiCultiData62, MultiCultiData65, MultiCultiData71, MultiCultiData74, MultiCultiData75, MultiCultiData77, MultiCultiData117, MultiCultiData121)
```

54, 75, 117
55, 58, 77
```{r}
MultiCultiData121 %>%
  ggplot() +
  geom_area(aes(x = time_h, y = meanActinic_par), size = 0.1, fill = "tan1", alpha = 0.6) +
  geom_point(aes(x = time_h, y = meanOD680, colour = as.factor(Strain)), size = 0.7, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="") +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed, scale="free_x") +
  theme_bw() 
```





```{r}
MultiCultiDataAllStrainsok2 <- MultiCultiDataAllStrainsok %>% 
  group_by(ID, timeRound) %>% 
  mutate(DeltaOD = meanOD680-meanOD720) %>% 
ungroup()

```



od720 from Multiculti - mean from day
```{r}
# colnames(MultiCultiDataAllStrainsok)
#group_by(ID, Strain, Par_ue, Day, Run, ExpDate, Photoperiod, Tube) %>% 
MultiCultiOD750 <- MultiCultiDataAllStrainsok %>% 

group_by(ID, Day, ExpDate) %>% 
summarize(ID, timeRound, Filename, Tube, Day, ExpDate, Run,  Strain, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par, meanOD680, meanOD720, meanActinic_parDay = mean(meanActinic_par), meanOD680Day = mean(meanOD680),  meanOD720Day = mean(meanOD720)) %>%
ungroup()

MultiCultiOD750Small <- MultiCultiOD750 %>%
  select(-c(timeRound, meanActinic_par, meanOD680, meanOD720)) %>% 
  unique()
```







Load previos Growth curve 
```{r read ProcessFile}

#data necessary for plot growth curve (round time) for all runs - contained od750, od680 and Actinic Par data
GrowthCurveFile <- "../ImportedData/SySlmanuscriptWWPhotoperiod/PicoBaltic_MultiCultiDataAllStrainsokAll.Rds"
GrowthCurveFileName <- str_split(string = GrowthCurveFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
GrowthCurve <- readRDS(GrowthCurveFile)  %>%
  ungroup()

```

Only for nice plot - lines for tmaxAG 
#I will fix this - take data from existed df!
```{r}

data_vline1 <- data.frame(Par_ue= c(30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900),Photoperiod= c(8,8,8,8,8,12,12,12,12,12,16,16,16,16,16,24,24,24,24,24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(347,321.02,240.90,187.92,168,347,245.39,189.48,162.62,168,347,168.39,113.76,111.56,110,154.64,114.68,93.32,93.78,110))

data_vline2 <- data.frame(Par_ue= c(30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900),Photoperiod= c(8,8,8,8,8,12,12,12,12,12,16,16,16,16,16,24,24,24,24,24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(346,319.92,240.81,214.41,168,346,216.33,163.44,136.03,168,299.38,166.28,137.32,111.28,109.45,119.35,103.77,100.38,79.20,94.23))

data_vline3 <- data.frame(Par_ue= c(30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900),Photoperiod= c(8,8,8,8,8,12,12,12,12,12,16,16,16,16,16,24,24,24,24,24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(345,347,266.84,240.72,168,345,296.45,217.80,191.03,168,345,191.49,114.95,112.75,108,157.85,120.27,110.28,95.79,79.66))

data_vline4 <- data.frame(Par_ue= c(30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900,30, 90, 180, 300, 900),Photoperiod= c(8,8,8,8,8,12,12,12,12,12,16,16,16,16,16,24,24,24,24,24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)"), value = c(344, 345, 266.93, 215.42, 168,344, 244.38,190.39,163.62,168,299.57, 168.85, 137.50, 112.29, 107,138.78, 120.18, 108.08, 98.36, 107))

```


Choose growth curve, remove unused stuff, add facets and change strain name for nice plot
```{r}

GrowthCurveSmall <- GrowthCurve %>% 
  group_by(ID, timeRound) %>% 
  mutate(DeltaOD = meanOD680-meanOD720) %>% 
  ungroup()

GrowthCurveSmall <- GrowthCurveSmall %>%
  filter(Par_ue != 600) 

MultiCultiData1 <- GrowthCurveSmall %>%
  filter(Par_ue==900 & Photoperiod == 24) %>%
  filter(Run == 121)

MultiCultiData2 <- GrowthCurveSmall %>%
  filter(Par_ue==900 & Photoperiod == 8 | Photoperiod == 12| Photoperiod == 16) 

MultiCultiData3 <- GrowthCurveSmall %>%
  filter(Photoperiod==24 & Par_ue == 30 | Par_ue == 90 | Par_ue == 180 | Par_ue == 300) 

MultiCultiData4 <- GrowthCurveSmall %>% 
  filter(Photoperiod!=24) %>% 
  filter(Par_ue!=900)

GrowthCurveAll<- rbind(MultiCultiData1, MultiCultiData2, MultiCultiData3, MultiCultiData4)

rm(MultiCultiData1, MultiCultiData2, MultiCultiData3, MultiCultiData4, GrowthCurveSmall, GrowthCurve)


GrowthCurveAll$facetsPar_ue = factor(GrowthCurveAll$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))

GrowthCurveAll$facetsPhotoperiod = factor(GrowthCurveAll$WL, labels = c("Photoperiod~(h)"))

GrowthCurveAll <- GrowthCurveAll %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 

```


GrowthCurveAll - contained Growth curve - per strain combine with max growth
Growth curve plot
```{r fig.height = 8, fig.width = 8, warning = FALSE}


MultiCultiDataAll %>%
  #filter(timeRound <= 110) %>%
  ggplot() +
  geom_area(aes(x = time_h, y = meanActinic_par), size = 0.1, fill = "tan1", alpha = 0.6) +
  geom_point(aes(x = time_h, y = meanOD680, colour = as.factor(Strain)), size = 0.7, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="") +
  labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed, scale="free_x") +
  theme_bw() 





Plot <- GrowthCurveAll %>%
  #filter(timeRound <= 110) %>%
  ggplot() +
  geom_area(aes(x = timeRound, y = meanActinic_par), size = 0.1, fill = "tan1", alpha = 0.6) +
  geom_line(aes(x = timeRound, y = meanOD680, colour = as.factor(Strain)), size = 0.7, show.legend = T) +

  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +

  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="") +
  labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +

    # ggh4x::facet_nested(rows = vars(WL, Photoperiod), cols = vars(O2, Par_ue), labeller = labeller(Photoperiod = Photoperiod.labs,  Strain = label_value, Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs), scale="free_x") +
  
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +

  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.085,0.96),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        #plot.background = element_rect(colour = "dodgerblue4", size = 3),
        legend.text = element_text(size=10))

Plot
```





