---
title: "Process_GrowthRateSolisenseData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

This RMD process growth rate and Solisense rds.

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(caret)
library(reshape2)
library(gcookbook)
library(scales)
library(Cairo) #for greek symbols
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessesGrowthRateData")
DataInGrowthRate <- file.path("..", "Data", "ProcessedData", "ProcessesGrowthRateData", fsep = .Platform$file.sep)

DataInSolisense <- file.path("..", "Data", "ProcessedData", "ProcessedSolisenseData", fsep = .Platform$file.sep)

PlotsPath <- file.path("..", "Output", "Plots")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read Imported_Solisense RDS

```{r Exported Rmd}
list.files(path = DataInGrowthRate, pattern = Project, full.names = TRUE)
list.files(path = DataInSolisense, pattern = Project, full.names = TRUE)
```

```{r read ProcessFile}
GrowthRateFile <- "../Data/ProcessedData/ProcessesGrowthRateData/Baltic_Photoperiod_Procesed_GrowthRate.Rds"
GrowthRateFileName <- str_split(string = GrowthRateFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

GrowthRate <- readRDS(GrowthRateFile)  %>%
  ungroup()
```

```{r read ProcessFile}
SolisenseFile <- "../Data/ProcessedData/ProcessedSolisenseData/Baltic_Photoperiod_Procesed_SolisensePigmentsExp.Rds"
SolisenseFileName <- str_split(string = SolisenseFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

Solisense <- readRDS(SolisenseFile)  %>%
  ungroup()
```

# Merge Growth rate and Solisense

```{r Joining growth rate and Solisense exp data}
GrowthRateSoliExp <- Solisense %>% 
  left_join(., GrowthRate, by = c("SampleID"="SampleID", "Run"="Run",  "Strain"="Strain", "ExpDate"="ExpDate", "Par_ue"="Par_ue","Photoperiod"="Photoperiod", "O2"="O2", "WL"="WL", "PARPhotonDose_day"="PARPhotonDose_day", "ObsDate"="ObsDate", "E_days"="E_days", "Time_h"="E_hours", "E_daysExp" = "E_daysExp")) 
```

#sig per phyco/chla ratio
Issue - not always pigment based on Olis correspond to Solisense data-> I combine these two df with only selected exp data

Later - come back to OD680data from Multiculti and choose cell/ml (based on pamas corr) corresponding with the same day of sigma and JVPSII!!! Before calculations! Fix this Sylwia!!!!!


```{r Test plot}

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

GrowthRateSoliExp %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()
```



JVPSII

JVPSII vs Chl Turner (ug/L) and JVPSII vs photonDose

```{r warning = FALSE}

GrowthRateSoliExp %>% 
  ggplot() +
  geom_point(aes(x = ChlaugLExp, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  # geom_errorbar(aes(x = ChlapgcellExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()


GrowthRateSoliExp %>% 
  ggplot() +
  geom_point(aes(x = cellLExp, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


GrowthRateSoliExp %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()
```

!!!!! Znalezc blad!!!! Brakujace wartosci, brak 24h!!!!!

Growth rate vs JVPSII


#meandeltaOD_Lmu_corr ->mean for real replica from MultiCulti
```{r fig.height = 8, fig.width = 8, warning = FALSE}
# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

GrowthRateSoliExp %>% 
  #filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(JVPSII_ETRqpOxbo_aLHII_Sig, deltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
#   geom_errorbar(aes(x = PhotonDose_value, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Par_ue)), width=4000000, data = . %>% filter(deltaOD_Lmu_se<8.057558e-03), show.legend = F) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  #labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = ""~italic(JV)~""["PSII"]*" ( µmol"~e^-~""~L^-1~""~s^-1~")") +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
```



JVPSII per Turner Chl ug/L and per cell/L
```{r}
#colnames(SolFitsAllPigment)

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig

GrowthRateSoliExp<-GrowthRateSoliExp %>% 
  #Turner
  mutate(meanJVPSII_aLHIIOxbomax_Chl = meanJVPSII_aLHIIOxbomax/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Chl = meanJVPSII_ETRtauav_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Chl = meanJVPSII_ETRqpOxbo_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Chl = meanJVPSII_ETRtauav_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Chl = meanJVPSII_ETRqpOxbo_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  
  #cell per L based on pamas corr
  mutate(meanJVPSII_aLHIIOxbomax_Corrcell = meanJVPSII_aLHIIOxbomax/cellLExp) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Corrcell = meanJVPSII_ETRtauav_FoSig/cellLExp) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Corrcell = meanJVPSII_ETRqpOxbo_FoSig/cellLExp) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Corrcell = meanJVPSII_ETRtauav_aLHII_Sig/cellLExp) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell = meanJVPSII_ETRqpOxbo_aLHII_Sig/cellLExp) %>% 
  
 
  #Turner - one value
  mutate(AllmeanJVPSII_aLHIIOxbomax_Chl = AllmeanJVPSII_aLHIIOxbomax/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Chl = AllmeanJVPSII_ETRtauav_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Chl = AllmeanJVPSII_ETRqpOxbo_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Chl = AllmeanJVPSII_ETRtauav_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Chl = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 

  #cell per L based on pamas corr - one value
  mutate(AllmeanJVPSII_aLHIIOxbomax_Corrcell = AllmeanJVPSII_aLHIIOxbomax/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Corrcell = AllmeanJVPSII_ETRtauav_FoSig/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell = AllmeanJVPSII_ETRqpOxbo_FoSig/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell = AllmeanJVPSII_ETRtauav_aLHII_Sig/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig/cellLExp) 
```



Growth rate vs JVPSII per Chl Turner 

```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


GrowthRateSoliExp %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Chl, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 



GrowthRateSoliExp %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Chl, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


```


Growth rate vs JVPSII per cell/L based on Pamas correlation

Growth rate vs JVPSII per cell
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


GrowthRateSoliExp
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


GrowthRateSoliExp
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


```


Growth rate vs JVPSII per cell/L based on MD Pico

Growth rate vs JVPSII per cell
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


GrowthRateSoliExp
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_MDcell, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


GrowthRateSoliExp 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_MDcell, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 

```

Growt rate per day
```{r}

GrowthRateSoliExp<-GrowthRateSoliExp %>% 

  mutate(deltaOD_Lmu_corr_day=deltaOD_Lmu_corr*24) %>% 
  mutate(deltaOD_Lmu_se_day=deltaOD_Lmu_se*24) %>% 
  mutate(meandeltaOD_Lmu_corr_day=meandeltaOD_Lmu_corr*24) %>% 
  mutate(sddeltaOD_Lmu_corr_day=sddeltaOD_Lmu_corr*24)

```



calculate JVPSII per day
```{r}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


SolFitsAllPigmentTurnerDay81216<-GrowthRateSoliExp %>% 
  filter(Photoperiod !=24) %>% 
  mutate(AllmeanJVPSII_aLHIIOxbomax_Corrcell_day = AllmeanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Corrcell_day = AllmeanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*8/2) %>%
  mutate(meanJVPSII_aLHIIOxbomax_Corrcell_day = meanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Corrcell_day = meanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = meanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = meanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*Photoperiod/2) 
  


SolFitsAllPigmentTurnerDay900<-GrowthRateSoliExp %>% 
  filter(Photoperiod ==24) %>% 
  mutate(AllmeanJVPSII_aLHIIOxbomax_Corrcell_day = AllmeanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Corrcell_day = AllmeanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*Photoperiod) %>%
  mutate(meanJVPSII_aLHIIOxbomax_Corrcell_day = meanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Corrcell_day = meanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = meanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = meanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*Photoperiod) 
  

SolFitsAllPigmentTurnerDay<-rbind(SolFitsAllPigmentTurnerDay81216, SolFitsAllPigmentTurnerDay900)
  rm(SolFitsAllPigmentTurnerDay81216, SolFitsAllPigmentTurnerDay900)
```


Growth rate vs JVPSII per cell (pamas corr) per day
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_aLHIIOxbomax_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw()


SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRtauav_FoSig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 




SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 



SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 



SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Par_ue)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(labeller = label_parsed) +
  theme_bw() 


```



6.02 x 10^23 electrons per mole

6.02*10e23 = 6.02e+24
6.02e+24/1000000 = 6.02e+18 ->umol e



# Save assembled spectra data set
```{r save Olis}

# saveRDS(SolFitsAllPigmentTurnerDay, file.path(DataOut, paste(Project, "SolFitsAllPigmentTurnerNew.Rds", sep = "_"), fsep = .Platform$file.sep))

```


Set up R codes for Greek letters

\u0391  Α   Greek Capital Letter Alpha
\u0392  Β   Greek Capital Letter Beta
\u0393  Γ   Greek Capital Letter Gamma
\u0394  Δ   Greek Capital Letter Delta
\u0395  Ε   Greek Capital Letter Epsilon
\u0396  Ζ   Greek Capital Letter Zeta
\u0397  Η   Greek Capital Letter Eta
\u0398  Θ   Greek Capital Letter Theta
\u0399  Ι   Greek Capital Letter Iota
\u039A  Κ   Greek Capital Letter Kappa
\u039B  Λ   Greek Capital Letter Lambda
\u039C  Μ   Greek Capital Letter Mu
\u039D  Ν   Greek Capital Letter Nu
\u039E  Ξ   Greek Capital Letter Xi
\u039F  Ο   Greek Capital Letter Omicron
\u03A0  Π   Greek Capital Letter Pi
\u03A1  Ρ   Greek Capital Letter Rho
\u03A3  Σ   Greek Capital Letter Sigma
\u03A4  Τ   Greek Capital Letter Tau
\u03A5  Υ   Greek Capital Letter Upsilon
\u03A6  Φ   Greek Capital Letter Phi
\u03A7  Χ   Greek Capital Letter Chi
\u03A8  Ψ   Greek Capital Letter Psi
\u03A9  Ω   Greek Capital Letter Omega
\u03B1  α   Greek Small Letter alpha
\u03B2  β   Greek Small Letter beta
\u03B3  γ   Greek Small Letter gamma
\u03B4  δ   Greek Small Letter delta
\u03B5  ε   Greek Small Letter epsilon
\u03B6  ζ   Greek Small Letter zeta
\u03B7  η   Greek Small Letter eta
\u03B8  θ   Greek Small Letter theta
\u03B9  ι   Greek Small Letter iota
\u03BA  κ   Greek Small Letter kappa
\u03BB  λ   Greek Small Letter lambda
\u03BC  μ   Greek Small Letter mu
\u03BD  ν   Greek Small Letter nu
\u03BE  ξ   Greek Small Letter xi
\u03BF  ο   Greek Small Letter omicron
\u03C0  π   Greek Small Letter pi
\u03C1  ρ   Greek Small Letter rho
\u03C2  ς   Greek Small Letter final sigma
\u03C3  σ   Greek Small Letter sigma
\u03C4  τ   Greek Small Letter tau
\u03C5  υ   Greek Small Letter upsilon
\u03C6  φ   Greek Small Letter phi
\u03C7  χ   Greek Small Letter chi
\u03C8  ψ   Greek Small Letter psi
\u03C9  ω   Greek Small Letter omega





