---
title: "Process_SolisensePigmentsData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

This RMD process Solisense and pigments rds.

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(caret)
library(reshape2)
library(gcookbook)
library(scales)
library(Cairo) #for greek symbols
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisenseData")
DataIn <- file.path("..", "Data", "ImportedData", "ImportedSolisenseData", fsep = .Platform$file.sep)
```

# List and read Imported_Solisense RDS

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

# This RDS contained only data from corresponding growth light 
# Also, conteined mean sig - mean for replica measured on the same day

```{r read ProcessFile}
SolisenseFile <- "../Data/ImportedData/ImportedSolisenseData/Baltic_Photoperiod_Imported_SolisenseLight.Rds"  

SolisenseFileName <- str_split(string = SolisenseFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

SolFits <- readRDS(SolisenseFile)  %>%
  ungroup()
```

# This RDS contained only sigma in 1s of dark after corresponding light (it caused problems when I tried to combain them with sig in the light)
# Also, conteined mean for sig1s - mean for replica measured on the same day

```{r read ProcessFile}
Solisense1sFile <- "../Data/ImportedData/ImportedSolisenseData/Baltic_Photoperiod_Imported_SolisenseDarkafterLight.Rds"

Solisense1sFileName <- str_split(string = Solisense1sFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

SolFits1s <- readRDS(Solisense1sFile)  %>%
  ungroup()
```

```{r Preparing df for further analysis}
SolFits <-SolFits %>% 
  filter(Strain=="BA127R"| Strain=="BA48R"| Strain=="BA56G"| Strain=="BA77G") %>% 
  filter(WL=="WW") %>% 
  filter(O2==21) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 

SolFits$facetsPhotonDose = factor(SolFits$WL, labels = c("PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})"))
SolFits$facetsExcitation = factor(SolFits$WL, labels = c("Excitation~(nm)"))
SolFits$facetsStrain = factor(SolFits$WL, labels = c("Strain"))


SolFits1s <-SolFits1s %>% 
  filter(Strain=="BA127R"| Strain=="BA48R"| Strain=="BA56G"| Strain=="BA77G") %>% 
  filter(WL=="WW") %>% 
  filter(O2==21) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 
```

# Filter unrevelant data and outliers

```{r filter outliers}
# #Filter one unrevelant data point 445nm, 16h, 900uE
# SolFitsAll445<-SolFits %>% 
#   filter(Ex_WL == 445) %>% 
#   filter(Sig_m2psii<250)  %>% 
#   filter(meanSig_nm2psii<2.5) 
# 
# SolFitsAll590<-SolFits %>% 
#   filter(Ex_WL == 590) 
#   
# SolFitsChoosen<-rbind(SolFitsAll445,SolFitsAll590)
#   rm(SolFitsAll445,SolFitsAll590)
```

# Choose only exp data for sigma and JVPSII in the corresponding light

```{r choose only exp data}
O1 <- SolFitsChoosen %>%
  filter(Par_ue == 30 | Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 900) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days <= 4)

O2 <- SolFitsChoosen %>%
  filter(Par_ue == 90 | Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days < 9)

O3 <- SolFitsChoosen %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 4)

O4 <- SolFitsChoosen %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 14)

O5 <- SolFitsChoosen %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=14)
  
O6 <- SolFitsChoosen %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days <=14)

O7 <- SolFitsChoosen %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days <=10)

O8 <- SolFitsChoosen %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=10)

O9 <- SolFitsChoosen %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=7)

SolFitsChoosenExp <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9)
```

# Choose only exp data for sigma and JVPSII at 1s after corresponding light

```{r choose only exp data for Sig 1s}
O1 <- SolFits1s %>%
  filter(Par_ue == 30 | Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 900) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days <= 4)

O2 <- SolFits1s %>%
  filter(Par_ue == 90 | Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days < 9)

O3 <- SolFits1s %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 4)

O4 <- SolFits1s %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 14)

O5 <- SolFits1s %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=14)
  
O6 <- SolFits1s %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days <=14)

O7 <- SolFits1s %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days <=10)

O8 <- SolFits1s %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=10)

O9 <- SolFits1s %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=7)

SolFitsChoosenExp1s <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9)
```

# Create preliminary plot

```{r preliminary plot}
SolFitsChoosen %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = JVPSII_ETRtauav_FoSig, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  # geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Ex_WL, Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsChoosenExp %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig_m2psii, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  # geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsChoosenExp %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = meanSig_nm2psii, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  # geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
 # scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  #labs(y = "Total Phyco/Chl " ~italic(a)~ "ratio", x = "Elapsed time (h)") +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
```

Make "one big" mean to combine all days (only from exp) and all replica when samples were measured 
(This give me only one value of JVPSII for further growth vs JVPSII plot and nice sig plot as well)

I select only data from exp phase here

Step_s, Dark1s, ActPAR, ActPARCorr, ActPARCorr_photonsm2s, LR_s, ETRCtauav, ETRqpOxbo,
```{r}
#colnames(SolFitsAllChoosenExp)
#SolFitsAllChoosen<-SolFitsAllChoosen %>% -contained all solisense data 

SolFitsAllChoosenExp<-SolFitsAllChoosenExp %>% 

  group_by(Strain, Ex_WL, Par_ue, Photoperiod) %>%

  summarize(CultureID, Ex_WL, Par_ue, Photoperiod, WL, O2, Filename, Run, Strain, InnocDate, ExpDate, PARPhotonDose, DATE, MDcellsL, meanMDcellsL, sdMDcellsL, TurnerChl_ugL, meanTurnerChl_ugL, sdTurnerChl_ugL, ObsDate, ObsDateTime, FvFm, meanSig, sdSig, Sig_nm2psii, meanSig_nm2psii, sdSig_nm2psii, Sigdark, meanSigdark_nm2psii, sdSigdark_nm2psii, Sigmax, FoOxbo, Fm, Fo, Fodark, Fomin, 
            
JVPSII_aLHIIOxbomax, JVPSII_ETRtauav_FoSig, JVPSII_ETRqpOxbo_FoSig, JVPSII_ETRtauav_aLHII_Sig, JVPSII_ETRqpOxbo_aLHII_Sig,

E_days, Time_h, facetsPhotonDose, facetsExcitation, facetsStrain, 

             AllmeanJVPSII_aLHIIOxbomax= mean(JVPSII_aLHIIOxbomax),
             AllmeanJVPSII_ETRtauav_FoSig= mean(JVPSII_ETRtauav_FoSig),
             AllmeanJVPSII_ETRqpOxbo_FoSig= mean(JVPSII_ETRqpOxbo_FoSig),
            AllmeanJVPSII_ETRtauav_aLHII_Sig = mean(JVPSII_ETRtauav_aLHII_Sig),
             AllmeanJVPSII_ETRqpOxbo_aLHII_Sig= mean(JVPSII_ETRqpOxbo_aLHII_Sig),
            AllmeanTurnerChl_ugL = mean(TurnerChl_ugL),
            AllsdTurnerChl_ugL = sd(TurnerChl_ugL),
            AllmeanMDcellsL= mean(MDcellsL),
            AllsdMDcellsL= sd(MDcellsL),
            AllmeanSig_nm2psii = mean(Sig_nm2psii),
            AllsdSig_nm2psii = sd(Sig_nm2psii),
            AllmeanSigdark_nm2psii = mean(Sigdark_nm2psii),
            AllsdSigdark_nm2psii = sd(Sigdark_nm2psii)) %>%
  ungroup()
```

# Create preliminary plot

```{r preliminary plot}

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAllChoosenExp %>% 
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig_m2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "Sigma", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1000, by = 200)) +
  coord_cartesian(ylim = c(0, 1000)) +
  ggh4x::facet_nested(cols = vars(facetsExcitation,Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsAllChoosenExp %>% 
  filter(Ex_WL==590) %>% 
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  labs(y = "Sigma", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1000, by = 200)) +
  coord_cartesian(ylim = c(0, 1000)) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsAllChoosenExp %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose, y = meanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PARPhotonDose, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*"'(nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(cols = vars(facetsExcitation,Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsAllChoosenExp %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose, y = meanSigdark_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PARPhotonDose, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(cols = vars(facetsExcitation,Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsAllChoosenExp1s %>% # data from second df contained sig 1s
  filter(Par_ue !=600) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose, y = meanSig1s_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  # geom_errorbar(aes(x = PARPhotonDose, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```



# Fit data to one phase decay

multiple curves PAR photon Dose 590 ->sin in the light
```{r}
SolFitsAllfit590 <-SolFitsAllChoosen %>% 
  filter(Ex_WL == 590) %>% 
  # filter(E_days<10) %>% 
  filter(E_days !=2) %>%
  #filter(E_days !=3) %>%
  select(c(meanSig_nm2psii, PARPhotonDose, Photoperiod, Par_ue, Strain, Ex_WL)) %>% 
  mutate(y=meanSig_nm2psii) %>% 
  mutate(t=PARPhotonDose) 
  
# Fit the data
fitted <- SolFitsAllfit590 %>% 
  nest(-Strain) %>%
  mutate(
    fit = map(data, ~nls(y ~ SSasymp(t, yf, y0, log_alpha), data = .)),
    tidied = map(fit, tidy),
    augmented590 = map(fit, augment),
  )  

# Produce a table of fit parameters: y0, yf, alpha - doesnt work for now - fix this later!
# fitted %>% 
#   unnest(tidied) %>% 
#   select(term, estimate) %>% 
#   spread(term, estimate) %>% 
#   mutate(alpha = exp(log_alpha))

#Plotting with gglot2
augmented590 <- fitted %>% 
  unnest(augmented590)
# qplot(t, y, data = augmented590, geom = 'point', colour = Strain) +
#   geom_line(aes(y=.fitted))
```

multiple curves PAR photon Dose 590 ->sig dark
```{r}

SolFitsAllfit590dark <-SolFitsAllChoosen %>% 
  filter(Ex_WL == 590) %>% 
  # filter(E_days<10) %>% 
  filter(E_days !=2) %>%
  #filter(E_days !=3) %>%
  select(c(meanSigdark_nm2psii, PARPhotonDose, Photoperiod, Par_ue, Strain, Ex_WL)) %>% 
  mutate(y=meanSigdark_nm2psii) %>% 
  mutate(t=PARPhotonDose) 
  
# Fit the data
fittedark <- SolFitsAllfit590dark %>% 
  nest(-Strain) %>%
  mutate(
    fit = map(data, ~nls(y ~ SSasymp(t, yf, y0, log_alpha), data = .)),
    tidied = map(fit, tidy),
    augmented590dark = map(fit, augment),
  )  

augmented590dark <- fittedark %>% 
  unnest(augmented590dark)
```


mutate for nice plot PAR photon Dose 590 and 445
```{r}
augmented590 <- augmented590 %>% 
  mutate(Ex_WL=Strain) %>% 
      mutate(Ex_WL=case_when(Ex_WL=="PE-rich_127"~590,
         Ex_WL=="PE-rich_048"~590,
        Ex_WL=="PC-rich_056"~590,
         Ex_WL=="PC-rich_077"~590)) %>% 
  mutate(Ex_WL = as.factor(Ex_WL)) %>% 
  mutate(O2=Ex_WL) %>% 
  mutate(O2=case_when(O2==590~21)) %>% 
  mutate(WL=Ex_WL) %>% 
  mutate(WL=case_when(WL==590~"WW")) 

augmented590dark <- augmented590dark %>% 
  mutate(Ex_WL=Strain) %>% 
      mutate(Ex_WL=case_when(Ex_WL=="PE-rich_127"~590,
         Ex_WL=="PE-rich_048"~590,
        Ex_WL=="PC-rich_056"~590,
         Ex_WL=="PC-rich_077"~590)) %>% 
  mutate(Ex_WL = as.factor(Ex_WL)) %>% 
  mutate(O2=Ex_WL) %>% 
  mutate(O2=case_when(O2==590~21)) %>% 
  mutate(WL=Ex_WL) %>% 
  mutate(WL=case_when(WL==590~"WW")) 
```

```{r Delete unused df from environment}
rm(SolFitsAllfit445, SolFitsAllfit590)
```

```{r Final plot, fig.height = 8, fig.width = 8, warning = FALSE}
#Plot sigma vs photondose - mean only replica (shows different days from exp phase)
WL.labs <- c("Excitation (nm)")
names(WL.labs) <- c("WW")
O2.labs <- c("Strain")
names(O2.labs) <- c(21)

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

ggplot(SolFitsAllChoosenExp, aes(x = PARPhotonDose, y = meanSig_nm2psii)) +
  geom_point(aes(x = PARPhotonDose, y = meanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PARPhotonDose, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Par_ue))) +
  geom_line(aes(t, .fitted), show.legend = F, augmented590) +
  #geom_line(aes(t, .fitted), show.legend = F, augmented445) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*"'(nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # scale_y_continuous(breaks=seq(0, 1000, by = 200)) +
  # coord_cartesian(ylim = c(0, 1000)) +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(rows = vars(O2,Strain), cols = vars(WL,Ex_WL), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.44,0.89),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=9))
  
  
ggplot(SolFitsAllChoosenExp, aes(x = PARPhotonDose, y = meanSigdark_nm2psii)) +
  geom_point(aes(x = PARPhotonDose, y = meanSigdark_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PARPhotonDose, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Par_ue))) +
  geom_line(aes(t, .fitted), show.legend = F, augmented590dark) +
  #geom_line(aes(t, .fitted), show.legend = F, augmented445) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(rows = vars(O2,Strain), cols = vars(WL,Ex_WL), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.44,0.89),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=9))
  
  
ggplot(SolFitsAllChoosenExp1s, aes(x = PARPhotonDose, y = meanSig1s_nm2psii)) +
  geom_point(aes(x = PARPhotonDose, y = meanSig1s_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PARPhotonDose, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Par_ue))) +
  # geom_line(aes(t, .fitted), show.legend = F, augmented590dark) +
  #geom_line(aes(t, .fitted), show.legend = F, augmented445) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(label=scientific_10) +
  ggh4x::facet_nested(rows = vars(O2,Strain), cols = vars(WL,Ex_WL), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.44,0.89),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=9))
```




#sig per phyco/chla ratio
Issue - not always pigment based on Olis correspond to Solisense data-> I combine these two df with only selected exp data

Later - come back to OD680data from Multiculti and choose cell/ml (based on pamas corr) corresponding with the same day of sigma and JVPSII!!! Before calculations! Fix this Sylwia!!!!!

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataIn <- file.path("..", "Data", "ProcessedData", fsep = .Platform$file.sep)
```

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

```{r read pigments File}
#df ontained mean OD per day from Multiculti and Abs from Olis spectra for selected nm. Based on this I calculated pigments per mL and per cell (pg/cell)

MCPigmentExpFile <- "../Data/ProcessedData/Baltic_Photoperiod_Processed_PigmentsExp.Rds"
MCPigmentExpFileName <- str_split(string = MCPigmentExpFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
MCPigmentExp <- readRDS(MCPigmentExpFile)  %>%
  ungroup()
```

```{r Joining Solisense and pig exp data}
SolFitsPigmentExp <- SolFitsChoosenExp %>% 
  left_join(., MCPigmentExp, by = c("Run"="Run","CultureID"="ID","Strain"="Strain","InnocDate"="InnocDate","ExpDate"="ExpDate","Par_ue"="Par_ue","Photoperiod"="Photoperiod","O2"="O2","WL"="WL","PARPhotonDose"="PARPhotonDose", "facetsStrain" = "facetsStrain")) 

SolFitsPigmentExp1s <- SolFitsChoosenExp1s %>% 
  left_join(., MCPigmentExp, by = c("Run"="Run","CultureID"="ID","Strain"="Strain","InnocDate"="InnocDate","ExpDate"="ExpDate","Par_ue"="Par_ue","Photoperiod"="Photoperiod","O2"="O2","WL"="WL","PARPhotonDose"="PARPhotonDose")) 
```

```{r Test plot}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsPigmentExp %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
    geom_smooth(aes(x = PhycoChlaRatioExp, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, alpha =0, show.legend = F, method="lm") +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()


SolFitsPigmentExp %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSig_nm2psii, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
    geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Strain))) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsPigmentExp %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSigdark_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigdark_nm2psii - AllsdSigdark_nm2psii, ymax = AllmeanSigdark_nm2psii + AllsdSigdark_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsPigmentExp %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSigdark_nm2psii, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
    geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigdark_nm2psii - AllsdSigdark_nm2psii, ymax = AllmeanSigdark_nm2psii + AllsdSigdark_nm2psii, colour=as.factor(Strain))) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsPigmentExp1s %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsPigmentExp1s %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
    geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Strain))) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw()
```

# Combine PC and PE-rich strains together and filter day 2 and 3 b/c they caused problems

```{r}
SolFitsAllPigmentPC<-SolFitsPigmentExp %>% 
  filter(E_days!=2) %>% 
  filter(E_days!=3) %>% 
  filter(Strain == "PC-rich_056" | Strain == "PC-rich_077") 
SolFitsAllPigmentPC$StrainGroup = "PC-rich"

SolFitsAllPigmentPE<-SolFitsPigmentExp %>% 
  filter(E_days!=2) %>% 
  filter(E_days!=3) %>% 
  filter(Strain == "PE-rich_048" | Strain == "PE-rich_127")  
SolFitsAllPigmentPE$StrainGroup = "PE-rich"
  
SolFitsAllPigmentPCPE<-rbind(SolFitsAllPigmentPC, SolFitsAllPigmentPE)



SolFitsAllPigmentPC1s<-SolFitsPigmentExp1s %>% 
  filter(E_days!=2) %>% 
  filter(E_days!=3) %>% 
  filter(Strain == "PC-rich_056" | Strain == "PC-rich_077") 
SolFitsAllPigmentPC1s$StrainGroup = "PC-rich"

SolFitsAllPigmentPE1s<-SolFitsPigmentExp1s %>% 
  filter(E_days!=2) %>% 
  filter(E_days!=3) %>% 
  filter(Strain == "PE-rich_048" | Strain == "PE-rich_127")  
SolFitsAllPigmentPE1s$StrainGroup = "PE-rich"
  
SolFitsAllPigmentPCPE1s<-rbind(SolFitsAllPigmentPC1s, SolFitsAllPigmentPE1s)
```


# Linear fit per par_ue

```{r linear fit}
SolFitsAllPigmentfitPhycoChlalinear <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  nest(data = -c("Par_ue", "Ex_WL")) |>  
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))

         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )

# Linear_Model_PredictPhycoChla <- SolFitsAllPigmentfitPhycoChlalinear |>
#   unnest(Linear_Model_Predict)


SolFitsAllPigmentfitPhycoChlalineardark <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  nest(data = -c("Par_ue", "Ex_WL")) |>  
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))

         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )



SolFitsAllPigmentfitPhycoChlalinear1s <- SolFitsAllPigmentPCPE1s |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  nest(data = -c("Par_ue", "Ex_WL")) |>  
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))

         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )




SolFitsAllPigmentfitPhycoChlalinearPCPE1s <- SolFitsAllPigmentPCPE1s |>  
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  nest(data = -c("Par_ue", "Ex_WL", "StrainGroup")) |>  
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))

         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )
```

# Create preliminary plot

```{r preliminary plot}
#Plot sig vs phyco/Chla ratio -> linear fit

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAllPigmentfitPhycoChlalinear %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  # scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  # scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y = "Sigma", x = "Total phycobilin content ( pg "~cell^-1~")") +
  #labs(y=expression(paste(sigma,""["PSII"]*"'(nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentfitPhycoChlalineardark %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentfitPhycoChlalinear1s %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE1s) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE1s) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw()
```

# Linear fit Strain

```{r linear fit}
SolFitsAllPigmentfitPhycoChlalinearStrain <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))

         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )




SolFitsAllPigmentfitPhycoChlalineardarkStrain <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |> 
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))

         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )



SolFitsAllPigmentfitPhycoChlalinearStrain1s <- SolFitsAllPigmentPCPE1s |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))

         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )

#xxxxxx


SolFitsAllPigmentfitPhycoChlalinearStrainGroup <- SolFitsAllPigmentPCPE |>  
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("StrainGroup", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )


SolFitsAllPigmentfitPhycoChlalineardarkStrainGroup <- SolFitsAllPigmentPCPE |>  
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("StrainGroup", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |> 
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )


SolFitsAllPigmentfitPhycoChlalinearStrainGroup1s <- SolFitsAllPigmentPCPE1s |>  
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  nest(data = -c("StrainGroup", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  # nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )
```

# Creat preliminary plot

```{r preliminary plot}
#Plot sig vs phyco/Chla ratio -> linear fit
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


SolFitsAllPigmentfitPhycoChlalinearStrain %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  # scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  # scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentfitPhycoChlalineardarkStrain %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain),labeller = label_parsed) +
  theme_bw() 
  
  
SolFitsAllPigmentfitPhycoChlalinearStrain1s %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE1s) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE1s) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
  
  #xxxxxxxx
  
SolFitsAllPigmentfitPhycoChlalineardarkStrainGroup %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(StrainGroup),labeller = label_parsed) +
  theme_bw() 
```

# Linear fit Ex_WL

```{r linear fit}
SolFitsAllPigmentfitPhycoChlalinearExWL <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))

         
         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )



SolFitsAllPigmentfitPhycoChlalineardarkExWL <- SolFitsAllPigmentPCPE |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |> 
  nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))

         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )



SolFitsAllPigmentfitPhycoChlalinearExWL1s <- SolFitsAllPigmentPCPE1s |>  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) |> 
  #nest(data = -c("Strain", "Ex_WL")) |> 
  #nest(data = -c("Par_ue", "Ex_WL")) |>  
  nest(data = -c("Ex_WL")) |> 
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp,
                                                    data = .x))

         ) |>    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance))
         )
```

# Creat preliminary plot

```{r preliminary plot, fig.height = 8, fig.width = 8, warning = FALSE}
#Plot sig vs phyco/Chla ratio -> linear fit
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


SolFitsAllPigmentfitPhycoChlalinearExWL %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  # geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigdark_nm2psii - AllsdSigdark_nm2psii, ymax = AllmeanSigdark_nm2psii + AllsdSigdark_nm2psii, colour=as.factor(Par_ue))) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  ggh4x::facet_nested(cols = vars(Ex_WL), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentfitPhycoChlalineardarkExWL %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +  
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentfitPhycoChlalinearExWL1s %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE1s) + 
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), labeller = label_parsed) +
  theme_bw() 
```



JVPSII

JVPSII vs Chl Turner (ug/L) and JVPSII vs photonDose
I also have data for ChlaugLExp based on Olis corr, but Chla Turner is better
```{r fig.height = 8, fig.width = 8, warning = FALSE}
#colnames(SolFitsAllPigment)

SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = AllmeanTurnerChl_ugL, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  # geom_errorbar(aes(x = ChlapgcellExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  #labs(y=expression(paste(sigma,""["PSII"]*"'(nm"^"2"*")")), x = "Chl" ~italic(a)~ "content ( pg  " ~ cell^-1~")") +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()


SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = cellLExp, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 



SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = AllmeanMDcellsL, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()


SolFitsAllPigment %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()

```




Growth rate vs JVPSII
#meandeltaOD_Lmu_corr ->mean for real replica from MultiCulti
```{r fig.height = 8, fig.width = 8, warning = FALSE}
# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

Plot<-SolFitsAllPigment %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
#   geom_errorbar(aes(x = PhotonDose_value, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Par_ue)), width=4000000, data = . %>% filter(deltaOD_Lmu_se<8.057558e-03), show.legend = F) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  #labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = ""~italic(JV)~""["PSII"]*" ( µmol"~e^-~""~L^-1~""~s^-1~")") +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot
```



JVPSII per Turner Chl ug/L and per cell/L
```{r}
#colnames(SolFitsAllPigment)

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig

SolFitsAllPigmentTurner<-SolFitsAllPigment %>% 
  #Turner
  mutate(meanJVPSII_aLHIIOxbomax_Chl = meanJVPSII_aLHIIOxbomax/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Chl = meanJVPSII_ETRtauav_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Chl = meanJVPSII_ETRqpOxbo_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Chl = meanJVPSII_ETRtauav_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Chl = meanJVPSII_ETRqpOxbo_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  
  #cell per L based on MD Pico
  mutate(meanJVPSII_aLHIIOxbomax_MDcell = meanJVPSII_aLHIIOxbomax/AllmeanMDcellsL) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_MDcell = meanJVPSII_ETRtauav_FoSig/AllmeanMDcellsL) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_MDcell = meanJVPSII_ETRqpOxbo_FoSig/AllmeanMDcellsL) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_MDcell = meanJVPSII_ETRtauav_aLHII_Sig/AllmeanMDcellsL) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_MDcell = meanJVPSII_ETRqpOxbo_aLHII_Sig/AllmeanMDcellsL) %>% 
  
  #cell per L based on pamas corr
  mutate(meanJVPSII_aLHIIOxbomax_Corrcell = meanJVPSII_aLHIIOxbomax/cellLExp) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Corrcell = meanJVPSII_ETRtauav_FoSig/cellLExp) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Corrcell = meanJVPSII_ETRqpOxbo_FoSig/cellLExp) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Corrcell = meanJVPSII_ETRtauav_aLHII_Sig/cellLExp) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell = meanJVPSII_ETRqpOxbo_aLHII_Sig/cellLExp) %>% 
  
 
  #Turner - one value
  mutate(AllmeanJVPSII_aLHIIOxbomax_Chl = AllmeanJVPSII_aLHIIOxbomax/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Chl = AllmeanJVPSII_ETRtauav_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Chl = AllmeanJVPSII_ETRqpOxbo_FoSig/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Chl = AllmeanJVPSII_ETRtauav_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Chl = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig/AllmeanTurnerChl_ugL) %>% 
  
  #cell per L based on MD Pico - one value
  mutate(AllmeanJVPSII_aLHIIOxbomax_MDcell = AllmeanJVPSII_aLHIIOxbomax/AllmeanMDcellsL) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_MDcell = AllmeanJVPSII_ETRtauav_FoSig/AllmeanMDcellsL) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_MDcell = AllmeanJVPSII_ETRqpOxbo_FoSig/AllmeanMDcellsL) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_MDcell = AllmeanJVPSII_ETRtauav_aLHII_Sig/AllmeanMDcellsL) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_MDcell = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig/AllmeanMDcellsL) %>% 
  
  #cell per L based on pamas corr - one value
  mutate(AllmeanJVPSII_aLHIIOxbomax_Corrcell = AllmeanJVPSII_aLHIIOxbomax/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Corrcell = AllmeanJVPSII_ETRtauav_FoSig/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell = AllmeanJVPSII_ETRqpOxbo_FoSig/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell = AllmeanJVPSII_ETRtauav_aLHII_Sig/cellLExp) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig/cellLExp) 

```



Growth rate vs JVPSII per Chl Turner 

```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Chl, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Chl, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
Plot

```


Growth rate vs JVPSII per cell/L based on Pamas correlation

Growth rate vs JVPSII per cell
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
Plot

```


Growth rate vs JVPSII per cell/L based on MD Pico

Growth rate vs JVPSII per cell
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_MDcell, meandeltaOD_Lmu_corr, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllPigmentTurner %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_MDcell, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
Plot

```

Growt rate per day
```{r}
#colnames(SolFitsAllPigmentTurnerDay2)
SolFitsAllPigmentTurnerDay2<-SolFitsAllPigmentTurner %>% 
  # select(-c(Alp1QA, Tau1QA, Alp2QA, Tau2QA, Alp3QA, Tau3QA, WtTau, InvWtTau, C_WtTau, Fmdark, Fodark, Fomin, Fmmax, Sigdark, Sigmax, qp, aLHIIdark, aLHIIminmax, meanSig, sdSig, sdSig_m2psii, deltaOD_LseGrowthFlag, GrowthAmpdeltaODFlag_14days)) %>% 
  mutate(deltaOD_Lmu_corr_day=deltaOD_Lmu_corr*24) %>% 
  mutate(deltaOD_Lmu_se_day=deltaOD_Lmu_se*24) %>% 
  mutate(meandeltaOD_Lmu_corr_day=meandeltaOD_Lmu_corr*24) %>% 
  mutate(sddeltaOD_Lmu_corr_day=sddeltaOD_Lmu_corr*24)

```



calculate JVPSII per day
```{r}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


SolFitsAllPigmentTurnerDay81216<-SolFitsAllPigmentTurnerDay2 %>% 
  filter(Photoperiod !=24) %>% 
  mutate(AllmeanJVPSII_aLHIIOxbomax_Corrcell_day = AllmeanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Corrcell_day = AllmeanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*8/2) %>%
  mutate(meanJVPSII_aLHIIOxbomax_Corrcell_day = meanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Corrcell_day = meanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = meanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = meanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod/2) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*Photoperiod/2) 
  
SolFitsAllPigmentTurnerDay900<-SolFitsAllPigmentTurnerDay2 %>% 
  filter(Photoperiod ==24) %>% 
  mutate(AllmeanJVPSII_aLHIIOxbomax_Corrcell_day = AllmeanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRtauav_FoSig_Corrcell_day = AllmeanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod) %>% 
  mutate(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*Photoperiod) %>%
  mutate(meanJVPSII_aLHIIOxbomax_Corrcell_day = meanJVPSII_aLHIIOxbomax_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRtauav_FoSig_Corrcell_day = meanJVPSII_ETRtauav_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRqpOxbo_FoSig_Corrcell_day = meanJVPSII_ETRqpOxbo_FoSig_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day = meanJVPSII_ETRtauav_aLHII_Sig_Corrcell*3600*Photoperiod) %>% 
  mutate(meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day = meanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell*3600*Photoperiod) 
  

SolFitsAllPigmentTurnerDay<-rbind(SolFitsAllPigmentTurnerDay81216, SolFitsAllPigmentTurnerDay900)
  rm(SolFitsAllPigmentTurnerDay81216, SolFitsAllPigmentTurnerDay900)
```


Growth rate vs JVPSII per cell (pamas corr) per day
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# JVPSII_aLHIIOxbomax
# JVPSII_ETRtauav_FoSig
# JVPSII_ETRqpOxbo_FoSig
# JVPSII_ETRtauav_aLHII_Sig
# JVPSII_ETRqpOxbo_aLHII_Sig


lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_aLHIIOxbomax_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw()
Plot

Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRtauav_FoSig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot

Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_FoSig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot



Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRtauav_aLHII_Sig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Strain)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
    ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot


Plot<-SolFitsAllPigmentTurnerDay %>% 
  filter(Ex_WL==445) %>% 
ggplot() +
  geom_point(aes(AllmeanJVPSII_ETRqpOxbo_aLHII_Sig_Corrcell_day, deltaOD_Lmu_corr_day, colour=as.factor(Par_ue)), alpha = 0.9, size = 3.5, show.legend = T) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
    ggh4x::facet_nested(labeller = label_parsed) +
  theme_bw() 
Plot

```



6.02 x 10^23 electrons per mole

6.02*10e23 = 6.02e+24
6.02e+24/1000000 = 6.02e+18 ->umol e



# Save assembled spectra data set
```{r save Olis}

# saveRDS(SolFitsAllPigmentTurnerDay, file.path(DataOut, paste(Project, "SolFitsAllPigmentTurnerNew.Rds", sep = "_"), fsep = .Platform$file.sep))


```


Set up R codes for Greek letters

\u0391  Α   Greek Capital Letter Alpha
\u0392  Β   Greek Capital Letter Beta
\u0393  Γ   Greek Capital Letter Gamma
\u0394  Δ   Greek Capital Letter Delta
\u0395  Ε   Greek Capital Letter Epsilon
\u0396  Ζ   Greek Capital Letter Zeta
\u0397  Η   Greek Capital Letter Eta
\u0398  Θ   Greek Capital Letter Theta
\u0399  Ι   Greek Capital Letter Iota
\u039A  Κ   Greek Capital Letter Kappa
\u039B  Λ   Greek Capital Letter Lambda
\u039C  Μ   Greek Capital Letter Mu
\u039D  Ν   Greek Capital Letter Nu
\u039E  Ξ   Greek Capital Letter Xi
\u039F  Ο   Greek Capital Letter Omicron
\u03A0  Π   Greek Capital Letter Pi
\u03A1  Ρ   Greek Capital Letter Rho
\u03A3  Σ   Greek Capital Letter Sigma
\u03A4  Τ   Greek Capital Letter Tau
\u03A5  Υ   Greek Capital Letter Upsilon
\u03A6  Φ   Greek Capital Letter Phi
\u03A7  Χ   Greek Capital Letter Chi
\u03A8  Ψ   Greek Capital Letter Psi
\u03A9  Ω   Greek Capital Letter Omega
\u03B1  α   Greek Small Letter alpha
\u03B2  β   Greek Small Letter beta
\u03B3  γ   Greek Small Letter gamma
\u03B4  δ   Greek Small Letter delta
\u03B5  ε   Greek Small Letter epsilon
\u03B6  ζ   Greek Small Letter zeta
\u03B7  η   Greek Small Letter eta
\u03B8  θ   Greek Small Letter theta
\u03B9  ι   Greek Small Letter iota
\u03BA  κ   Greek Small Letter kappa
\u03BB  λ   Greek Small Letter lambda
\u03BC  μ   Greek Small Letter mu
\u03BD  ν   Greek Small Letter nu
\u03BE  ξ   Greek Small Letter xi
\u03BF  ο   Greek Small Letter omicron
\u03C0  π   Greek Small Letter pi
\u03C1  ρ   Greek Small Letter rho
\u03C2  ς   Greek Small Letter final sigma
\u03C3  σ   Greek Small Letter sigma
\u03C4  τ   Greek Small Letter tau
\u03C5  υ   Greek Small Letter upsilon
\u03C6  φ   Greek Small Letter phi
\u03C7  χ   Greek Small Letter chi
\u03C8  ψ   Greek Small Letter psi
\u03C9  ω   Greek Small Letter omega





