---
title: "Process_GrowthCurve"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

This RMD process MultiCulti files and generate growth curve plot.

# Load Libraries and set Project Variables

```{r load libraries} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthCurveData")
DataIn <- file.path("..", "Data", "ImportedData", "ImportedMCData", fsep = .Platform$file.sep)

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read imported MC files

```{r Exported Rmd only first time in session}
list.files(path = DataIn, full.names = TRUE)
```

# Import selected Rds and calculate mean OD from every hour based on ToD and time

## Import Run39

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20211214_PICO_MC247_RUN39_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData39 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run40

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20211223_PICO_MC257_RUN40_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData40 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run43

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20211229_PICO_MC247_RUN43_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData43 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run44

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220107_PICO_MC257_RUN44_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData44 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run45

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220113_PICO_MC247_RUN45_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData45 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run46

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220122_PICO_MC257_RUN46_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData46 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run60

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220405_PICO_MC247_RUN60_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData60 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run62

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220410_PICO_MC257_RUN62_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData62 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run65

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220420_PICO_MC257_RUN65_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData65 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run71

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220507_PICO_MC257_RUN71_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData71 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run74

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20220607_PICO_MC257_RUN74_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData74 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

## Import Run121

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}
MultiCultiFile <- "../Data/ImportedData/ImportedMCData/20230816_PICO_MC257_RUN121_TargetDataMetaFilter.Rds"
MultiCultiFileName <- str_split(string = MultiCultiFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 
MultiCultiData <- readRDS(MultiCultiFile)  

MultiCultiData$ToD = sub("\\..*", "", MultiCultiData$ToD)
MultiCultiData$time = sub("\\..*", "", MultiCultiData$time)

MultiCultiData <- MultiCultiData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) %>% 
  mutate(DeltaOD = OD680-OD720) 
  
MultiCultiData121 <- MultiCultiData %>%   
  group_by(CultureID, Day, ToD, time_h) %>% 
  summarize(Run, CultureID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```
# Merge selected Runs

```{r Mere selected Runs}
MultiCultiDataAll<-rbind(MultiCultiData39, MultiCultiData40, MultiCultiData43, MultiCultiData44, MultiCultiData45, MultiCultiData46, MultiCultiData60, MultiCultiData62, MultiCultiData65, MultiCultiData71, MultiCultiData74, MultiCultiData121)

rm(MultiCultiData39, MultiCultiData40, MultiCultiData43, MultiCultiData44, MultiCultiData45, MultiCultiData46, MultiCultiData60, MultiCultiData62, MultiCultiData65, MultiCultiData71, MultiCultiData74, MultiCultiData121, MultiCultiData)
```

# Create 4 df for vertical lines (coloured as Strain) contained tMaxAG values

```{r create df for vertical lines}
data_vline_056 <- data.frame(Par_ue= c(30, 30, 30, 30, 90, 90, 90, 90, 180, 180, 180, 180, 300, 300, 300, 300, 900, 900, 900, 900),Photoperiod= c(8,12,16,24, 8,12,16,24, 8,12,16,24, 8,12,16,24, 8,12,16, 24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)"), value = c(315.6667, 318.4167, 272.2500, 157.85, 290.9167, 196.7500, 151.2500, 120.27, 219.0000, 148.6667, 124.9167, 110.28, 195.0000, 123.7500, 101.2500, 95.79, 146.0000, 123.16667, 99.58333, 79.66))

data_vline_077 <- data.frame(Par_ue= c(30, 30, 30, 30, 90, 90, 90, 90, 180, 180, 180, 180, 300, 300, 300, 300, 900, 900, 900, 900),Photoperiod= c(8,12,16,24, 8,12,16,24, 8,12,16,24, 8,12,16,24, 8,12,16, 24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)"), value = c(315.1667, 319.0000, 321.0833, 138.78, 291.9167, 223.1667, 153.1667, 120.18, 219.0833, 172.3333, 103.5000, 108.08, 170.9167, 147.9167, 101.5000, 98.36, 145.83333, 147.08333, 123.50000, 107))

data_vline_048 <- data.frame(Par_ue= c(30, 30, 30, 30, 90, 90, 90, 90, 180, 180, 180, 180, 300, 300, 300, 300, 900, 900, 900, 900),Photoperiod= c(8,12,16,24, 8,12,16,24, 8,12,16,24, 8,12,16,24, 8,12,16, 24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)"), value = c(244.2500, 318.0833, 272.4167, 119.35, 316.6667, 222.2500, 153.5833, 103.77, 242.7500, 173.1667, 125.0833, 100.38, 195.9167, 148.8333, 102.1667, 79.20, 146.0833, 161.08333, 147.33333, 94.23))

data_vline_127 <- data.frame(Par_ue= c(30, 30, 30, 30, 90, 90, 90, 90, 180, 180, 180, 180, 300, 300, 300, 300, 900, 900, 900, 900),Photoperiod= c(8,12,16,24, 8,12,16,24, 8,12,16,24, 8,12,16,24, 8,12,16, 24),facetsPar_ue= c("PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})","PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})", "PAR~(µmol~photons~m^{-2}~s^{-1})"),facetsPhotoperiod= c("Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)","Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)", "Photoperiod~(h)"), value = c(293.8333, 321.0833, 323.0833, 154.64, 317.2500, 269.5833, 174.1667, 114.68, 242.6667, 198.0833, 104.5833, 93.32, 218.9167, 173.7500, 102.5833, 93.78, 147.5000, 148.41667, 148.66667, 110))
```

# Add facets labels and change strain name to create plot

```{r add facets labels and change strain names}
MultiCultiDataAll$facetsPar_ue = factor(MultiCultiDataAll$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
MultiCultiDataAll$facetsPhotoperiod = factor(MultiCultiDataAll$WL, labels = c("Photoperiod~(h)"))

MultiCultiDataAll <- MultiCultiDataAll %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 
```

# Create GrowthCurve plot

```{r create GrowthCurve plot, fig.height = 8, fig.width = 8, warning = FALSE}
MultiCultiDataAll %>%
  ggplot() +
  geom_area(aes(x = time_h, y = meanActinic_par_h), size = 0.1, fill = "tan1", alpha = 0.6) +
  geom_line(aes(x = time_h, y = meanOD680_h, colour = as.factor(Strain)), size = 0.7, show.legend = T) +
  geom_vline(data = data_vline_056, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline_077, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline_048, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline_127, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="") +
  labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.085,0.96),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=10))
```

# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r}
rm(data_vline_056, data_vline_077, data_vline_048, data_vline_127)
```

# Save rds for further analysis

```{r save rds}
saveRDS(MultiCultiDataAll, file.path(DataOut, paste(Project, "Imported_GrowtCurve.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```





