---
title: "Process_SolisensePigmentsData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_SolisensePigmentsData.Rmd processes and combines Baltic_Photoperiod_Imported_SolisenseDarkafterLight.Rds and Baltic_Photoperiod_Imported_SolisenseLight.Rds from Data/ImportedData/ImportedSolisenseData folder. This .Rmd generates Baltic_Photoperiod_Processed_SolisensePigmentsExp.Rds (stored in Data/ProcessedData/ProcessedSolisenseData folder) and three plots: Sigma_SupPlot.png, SigmavsPigments590_Plot, SigmavsPigments445_SupPlot.png (stored in Output/Plots folder).

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(caret)
library(reshape2)
library(gcookbook)
library(scales)
library(Cairo) #for greek symbols
library(googledrive)
library(googlesheets4)
library(readxl)
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisenseData")
DataIn <- file.path("..", "Data", "ImportedData", "ImportedSolisenseData", fsep = .Platform$file.sep)

PlotsPath <- file.path("..", "Output", "Plots")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS")
RDSTablePath <- file.path("..", "Output", "TablesRDS")
```

# List and read Imported_Solisense RDS

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

# This RDS contained only data from corresponding growth light 
# Also, conteined mean sig - mean for replica measured on the same day

```{r read ProcessFile Sol}
SolisenseFile <- "../Data/ImportedData/ImportedSolisenseData/Baltic_Photoperiod_Imported_SolisenseLight.Rds"  

SolisenseFileName <- str_split(string = SolisenseFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

SolFits <- readRDS(SolisenseFile)  %>%
  ungroup()
```

# This RDS contained only sigma in 1s of dark after corresponding light (it caused problems when I tried to combain them with sig in the light)
# Also, conteined mean for sig1s - mean for replica measured on the same day

```{r read ProcessFile Sol1s}
Solisense1sFile <- "../Data/ImportedData/ImportedSolisenseData/Baltic_Photoperiod_Imported_SolisenseDarkafterLight.Rds"

Solisense1sFileName <- str_split(string = Solisense1sFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

SolFits1s <- readRDS(Solisense1sFile)  %>%
  ungroup()
```


```{r Preparing df for further analysis}
SolFits <-SolFits %>% 
  select(c(SampleID, Run, Strain, ExpDate, Par_ue, Photoperiod, MC, Tube, O2, WL, LightShape, ExpEndDate, PARPhotonDose_day, FilenameSolisense, ObsDate, ObsTime, Ex_WL, ActPAR, LR_s, nm445, nm590, nm445Corr, nm590Corr, ActPARCorr, Sig, Sig_nm2psii, Sigdark, Sigdark_nm2psii, ActPARCorr_photonsm2s, FoOxbo, qpOxbo,  JVPSII_aLHIIOxbomax, JVPSII_ETRtauav_FoSig, JVPSII_ETRqpOxbo_FoSig, JVPSII_ETRtauav_aLHII_Sig, JVPSII_ETRqpOxbo_aLHII_Sig, E_days, Time_h)) %>% 
  filter(Strain=="BA127R"| Strain=="BA48R"| Strain=="BA56G"| Strain=="BA77G") %>% 
  filter(WL=="WW") %>% 
  filter(O2==21) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 
SolFits$facetsPhotonDose_day = factor(SolFits$WL, labels = c("PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})"))
SolFits$facetsExcitation = factor(SolFits$WL, labels = c("Excitation~(nm)"))
SolFits$facetsStrain = factor(SolFits$WL, labels = c("Strain"))


SolFits1s <-SolFits1s %>% 
  select(c(SampleID, Run, Strain, ExpDate, Par_ue, Photoperiod, MC, Tube, O2, WL, LightShape, ExpEndDate, PARPhotonDose_day, FilenameSolisense, ObsDate, ObsTime, Ex_WL, ActPAR, LR_s, nm445, nm590, nm445Corr, nm590Corr, ActPARCorr, Sig1s, Sig1s_nm2psii, ActPARCorr_photonsm2s, E_days, Time_h)) %>% 
  filter(Strain=="BA127R"| Strain=="BA48R"| Strain=="BA56G"| Strain=="BA77G") %>% 
  filter(WL=="WW") %>% 
  filter(O2==21) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 
SolFits1s$facetsPhotonDose_day = factor(SolFits1s$WL, labels = c("PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})"))
SolFits1s$facetsExcitation = factor(SolFits1s$WL, labels = c("Excitation~(nm)"))
SolFits1s$facetsStrain = factor(SolFits1s$WL, labels = c("Strain"))
```

# Filter unrevelant data and outliers

```{r filter outliers}
# #Filter one unrevelant data point at 445nm, 16h, 900uE
SolFitsAll445<-SolFits %>%
  filter(Ex_WL == 445) %>%
  filter(Sig<250) 
SolFitsAll590<-SolFits %>%
  filter(Ex_WL == 590)
SolFits<-rbind(SolFitsAll445,SolFitsAll590)
  rm(SolFitsAll445,SolFitsAll590)
  
SolFitsAll4451s<-SolFits1s %>%
  filter(Ex_WL == 445) %>%
  filter(Sig1s<250) 
SolFitsAll5901s<-SolFits1s %>%
  filter(Ex_WL == 590)
SolFits1s<-rbind(SolFitsAll4451s,SolFitsAll5901s)
  rm(SolFitsAll4451s,SolFitsAll5901s)  
```

# Create preliminary plots 

```{r preliminary plot}
SolFits %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = Sig, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  facet_grid(rows = vars(Ex_WL), cols = vars(Photoperiod)) +
  theme_bw()
```

# Load tmaxAG catalog and create 4 df for vertical lines (coloured as Strain) contained tMaxAG values

```{r}
gs4_deauth()
tmaxAG<- read_sheet("https://docs.google.com/spreadsheets/d/1ksY7xlg9wOsICOBRmZkHPKdd9KOislNwPDzyuJ3UIUI/edit#gid=0")
as.data.frame(tmaxAG)
tmaxAG <- tmaxAG

tmaxAG<-tmaxAG %>% 
  mutate(Par_ue = as.numeric(Par_ue)) %>%
  mutate(Photoperiod = as.numeric(Photoperiod)) %>%
  mutate(tMaxAG = as.numeric(tMaxAG)) %>%
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))
```

```{r select revelant columns}
tMaxAGLines_056<-tmaxAG %>% 
  filter(Strain == "PC-rich_056") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_077<-tmaxAG %>% 
  filter(Strain == "PC-rich_077") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_048<-tmaxAG %>% 
  filter(Strain == "PE-rich_048") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_127<-tmaxAG %>% 
  filter(Strain == "PE-rich_127") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
```

# Choose only exp data for sigma and JVPSII in the corresponding light

```{r choose only exp data}
O1 <- SolFits %>%
  filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 900) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days <= 4)

O2 <- SolFits %>%
  filter(Par_ue == 90 | Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days < 9)

O3 <- SolFits %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 4)

O4 <- SolFits %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 14)

O5 <- SolFits %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=14)
  
O6 <- SolFits %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days <=14)

O7 <- SolFits %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days <=10)

O8 <- SolFits %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=10)

O9 <- SolFits %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=7)

O10 <- SolFits %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days <= 8)

SolFitsExp <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)
```


# Choose only Stationary data for sigma and JVPSII in the corresponding light

```{r choose only St data}
O1 <- SolFits %>%
  filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 900) %>%
  filter(Photoperiod == 24) %>%
  filter(E_days > 4)

O2 <- SolFits %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >14)
  
O3 <- SolFits %>%
  filter(Par_ue == 90) %>%
  filter(Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >10)

O4 <- SolFits %>%
  filter(Par_ue == 180 | Par_ue == 300) %>%
  filter(Photoperiod == 8 | Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >10)

O5 <- SolFits %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 16) %>% 
  filter(E_days >7)

SolFitsSt <-rbind(O1, O2, O3, O4, O5)

rm(O1, O2, O3, O4, O5)
```



# Choose only exp data for sigma at 1s after corresponding light

```{r choose only exp data for Sig 1s}
O1 <- SolFits1s %>%
  filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 900) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days <= 4)

O2 <- SolFits1s %>%
  filter(Par_ue == 90 | Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days < 9)

O3 <- SolFits1s %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 4)

O4 <- SolFits1s %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 14)

O5 <- SolFits1s %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=14)
  
O6 <- SolFits1s %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days <=14)

O7 <- SolFits1s %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days <=10)

O8 <- SolFits1s %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=10)

O9 <- SolFits1s %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=7)

O10 <- SolFits1s %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days <= 8)

SolFitsExp1s <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)
```


# Choose only Stationary data for sigma at 1s after corresponding light

```{r choose only St data}
O1 <- SolFits1s %>%
  filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 900) %>%
  filter(Photoperiod == 24) %>%
  filter(E_days > 4)

O2 <- SolFits1s %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >14)
  
O3 <- SolFits1s %>%
  filter(Par_ue == 90) %>%
  filter(Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >10)

O4 <- SolFits1s %>%
  filter(Par_ue == 180 | Par_ue == 300) %>%
  filter(Photoperiod == 8 | Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >10)

O5 <- SolFits1s %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 16) %>% 
  filter(E_days >7)

SolFitsSt1s <-rbind(O1, O2, O3, O4, O5)

rm(O1, O2, O3, O4, O5)
```






# Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFits %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4") +
  geom_vline(data = tMaxAGLines_077, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1") +
  geom_vline(data = tMaxAGLines_048, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = tMaxAGLines_127, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsExp %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4") +
  geom_vline(data = tMaxAGLines_077, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1") +
  geom_vline(data = tMaxAGLines_048, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = tMaxAGLines_127, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsSt %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4") +
  geom_vline(data = tMaxAGLines_077, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1") +
  geom_vline(data = tMaxAGLines_048, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = tMaxAGLines_127, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
```
# Combine Exp and St data

```{r}
  SolFitsExp$Phase <- 'Exponential'
  SolFitsExp1s$Phase <- 'Exponential'
  
  SolFitsSt$Phase <- 'Pre-stationary'
  SolFitsSt1s$Phase <- 'Pre-stationary'
  
  SolFitsExpSt <-rbind(SolFitsExp, SolFitsSt)
  SolFitsExpSt1s <-rbind(SolFitsExp1s, SolFitsSt1s)
  
  rm(SolFitsExp, SolFitsSt, SolFitsExp1s, SolFitsSt1s, tmaxAG, tMaxAGLines_056, tMaxAGLines_077, tMaxAGLines_048, tMaxAGLines_127, SolFits, SolFits1s)
```

#Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsExpSt %>%
  # filter(E_days!=2) %>% 
  filter(Ex_WL==445) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)),  alpha = 0.8, size = 3, show.legend = T) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab2) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab3) +
  ggh4x::facet_nested(cols = vars(Phase), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```

# Calculate Sigma mean from 3 replica measured on the same day
# 6 replica b/c 3 replica * 2 values ("up" and "down")

```{r calculate Sigma mean from 3 replica measured on the same day}
SolFitsExpSt <- SolFitsExpSt %>%
  group_by(SampleID, Ex_WL, ObsDate, Par_ue, Photoperiod, WL, O2, Phase) %>%
  
  summarize(SampleID, Ex_WL, FilenameSolisense, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, Phase,  PARPhotonDose_day, ObsDate, ObsTime, Sig, Sig_nm2psii, ActPARCorr_photonsm2s, Sigdark_nm2psii, FoOxbo, qpOxbo, JVPSII_aLHIIOxbomax, JVPSII_ETRtauav_FoSig, JVPSII_ETRqpOxbo_FoSig, JVPSII_ETRtauav_aLHII_Sig, JVPSII_ETRqpOxbo_aLHII_Sig, facetsPhotonDose_day, facetsExcitation, facetsStrain,
            meanSig_nm2psii = mean(Sig_nm2psii),
            sdSig_nm2psii = sd(Sig_nm2psii),
            meanSigdark_nm2psii = mean(Sigdark_nm2psii),
            sdSigdark_nm2psii = sd(Sigdark_nm2psii)) %>%
  ungroup()

SolFitsExpSt<- SolFitsExpSt %>%
group_by(SampleID) %>%
  arrange(ObsDate) %>%
  mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
ungroup()

SolFitsExpSt<- SolFitsExpSt %>%
  mutate(Time_h = E_days*24)
```

# Calculate Sigma1s mean from 3 replica measured on the same day
# 6 replica b/c 3 replica * 2 values ("up" and "down")

```{r calculate Sigma1s mean from 3 replica measured on the same day}
SolFitsExpSt1s <- SolFitsExpSt1s %>%
  group_by(SampleID, Ex_WL, ObsDate, Par_ue, Photoperiod, WL, O2, Phase) %>%
  
  summarize(SampleID, Ex_WL, FilenameSolisense, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, Phase,  PARPhotonDose_day, ObsDate, ObsTime, Sig1s, Sig1s_nm2psii, ActPARCorr_photonsm2s, facetsPhotonDose_day, facetsExcitation, facetsStrain,
            meanSig1s_nm2psii = mean(Sig1s_nm2psii),
            sdSig1s_nm2psii = sd(Sig1s_nm2psii)) %>%
  ungroup()

SolFitsExpSt1s<- SolFitsExpSt1s %>%
group_by(SampleID) %>%
  arrange(ObsDate) %>%
  mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
ungroup()

SolFitsExpSt1s<- SolFitsExpSt1s %>%
  mutate(Time_h = E_days*24)
```

Make "one big - All" mean to combine all days (divided by Exp and St) and all replica when samples were measured 
(This give me only one value of JVPSII for further growth vs JVPSII plot and sig plot as well)


# Calculate Sigma mean from all data measured on Exp or St phase 
# Usually Allmean contains 12 replica - two different days of measurements * 3 replica * 2 values (up and down)

```{r calculate Sigma mean from exp phase}

SolFitsExpSt<-SolFitsExpSt %>% 
  group_by(Strain, Ex_WL, Par_ue, Photoperiod, WL, O2, Phase) %>%
  
  summarize(SampleID, Ex_WL, FilenameSolisense, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, Phase,  PARPhotonDose_day, ObsDate, ObsTime, Sig, Sig_nm2psii, meanSig_nm2psii, sdSig_nm2psii, ActPARCorr_photonsm2s, Sigdark_nm2psii, meanSigdark_nm2psii, sdSigdark_nm2psii, FoOxbo, qpOxbo, JVPSII_aLHIIOxbomax, JVPSII_ETRtauav_FoSig, JVPSII_ETRqpOxbo_FoSig, JVPSII_ETRtauav_aLHII_Sig, JVPSII_ETRqpOxbo_aLHII_Sig, facetsPhotonDose_day, facetsExcitation, facetsStrain, E_days, Time_h,
              
            #  AllmeanJVPSII_aLHIIOxbomax= mean(JVPSII_aLHIIOxbomax),
            #  AllmeanJVPSII_ETRtauav_FoSig= mean(JVPSII_ETRtauav_FoSig),
            #  AllmeanJVPSII_ETRqpOxbo_FoSig= mean(JVPSII_ETRqpOxbo_FoSig),
            # AllmeanJVPSII_ETRtauav_aLHII_Sig = mean(JVPSII_ETRtauav_aLHII_Sig),
            #  AllmeanJVPSII_ETRqpOxbo_aLHII_Sig= mean(JVPSII_ETRqpOxbo_aLHII_Sig),
            AllmeanSig_nm2psii = mean(Sig_nm2psii),
            AllsdSig_nm2psii = sd(Sig_nm2psii),
            AllmeanSigdark_nm2psii = mean(Sigdark_nm2psii),
            AllsdSigdark_nm2psii = sd(Sigdark_nm2psii)) %>%
  ungroup()
```

# Filter otliers to calculate exponential decay function

```{r filter outliers (5 data points from Exp)}
Sol1<-SolFitsExpSt %>% #keeping all data
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue !=900) %>% 
  filter(Strain=="PE-rich_048") 
Sol2<-SolFitsExpSt %>% #keeping all data
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue !=900) %>% 
  filter(Strain=="PC-rich_077") 

Sol3<-SolFitsExpSt %>% #keeping all data except <180 (one data point)
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue !=900) %>% 
  filter(Strain=="PC-rich_056") %>% 
  filter(Sig>180)

Sol4<-SolFitsExpSt %>% #removing one data point
  filter(Phase == "Exponential") %>%
  filter(Ex_WL==590) %>%
  filter(Par_ue ==30) %>%
  filter(Strain=="PE-rich_127") %>%
  filter(Sig>310)

Sol5<-SolFitsExpSt %>%
  filter(Phase == "Exponential") %>% #removing 3 data points
  filter(Ex_WL==590) %>%
  filter(Par_ue ==300 | Par_ue ==180 | Par_ue ==90) %>%
  filter(Strain=="PE-rich_127") %>%
  filter(Sig>200)

Sol6<-SolFitsExpSt %>% # keeping all except 2 data points
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue ==900) %>% 
  filter(Sig<600)

Sol7<-SolFitsExpSt %>% 
  filter(Ex_WL==445) 

Sol8<-SolFitsExpSt %>% 
  filter(Phase == "Pre-stationary") %>% 
  filter(Strain=="PC-rich_056") %>% 
  filter(Par_ue ==30 | Par_ue ==300) 

Sol9<-SolFitsExpSt %>% 
  filter(Phase == "Pre-stationary") %>% 
  filter(Strain=="PC-rich_056") %>% 
  filter(Par_ue ==180 | Par_ue ==90) 

Sol10<-SolFitsExpSt %>% 
  filter(Phase == "Pre-stationary") %>% 
  filter(Par_ue !=900) %>% 
  filter(Strain=="PE-rich_048") %>% 
  filter(Sig>290)
Sol11<-SolFitsExpSt %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Par_ue ==900) %>%
  filter(Strain=="PE-rich_048")
Sol12<-SolFitsExpSt %>% 
  filter(Phase == "Pre-stationary") %>% 
  filter(Strain=="PE-rich_127")
Sol13<-SolFitsExpSt %>% 
  filter(Phase == "Pre-stationary") %>% 
  filter(Strain=="PC-rich_077") %>% 
  filter(Sig<490)

SolFitsExpFitAll<-rbind(Sol1, Sol2, Sol3, Sol4, Sol5, Sol6, Sol7, Sol8, Sol9, Sol10, Sol11, Sol12, Sol13)

rm(Sol1, Sol2, Sol3, Sol4, Sol5, Sol6, Sol7, Sol8, Sol9, Sol10, Sol11, Sol12, Sol13)

```

# Create plot to check data before and after filtering outliers

```{r checking data before and after filtering outliers}
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsExpSt %>% 
  filter(Ex_WL == 590) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = Sig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  # geom_errorbar(aes(x = PARPhotonDose_day, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Phase), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 

SolFitsExpFitAll %>% 
  filter(Ex_WL == 590) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = Sig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  # geom_errorbar(aes(x = PARPhotonDose_day, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Phase), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```

# Fit the data to exponential decays

```{r fit the data to exponential decays, echo=FALSE, warning = FALSE}

SolFitsExpFit590Clean <-SolFitsExpFitAll %>% 
  drop_na(Sig_nm2psii) %>%
  filter(Ex_WL == 590) %>% 
  select(c(Sig_nm2psii, PARPhotonDose_day, Strain, Phase, O2, WL)) 

# Fit the data
fitted <- SolFitsExpFit590Clean %>% 
  nest(-c(Strain, Phase, O2, WL)) %>%
  mutate(
    fit = map(data, ~nls(Sig_nm2psii ~ SSasymp(PARPhotonDose_day, yf, y0, log_alpha), data = .)),
    tidied = map(fit, tidy),
    augmented590 = map(fit, augment))  

# Produce a table of fit parameters: y0, yf, alpha
fitted_Param590<-fitted %>% 
  unnest(tidied) %>% 
  select(Strain, Phase, term, estimate) %>% 
pivot_wider(., names_from = c(term), values_from = c(estimate)) %>% 
  mutate(alpha = exp(log_alpha))
```

```{r unnest, preparing df to preparing final plot, echo=FALSE, warning = FALSE}
augmented590<-fitted  %>%
  unnest(augmented590) %>%
  select(c(Strain, Phase, O2, WL, PARPhotonDose_day,Sig_nm2psii, .fitted)) 
```

# Create Sigma plot at 590

```{r create Sigma plot, fig.height = 8, fig.width = 8, warning = FALSE}

data_text_y0Exp<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('y0 = 7.4', 'y0 = 5.8', 'y0 = 8.5', 'y0 = 7.9'))
data_text_yfExp<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('yf = 3.1', 'yf = 1.5', 'yf = 3.8', 'yf = 3.7'))
data_text_lambdaExp<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('\u03BB = 3.3', '\u03BB = 2.6', '\u03BB = 1.9', '\u03BB = 3.3'))

data_text_y0St<- data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('y0 = 7.1', '  y0 = 10.4', 'y0 = 8.8', 'y0 = 9.5'))
data_text_yfSt<- data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('yf = 0.9', 'yf = 1.5', 'yf = 3.0', 'yf = 2.3'))
data_text_lambdaSt<- data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('\u03BB = 6.4', '\u03BB = 6.2', '\u03BB = 5.3', '\u03BB = 6.6'))

WL.labs <- c("Phase of growth")
names(WL.labs) <- c("WW")
O2.labs <- c("Strain")
names(O2.labs) <- c(21)

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsExpFitAll590<-SolFitsExpFitAll %>% 
  filter(Ex_WL==590) 

ggplot(SolFitsExpFitAll590, aes(x = PARPhotonDose_day, y = Sig_nm2psii)) +
  geom_point(aes(x = PARPhotonDose_day, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_point(aes(x = PARPhotonDose_day, y = Sig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, show.legend = F) +
  geom_errorbar(aes(x = PARPhotonDose_day, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue)), width=0, size=0.3, show.legend = F) +
  geom_line(aes(PARPhotonDose_day, .fitted), colour = "gray20", size=0.7, show.legend = F, augmented590) +
  geom_text(data=data_text_y0Exp, aes(x=75000000, y=10, label=label), size=3.5) +
  geom_text(data=data_text_yfExp, aes(x=75000000, y=8.5, label=label), size=3.5) +
  geom_text(data=data_text_lambdaExp, aes(x=75000000, y=7, label=label), size=3.5) +
  
  geom_text(data=data_text_y0St, aes(x=7500000, y=10, label=label), size=3.5) +
  geom_text(data=data_text_yfSt, aes(x=7500000, y=8.5, label=label), size=3.5) +
  geom_text(data=data_text_lambdaSt, aes(x=7500000, y=7, label=label), size=3.5) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*" quanta"^"-1"*")")), x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(breaks=seq(0, 60000000, by = 30000000), label=scientific_10) +
  scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  coord_cartesian(xlim = c(0, 80000000), ylim = c(0, 11)) +
  ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(WL, Phase), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.93,0.9),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        legend.title = element_blank(),
        legend.text = element_text(size=9))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("Sigma590_SupPlot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```


# Calculated Anova and Tukey test from exponential decay parameters

```{r calculated statistics}

Sig590Stats<-fitted_Param590
Sig590Stats2<-rbind(Sig590Stats, Sig590Stats)
Sig590Stats2$Strain <- factor(Sig590Stats2$Strain)
Sig590Stats2$Phase <- factor(Sig590Stats2$Phase)

# Two-way Anova
model<-aov(y0~Strain*Phase, data=Sig590Stats2)
AnovaTest_Sig590_y0<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
#TukeyHSDTest_Sig590_y0<-TukeyHSD(model, which = c("Strain", "Phase"))
AnovaTest_Sig590_y0$Parameter <- 'y0'

model<-aov(yf~Strain*Phase, data=Sig590Stats2)
AnovaTest_Sig590_yf<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
#TukeyHSDTest_Sig590_yf<-TukeyHSD(model, which = c("Strain", "Phase"))
AnovaTest_Sig590_yf$Parameter <- 'yf'

model<-aov(alpha~Strain*Phase, data=Sig590Stats2)
AnovaTest_Sig590_alpha<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
#TukeyHSDTest_Sig590_alpha<-TukeyHSD(model, which = c("Strain", "Phase"))
AnovaTest_Sig590_alpha$Parameter <- 'alpha'

AnovaTest_Sig590_Param<-rbind(AnovaTest_Sig590_y0, AnovaTest_Sig590_yf, AnovaTest_Sig590_alpha)

  rm(AnovaTest_Sig590_y0, AnovaTest_Sig590_yf, AnovaTest_Sig590_alpha, Sig590Stats, Sig590Stats2, model)
```

# Save RDS that create stats and tables

```{r}
saveRDS(AnovaTest_Sig590_Param, file.path(RDSTablePath, paste(Project, "Sig590_Anova.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

# saveRDS(TukeyHSDTest_y0_alpha, file.path(RDSTablePath, paste(Project, "GSTukey_y0.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


```{r}
SolFitsExpFit445Clean <-SolFitsExpFitAll %>% 
  drop_na(Sig_nm2psii) %>%
  filter(Ex_WL == 445) %>% 
  select(c(Sig_nm2psii, PARPhotonDose_day, Strain, Phase, O2, WL)) 

# Fit the data
fitted <- SolFitsExpFit445Clean %>% 
  nest(-c(Strain, Phase, O2, WL)) %>%
  mutate(Linear_Model = map(data, ~lm(Sig_nm2psii ~ PARPhotonDose_day, data = .))) %>% 
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))   

augmented445<-fitted %>% 
  unnest(Linear_Model_Predict) %>% 
  select(c(Strain, Phase, O2, WL, PARPhotonDose_day,Sig_nm2psii, .fitted)) 
```

# Create Sigma plot at 445

```{r create Sigma plot, fig.height = 8, fig.width = 8, warning = FALSE}

WL.labs <- c("Phase of growth")
names(WL.labs) <- c("WW")
O2.labs <- c("Strain")
names(O2.labs) <- c(21)

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsExpFitAll445<-SolFitsExpFitAll %>% 
  filter(Ex_WL==445) 

ggplot(SolFitsExpFitAll445, aes(x = PARPhotonDose_day, y = Sig_nm2psii)) +
  geom_point(aes(x = PARPhotonDose_day, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_point(aes(x = PARPhotonDose_day, y = Sig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, show.legend = F) +
  geom_errorbar(aes(x = PARPhotonDose_day, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue)), width=0, size=0.3, show.legend = F) +
  geom_line(aes(PARPhotonDose_day, .fitted), colour = "gray20", size=0.7, show.legend = F, augmented445) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*" quanta"^"-1"*")")), x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(breaks=seq(0, 60000000, by = 30000000), label=scientific_10) +
  scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  coord_cartesian(xlim = c(0, 80000000), ylim = c(0, 10)) +
  ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(WL, Phase), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.93,0.9),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        legend.title = element_blank(),
        legend.text = element_text(size=9))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("Sigma445_SupPlot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```

# Save RDS that create plot

```{r}
saveRDS(SolFitsExpFitAll, file.path(RDSPlotPath, paste(Project, "Plot_Sigma_1.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(augmented590, file.path(RDSPlotPath, paste(Project, "Plot_Sigma_2.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(fitted_Param590, file.path(RDSPlotPath, paste(Project, "Plot_Sigma_3.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Removed unneccessary df from the environment

```{r}
rm(SolFitsExpSt445, fitted, SolFitsExpFit590Clean, SolFitsExpFit590, SolFitsExpFitAll, SolFitsExpStPlot, fitted_Param, data_text_lambdaExp, data_text_y0Exp, data_text_yfExp, data_text_lambdaSt, data_text_y0St, data_text_yfSt)
```

# Sig per phyco/chla ratio

Issue - not always pigment based on Olis correspond to Solisense data-> I combine these two df with only selected exp data

Later - come back to OD680data from Multiculti and choose cell/ml (based on pamas corr) corresponding with the same day of sigma and JVPSII!!! Before calculations! Fix this Sylwia!!!!!

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataIn <- file.path("..", "Data", "ProcessedData", "ProcessedPigmentsData", fsep = .Platform$file.sep)
```

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

```{r read pigments File}
#df ontained mean OD per day from Multiculti and Abs from Olis spectra for selected nm. Based on this I calculated pigments per mL and per cell (pg/cell)

MCPigmentExpFile <- "../Data/ProcessedData/ProcessedPigmentsData/Baltic_Photoperiod_Processed_PigmentsExp.Rds"
MCPigmentExpFileName <- str_split(string = MCPigmentExpFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
MCPigmentExp <- readRDS(MCPigmentExpFile)  %>%
  ungroup()
```

# znalezc sposob, zeby polaczyc dni ale z buforem - bo nie zawsze pasuje 1:1., wrocic do rmd i wyciagnac jedna wartosc dla St!!!! bo inaczej za duzo wartosci, albo zrobic srednia dla exp i srednia dla st! z kilku dni, zamiast wybioerac jedna wartosc.

```{r Joining Solisense and pig exp data}
SolFitsPigmentExp <- SolFitsExpSt %>% 
  left_join(., MCPigmentExp, by = c("Strain"="Strain","Par_ue"="Par_ue","Photoperiod"="Photoperiod")) 
  # left_join(., MCPigmentExp, by = c("Strain"="Strain","Par_ue"="Par_ue","Photoperiod"="Photoperiod", "Run"="Run", "WL"="WL", "O2"="O2", "Phase"="Phase", "PARPhotonDose_day"="PARPhotonDose_day", "facetsStrain" = "facetsStrain", "E_days"="E_days", "Time_h"="Time_h", "ExpDate"="ExpDate")) 

SolFitsPigmentExp1s <- SolFitsExpSt1s %>% 
  left_join(., MCPigmentExp, by = c("Strain"="Strain","Par_ue"="Par_ue","Photoperiod"="Photoperiod")) 

#rm(SolFitsExpSt, SolFitsExpSt1s, MCPigmentExp)
```

# Create preliminary plots

```{r preliminary plots}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsPigmentExp %>% 
  filter(Ex_WL==590) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  # geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()

SolFitsPigmentExp %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  # geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()


SolFitsPigmentExp %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSig_nm2psii, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Strain))) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsPigmentExp %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSigdark_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigdark_nm2psii - AllsdSigdark_nm2psii, ymax = AllmeanSigdark_nm2psii + AllsdSigdark_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsPigmentExp %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSigdark_nm2psii, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigdark_nm2psii - AllsdSigdark_nm2psii, ymax = AllmeanSigdark_nm2psii + AllsdSigdark_nm2psii, colour=as.factor(Strain))) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(facetsExcitation, Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsPigmentExp1s %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = Sig1s_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  # geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Par_ue))) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsPigmentExp1s %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = Sig1s_nm2psii, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
    # geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Strain))) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw()
```

# Combine PC and PE-rich strains together

```{r combine PC and PE-rich strains}
SolFitsAllPigmentPC<-SolFitsPigmentExp %>% 
  filter(Strain == "PC-rich_056" | Strain == "PC-rich_077") 
SolFitsAllPigmentPC$StrainGroup = "PC-rich"
SolFitsAllPigmentPE<-SolFitsPigmentExp %>% 
  filter(Strain == "PE-rich_048" | Strain == "PE-rich_127")  
SolFitsAllPigmentPE$StrainGroup = "PE-rich"

SolFitsAllPigmentPCPE<-rbind(SolFitsAllPigmentPC, SolFitsAllPigmentPE)
rm(SolFitsAllPigmentPC, SolFitsAllPigmentPE)


SolFitsAllPigmentPC1s<-SolFitsPigmentExp1s %>% 
  filter(Strain == "PC-rich_056" | Strain == "PC-rich_077") 
SolFitsAllPigmentPC1s$StrainGroup = "PC-rich"
SolFitsAllPigmentPE1s<-SolFitsPigmentExp1s %>% 
  filter(Strain == "PE-rich_048" | Strain == "PE-rich_127")  
SolFitsAllPigmentPE1s$StrainGroup = "PE-rich"
  
SolFitsAllPigmentPCPE1s<-rbind(SolFitsAllPigmentPC1s, SolFitsAllPigmentPE1s)
rm(SolFitsAllPigmentPC1s, SolFitsAllPigmentPE1s, SolFitsPigmentExp1s)
```

# Filtering data measured from log and very early exponential phase of growth

```{r filtering data from log phase}
SolFitsAllPigmentPCPE<-SolFitsAllPigmentPCPE %>%
  filter(E_days!=2) %>%
  filter(E_days!=3)

SolFitsAllPigmentPCPE1s<-SolFitsAllPigmentPCPE1s %>%
  filter(E_days!=2) %>%
  filter(E_days!=3)
```

# Linear fit per Ex_WL

```{r linear fit}
SolFitsAllPigmentfitPhycoChlalinearExWL <- SolFitsAllPigmentPCPE %>%   
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL)) %>%  
  nest(data = -c("Ex_WL")) %>%  
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))


SolFitsAllPigmentfitPhycoChlalineardarkExWL <- SolFitsAllPigmentPCPE %>%   
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL)) %>% 
  nest(data = -c("Ex_WL")) %>% 
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))


SolFitsAllPigmentfitPhycoChlalinearExWL1s <- SolFitsAllPigmentPCPE1s %>%  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) %>% 
  nest(data = -c("Ex_WL")) %>% 
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))
```

# Creat preliminary plot

```{r preliminary plot, warning = FALSE}
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAllPigmentfitPhycoChlalinearExWL %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  # geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigdark_nm2psii - AllsdSigdark_nm2psii, ymax = AllmeanSigdark_nm2psii + AllsdSigdark_nm2psii, colour=as.factor(Par_ue))) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentfitPhycoChlalineardarkExWL %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +  
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentfitPhycoChlalinearExWL1s %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE1s) + 
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), labeller = label_parsed) +
  theme_bw() 
```

# Linear fit per par_ue

```{r linear fit}

SolFitsAllPigmentfitPhycoChlalinear <- SolFitsAllPigmentPCPE %>%   
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL)) %>%  
  nest(data = -c("Par_ue", "Ex_WL")) %>%   
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))


SolFitsAllPigmentfitPhycoChlalineardark <- SolFitsAllPigmentPCPE %>%   
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL)) %>%  
  nest(data = -c("Par_ue", "Ex_WL")) %>%   
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))


SolFitsAllPigmentfitPhycoChlalinear1s <- SolFitsAllPigmentPCPE1s %>%   
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) %>% 
  nest(data = -c("Par_ue", "Ex_WL")) %>%   
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))


SolFitsAllPigmentfitPhycoChlalinearPCPE1s <- SolFitsAllPigmentPCPE1s %>%   
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL)) %>%  
  nest(data = -c("Par_ue", "Ex_WL", "StrainGroup")) %>%  
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))
```

# Create preliminary plot

```{r preliminary plot}

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAllPigmentfitPhycoChlalinear %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  #labs(y=expression(paste(sigma,""["PSII"]*"'(nm"^"2"*")")), x = "Total phycobilins/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentfitPhycoChlalineardark %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentfitPhycoChlalinear1s %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE1s) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE1s) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw()
```

# Combine 590 sigma and sigma in the dark

```{r}
SolFitsAllPigmentPCPE$facetsPar_ue = factor(SolFitsAllPigmentPCPE$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
SolFitsAllPigmentPCPE$facetsExcitation590 = factor(SolFitsAllPigmentPCPE$O2, labels = c("Excitation~590~nm"))

SolFitsAllPigmentPCPEMerge1<-SolFitsAllPigmentPCPE %>% 
  select(c(Strain, Ex_WL, WL, Par_ue, Photoperiod, Sig_nm2psii, AllmeanSig_nm2psii, AllsdSig_nm2psii, PhycoChlaRatioExp, facetsPar_ue, facetsExcitation590)) %>% 
  filter(Ex_WL ==590) %>% 
  mutate(DifferentSigma = WL) %>%
  mutate(DifferentSigma = case_when(DifferentSigma=="WW"~"Light~condition")) %>% 
  rename(Sigma_value = Sig_nm2psii) %>% 
  rename(AllmeanSigma_value = AllmeanSig_nm2psii) %>% 
  rename(AllsdSigma_value = AllsdSig_nm2psii)

SolFitsAllPigmentPCPEMerge2<-SolFitsAllPigmentPCPE %>% 
  select(c(Strain, Ex_WL, WL, Par_ue, Photoperiod, Sigdark_nm2psii, AllmeanSigdark_nm2psii, AllsdSigdark_nm2psii, PhycoChlaRatioExp, facetsPar_ue, facetsExcitation590)) %>% 
  filter(Ex_WL ==590) %>% 
  mutate(DifferentSigma = WL) %>%
  mutate(DifferentSigma = case_when(DifferentSigma=="WW"~"Dark~condition")) %>% 
  rename(Sigma_value = Sigdark_nm2psii) %>% 
  rename(AllmeanSigma_value = AllmeanSigdark_nm2psii) %>% 
  rename(AllsdSigma_value = AllsdSigdark_nm2psii)

SolFitsAllPigmentPCPEMerge590<-rbind(SolFitsAllPigmentPCPEMerge1, SolFitsAllPigmentPCPEMerge2)
  rm(SolFitsAllPigmentPCPEMerge1, SolFitsAllPigmentPCPEMerge2)


SolFitsAllPigmentfitPhycoChlalinearMerge590 <- SolFitsAllPigmentPCPEMerge590 %>%   
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, Sigma_value, PhycoChlaRatioExp, WL, DifferentSigma, facetsPar_ue, facetsExcitation590)) %>%  
  nest(data = -c("Par_ue", "DifferentSigma", "facetsPar_ue", "facetsExcitation590")) %>%   
  mutate(Linear_Model = map(data, ~lm(Sigma_value ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))

```

# Create a preliminary plot

```{r preliminary plot}

SolFitsAllPigmentfitPhycoChlalinearMerge590 %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSigma_value, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPEMerge590) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigma_value - AllsdSigma_value, ymax = AllmeanSigma_value + AllsdSigma_value, colour=as.factor(Strain)), SolFitsAllPigmentPCPEMerge590) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(facetsExcitation590, DifferentSigma), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() 
```

# Create Sigma vs pigments ratio plot

```{r fig.height = 8, fig.width = 8, warning = FALSE}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAllPigmentfitPhycoChlalinearMerge590 %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSigma_value, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPEMerge590) + 
  geom_point(aes(x = PhycoChlaRatioExp, y = Sigma_value, colour=as.factor(Strain)), size = 1, show.legend = F, SolFitsAllPigmentPCPEMerge590) +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigma_value - AllsdSigma_value, ymax = AllmeanSigma_value + AllsdSigma_value, colour = as.factor(Strain)), show.legend = F, width=0, size=0.3, SolFitsAllPigmentPCPEMerge590) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_y_continuous(breaks=seq(0, 12, by = 3)) +
  coord_cartesian(ylim = c(0, 12)) +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*" quanta"^"-1"*")")), x = "Total phyco/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(facetsExcitation590, DifferentSigma), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.09,0.94),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```

# Save RDS that create plot

```{r}
saveRDS(SolFitsAllPigmentfitPhycoChlalinearMerge590, file.path(RDSPlotPath, paste(Project, "Plot_SigmavsPigments_1.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(SolFitsAllPigmentPCPEMerge590, file.path(RDSPlotPath, paste(Project, "Plot_SigmavsPigments_2.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("SigmavsPigments590_Plot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```




# Combine 445 sigma and sigma in the dark

```{r}

SolFitsAllPigmentPCPE$facetsExcitation445 = factor(SolFitsAllPigmentPCPE$O2, labels = c("Excitation~445~nm"))

SolFitsAllPigmentPCPEMerge1<-SolFitsAllPigmentPCPE %>% 
  select(c(Strain, Ex_WL, WL, Par_ue, Photoperiod, Sig_nm2psii, AllmeanSig_nm2psii, AllsdSig_nm2psii, PhycoChlaRatioExp, facetsPar_ue, facetsExcitation445)) %>% 
  filter(Ex_WL ==445) %>% 
  mutate(DifferentSigma = WL) %>%
  mutate(DifferentSigma = case_when(DifferentSigma=="WW"~"Light~condition")) %>% 
  rename(Sigma_value = Sig_nm2psii) %>% 
  rename(AllmeanSigma_value = AllmeanSig_nm2psii) %>% 
  rename(AllsdSigma_value = AllsdSig_nm2psii)

SolFitsAllPigmentPCPEMerge2<-SolFitsAllPigmentPCPE %>% 
  select(c(Strain, Ex_WL, WL, Par_ue, Photoperiod, Sigdark_nm2psii, AllmeanSigdark_nm2psii, AllsdSigdark_nm2psii, PhycoChlaRatioExp, facetsPar_ue, facetsExcitation445)) %>% 
  filter(Ex_WL ==445) %>% 
  mutate(DifferentSigma = WL) %>%
  mutate(DifferentSigma = case_when(DifferentSigma=="WW"~"Dark~condition")) %>% 
  rename(Sigma_value = Sigdark_nm2psii) %>% 
  rename(AllmeanSigma_value = AllmeanSigdark_nm2psii) %>% 
  rename(AllsdSigma_value = AllsdSigdark_nm2psii)

SolFitsAllPigmentPCPEMerge445<-rbind(SolFitsAllPigmentPCPEMerge1, SolFitsAllPigmentPCPEMerge2)
  rm(SolFitsAllPigmentPCPEMerge1, SolFitsAllPigmentPCPEMerge2)


SolFitsAllPigmentfitPhycoChlalinearMerge445 <- SolFitsAllPigmentPCPEMerge445 %>%   
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, Sigma_value, PhycoChlaRatioExp, WL, DifferentSigma, facetsPar_ue, facetsExcitation445)) %>%  
  nest(data = -c("Par_ue", "DifferentSigma", "facetsPar_ue", "facetsExcitation445")) %>%   
  mutate(Linear_Model = map(data, ~lm(Sigma_value ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))

```

# Create a preliminary plot

```{r preliminary plot}

SolFitsAllPigmentfitPhycoChlalinearMerge445 %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSigma_value, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPEMerge445) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigma_value - AllsdSigma_value, ymax = AllmeanSigma_value + AllsdSigma_value, colour=as.factor(Strain)), SolFitsAllPigmentPCPEMerge445) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(facetsExcitation445, DifferentSigma), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() 
```

# Create Sigma vs pigments ratio plot

```{r fig.height = 8, fig.width = 8, warning = FALSE}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAllPigmentfitPhycoChlalinearMerge445 %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSigma_value, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPEMerge445) + 
  geom_point(aes(x = PhycoChlaRatioExp, y = Sigma_value, colour=as.factor(Strain)), size = 1, show.legend = F, SolFitsAllPigmentPCPEMerge445) +
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSigma_value - AllsdSigma_value, ymax = AllmeanSigma_value + AllsdSigma_value, colour = as.factor(Strain)), show.legend = F, width=0, size=0.3, SolFitsAllPigmentPCPEMerge445) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_y_continuous(breaks=seq(0, 2.5, by = 0.5)) +
  coord_cartesian(ylim = c(0, 2.5)) +
  labs(y=expression(paste(sigma,""["PSII"]*" (nm"^"2"*" quanta"^"-1"*")")), x = "Total phyco/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(facetsExcitation445, DifferentSigma), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.09,0.94),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```

# Save RDS that create plot

```{r}
saveRDS(SolFitsAllPigmentfitPhycoChlalinearMerge445, file.path(RDSPlotPath, paste(Project, "SupPlot_SigmavsPigments_1.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(SolFitsAllPigmentPCPEMerge445, file.path(RDSPlotPath, paste(Project, "SupPlot_SigmavsPigments_2.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("SigmavsPigments445_SupPlot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```

# Linear fit per Strain

```{r linear fit}
SolFitsAllPigmentfitPhycoChlalinearStrain <- SolFitsAllPigmentPCPE %>%  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL, Phase, facetsExcitation, facetsStrain)) %>%  
  nest(data = -c("Strain", "Ex_WL", "Phase")) %>%  
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))


SolFitsAllPigmentfitPhycoChlalineardarkStrain <- SolFitsAllPigmentPCPE %>%   
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL, Phase)) %>%  
  nest(data = -c("Strain", "Ex_WL", "Phase")) %>% 
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))


SolFitsAllPigmentfitPhycoChlalinearStrain1s <- SolFitsAllPigmentPCPE1s %>%  
  select(c(Strain, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL, Phase)) %>%  
  nest(data = -c("Strain", "Ex_WL", "Phase")) %>% 
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%    
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))

#xxxxxx

SolFitsAllPigmentfitPhycoChlalinearStrainGroup <- SolFitsAllPigmentPCPE %>%   
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSig_nm2psii, PhycoChlaRatioExp, O2, WL, Phase)) %>%  
  nest(data = -c("StrainGroup", "Ex_WL", "Phase")) %>% 
  mutate(Linear_Model = map(data, ~lm(meanSig_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))


SolFitsAllPigmentfitPhycoChlalineardarkStrainGroup <- SolFitsAllPigmentPCPE %>%   
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSigdark_nm2psii, PhycoChlaRatioExp, O2, WL, Phase)) %>%  
  nest(data = -c("StrainGroup", "Ex_WL", "Phase")) %>% 
  mutate(Linear_Model = map(data, ~lm(meanSigdark_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))


SolFitsAllPigmentfitPhycoChlalinearStrainGroup1s <- SolFitsAllPigmentPCPE1s %>%   
  select(c(StrainGroup, Par_ue, Photoperiod, Ex_WL, meanSig1s_nm2psii, PhycoChlaRatioExp, O2, WL, Phase)) %>%
  nest(data = -c("StrainGroup", "Ex_WL", "Phase")) %>%  
  mutate(Linear_Model = map(data, ~lm(meanSig1s_nm2psii ~ PhycoChlaRatioExp, data = .x))) %>%     
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))
```

# Create preliminary plot

```{r preliminary plot}
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


SolFitsAllPigmentfitPhycoChlalinearStrain %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig_nm2psii - sdSig_nm2psii, ymax = meanSig_nm2psii + sdSig_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  # scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  # scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentfitPhycoChlalineardarkStrain %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain),labeller = label_parsed) +
  theme_bw() 
  
  
SolFitsAllPigmentfitPhycoChlalinearStrain1s %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSig1s_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE1s) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSig1s_nm2psii - sdSig1s_nm2psii, ymax = meanSig1s_nm2psii + sdSig1s_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE1s) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
  
  #xxxxxxxx
  
SolFitsAllPigmentfitPhycoChlalineardarkStrainGroup %>% 
  unnest(Linear_Model_Predict) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = meanSigdark_nm2psii, colour=as.factor(Strain)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE) + 
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = meanSigdark_nm2psii - sdSigdark_nm2psii, ymax = meanSigdark_nm2psii + sdSigdark_nm2psii, colour=as.factor(Strain)), SolFitsAllPigmentPCPE) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) + 
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(StrainGroup),labeller = label_parsed) +
  theme_bw() 
```

# Create Sigma vs pigments ratio plot

```{r fig.height = 8, fig.width = 8, warning = FALSE}
WL.labs <- c("Excitation (nm)")
names(WL.labs) <- c("WW")
O2.labs <- c("Strain")
names(O2.labs) <- c(21)

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAllPigmentPCPE590<-SolFitsAllPigmentPCPE %>% 
    filter(Ex_WL==590) 

SolFitsAllPigmentfitPhycoChlalinearStrain %>% 
  unnest(Linear_Model_Predict, data) %>% 
  filter(Ex_WL==590) %>% 
  ggplot() +
  geom_point(aes(x = PhycoChlaRatioExp, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T, SolFitsAllPigmentPCPE590) + 
  geom_point(aes(x = PhycoChlaRatioExp, y = Sig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, show.legend = F, SolFitsAllPigmentPCPE590) + 
  
  geom_errorbar(aes(x = PhycoChlaRatioExp, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour = as.factor(Par_ue)), show.legend = F, width=0, size=0.3, SolFitsAllPigmentPCPE590) +
  geom_line(aes(x = PhycoChlaRatioExp, y = `.fitted`), show.legend = F) +   
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  scale_y_continuous(breaks=seq(0, 8, by = 2)) +
  coord_cartesian(ylim = c(0, 9)) +
  labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*" quanta"^"-1"*")")), x = "Total phyco/Chl" ~italic(a)~ "ratio") +
  ggh4x::facet_nested(cols = vars(Phase), rows = vars(O2, Strain), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.92,0.88),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("SigmavsPigments590Phase_SupPlot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```


# Clean the environment

```{r}
rm(SolFitsAllPigmentfitPhycoChlalineardarkStrain, SolFitsAllPigmentfitPhycoChlalineardarkStrainGroup, SolFitsAllPigmentfitPhycoChlalinearStrain, SolFitsAllPigmentfitPhycoChlalinearStrain1s, SolFitsAllPigmentfitPhycoChlalinearStrainGroup, SolFitsAllPigmentfitPhycoChlalinearStrainGroup1s)
```


# Load Turner catalog

```{r load turner catalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
Turnercatalog<- read_sheet("https://docs.google.com/spreadsheets/d/13mQm0B3siS65UuGjNdzvpHFomfuwn6aAg7dBoq1IqrM/edit#gid=0")

as.data.frame(Turnercatalog)
ChlData <- Turnercatalog 

ChlData <- ChlData %>%  
  mutate(Chl_ugL = as.numeric(Reading_rfu) * as.numeric(Chl_slope) + as.numeric(Chl_intercept)) %>% 
  mutate(DATE = ymd(`DATE`)) %>% 
  rename(SampleID=CultureID) %>% 
  rename(ObsDate=DATE) %>% 
  select(c(SampleID, ObsDate, Chl_ugL)) %>% 
  filter(Chl_ugL<212354.754) #outliers
```

# Calculate Chl mean from 3 technical replica

```{r}
ChlData <- ChlData %>%
  group_by(SampleID, ObsDate) %>%
  summarize(SampleID, ObsDate, Chl_ugL,
            meanChl_ugL = mean(Chl_ugL),
            sdChl_ugL = sd(Chl_ugL)) %>%
  ungroup()
```
# Merge Sigma with chlorophyll Turner data

```{r}
SolFitsAllPigmentPCPETurner <- ChlData %>%
  left_join(., SolFitsPigmentExp, by = c("SampleID"="SampleID", "ObsDate"="ObsDate"))

SolFitsAllPigmentPCPETurner<-SolFitsAllPigmentPCPETurner %>% 
  filter(Strain=="PC-rich_056" | Strain == "PC-rich_077" | Strain == "PE-rich_048" | Strain == "PE-rich_127")
```

# Create preliminary JVPSII vs Chl Turner (ug/L) plot

```{r preliminary plots, warning = FALSE}
SolFitsAllPigmentPCPETurner %>% 
  ggplot() +
  geom_point(aes(x = Chl_ugL, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()


SolFitsAllPigmentPCPETurner %>% 
  ggplot() +
  geom_point(aes(x = cellLExp, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsAllPigmentPCPETurner %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()
```

# Clean the environment

```{r}
rm(Turnercatalog, ChlData, SolFitsAllPigmentPCPE, SolFitsAllPigmentPCPE1s)
```

# Save rds for further analysis

```{r save rds}
saveRDS(SolFitsAllPigmentPCPETurner, file.path(DataOut, paste(Project, "Processed_SolisensePigmentsExp.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(SolFitsAllPigmentPCPETurner)
```







Set up R codes for Greek letters

\u0391  Α   Greek Capital Letter Alpha
\u0392  Β   Greek Capital Letter Beta
\u0393  Γ   Greek Capital Letter Gamma
\u0394  Δ   Greek Capital Letter Delta
\u0395  Ε   Greek Capital Letter Epsilon
\u0396  Ζ   Greek Capital Letter Zeta
\u0397  Η   Greek Capital Letter Eta
\u0398  Θ   Greek Capital Letter Theta
\u0399  Ι   Greek Capital Letter Iota
\u039A  Κ   Greek Capital Letter Kappa
\u039B  Λ   Greek Capital Letter Lambda
\u039C  Μ   Greek Capital Letter Mu
\u039D  Ν   Greek Capital Letter Nu
\u039E  Ξ   Greek Capital Letter Xi
\u039F  Ο   Greek Capital Letter Omicron
\u03A0  Π   Greek Capital Letter Pi
\u03A1  Ρ   Greek Capital Letter Rho
\u03A3  Σ   Greek Capital Letter Sigma
\u03A4  Τ   Greek Capital Letter Tau
\u03A5  Υ   Greek Capital Letter Upsilon
\u03A6  Φ   Greek Capital Letter Phi
\u03A7  Χ   Greek Capital Letter Chi
\u03A8  Ψ   Greek Capital Letter Psi
\u03A9  Ω   Greek Capital Letter Omega
\u03B1  α   Greek Small Letter alpha
\u03B2  β   Greek Small Letter beta
\u03B3  γ   Greek Small Letter gamma
\u03B4  δ   Greek Small Letter delta
\u03B5  ε   Greek Small Letter epsilon
\u03B6  ζ   Greek Small Letter zeta
\u03B7  η   Greek Small Letter eta
\u03B8  θ   Greek Small Letter theta
\u03B9  ι   Greek Small Letter iota
\u03BA  κ   Greek Small Letter kappa
\u03BB  λ   Greek Small Letter lambda
\u03BC  μ   Greek Small Letter mu
\u03BD  ν   Greek Small Letter nu
\u03BE  ξ   Greek Small Letter xi
\u03BF  ο   Greek Small Letter omicron
\u03C0  π   Greek Small Letter pi
\u03C1  ρ   Greek Small Letter rho
\u03C2  ς   Greek Small Letter final sigma
\u03C3  σ   Greek Small Letter sigma
\u03C4  τ   Greek Small Letter tau
\u03C5  υ   Greek Small Letter upsilon
\u03C6  φ   Greek Small Letter phi
\u03C7  χ   Greek Small Letter chi
\u03C8  ψ   Greek Small Letter psi
\u03C9  ω   Greek Small Letter omega





