---
title: "Process OLIS spectral data"
author: "Douglas A. Campbell, Sylwia Sliwinska-Wilczewska"
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
---

```{r setup, include = FALSE}
# knitr::opts_chunk$set(echo = TRUE, message = FALSE)
# knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "CleanData")
DataIn <- file.path("..", "Data", "ProcessedData", fsep = .Platform$file.sep)

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)

library(dplyr)
library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)

library(ggspectra)
library(ggpubr)
library(caret)

library(photobiologyWavebands)
library(reshape2)
library(photobiology)

library(gcookbook)
library(RColorBrewer)
library(viridis)
library(scales)

library(reshape)
library(patchwork)
library(minpack.lm)
library(Cairo) #for greek symbols

```


```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")

names(Colours_nm) <- Wavelengths_nm
Colours_nm
```

```{r Exported Rmd only first time in session}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```
```{r Read imported Olis file}
#File choosen for spectra plot - 4 spectra only
OLISSpectraShortFile <- "../Data/ProcessedData/Baltic_Photoperiod_OlisSpectra.Rds"
OLISSpectraShortFileName <- str_split(string = OLISSpectraShortFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
OLISSpectraShort <- readRDS(OLISSpectraShortFile)  %>%
  ungroup()
```

```{r Delete unnecessary strains}
OLISSpectraShort1 <- OLISSpectraShort %>%
    filter(Strain=="BA127R" |Strain=="BA48R" | Strain=="BA56G" | Strain=="BA77G") 
```

```{r Changes in strain names}
OLISSpectraShort2 <- OLISSpectraShort1 %>%
      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))
```

```{r}
OLISSpectraShort3<-OLISSpectraShort2 %>% 
  filter(Strain == "PE-rich_127" | Strain == "PC-rich_077") %>%
  filter(Par_ue== 300) %>%
  filter(Photoperiod==12) %>%
  filter(WL=="WW") %>%
  filter(O2==21) %>% 
  filter(E_days==6 | E_days == 2 | E_days == 3) 

```



Export Jaz file
```{r}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "CleanData")
DataIn <- file.path("..", "Data", "ProcessedData", fsep = .Platform$file.sep)

FileEncode <- "UTF-8"
Delimiter <- ","

HeaderRows <- 0
```

Jaz file
Exported from PICO_SySlJazSpec_MultiCulti.Rmd only first time in session
```{r}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

Jaz file
```{r read ProcessFile}
JazFile <- "../ImportedData/Jaz/PicoBaltic_MultiCultiSpectraSySlWWPhotoperiodAll.Rds"

JazFileName <- str_split(string = JazFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

JazData <- readRDS(JazFile)  %>%
  ungroup()

colnames(JazData)
```

```{r}
JazData <- JazData %>%
   mutate(WavelengthRound = round(Wavelength))
colnames(JazData)

JazDataRound <- JazData %>%
group_by(Filename, WavelengthRound) %>%
  summarize(Counts, Filename, Instrument, Date, Strain, Par, WL, CDateTime, WavelengthRound, CountsMean = mean(Counts)) %>%
ungroup()

JazDataRound <- JazDataRound %>%
  summarize(Filename, Strain, Par, WL, WavelengthRound, CountsMean) %>%
  unique()

JazDataRound <- JazDataRound %>%
  filter(WavelengthRound >= 400 & WavelengthRound <= 700)

```
Normalization at 439
```{r}

EmissionJazWW <- JazDataRound %>%
  group_by(WL, Strain, Par) %>%
  filter(WavelengthRound == 439) %>%
  mutate(EmJaz439 = CountsMean) %>%
  select(Strain, EmJaz439, Par) %>%
  ungroup()

JazDataRoundMeta <- JazDataRound %>%
  left_join(., EmissionJazWW) %>%
  mutate(EmNormJaz439 = CountsMean / EmJaz439)
  
```
Combine Olis spectra and Jaz
```{r}

OLISSpectraMetaAll <- OLISSpectraMeta440All %>%
  left_join(., JazDataRoundMeta, by = c("Par_ue" = "Par", "nm" = "WavelengthRound", "Strain" = "Strain", "WL" = "WL")) %>%
  unique()

rm(JazDataRound, EmissionJazWW, JazData)
rm(OLISSpectraMeta440All, JazDataRoundMeta)
```

PUR Mireille idea
```{r}

OLISSpectraMetaAllPUR <- OLISSpectraMetaAll %>%

  mutate(PURNorm = (AbsNorm440*EmNormJaz439)) %>% # green line

  group_by(WL, Strain, Par_ue, Photoperiod, E_days) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% #sum of the green line
  mutate(SumEmNormJaz439 = sum(EmNormJaz439)) %>% #sum of the blue line
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz439)) %>% 
  ungroup() 


OLISSpectraMetaAllPUR1 <- OLISSpectraMetaAllPUR %>%
  filter(Photoperiod != "24") %>% 
  mutate(PURPhotonDose =(PUR/2)*Photoperiod*3600)
  
OLISSpectraMetaAllPUR2 <- OLISSpectraMetaAllPUR %>%
  filter(Photoperiod == "24") %>% 
  mutate(PURPhotonDose = PUR*Photoperiod*3600) 
  
  OLISSpectraMetaAllPUR <-rbind(OLISSpectraMetaAllPUR1, OLISSpectraMetaAllPUR2)
  rm(OLISSpectraMetaAllPUR1,OLISSpectraMetaAllPUR2)


```

Clean OLISSpectraMetaAllPUR for WW photoperiod manuscript - contain absorbance and all nm
```{r}
#colnames(OLISSpectraMetaAllPURClean)

OLISSpectraMetaAllPURClean<-OLISSpectraMetaAllPUR %>% 
  filter(Strain == "BA127R" | Strain == "BA77G" | Strain == "BA48R" | Strain == "BA56G") %>%
  select(-c(PrimaryOperator, doi, ProjectID, Inoc_mL, Media_mL, Plate, Well, Salinity,  N2, Ar, CO2, Media, MediaDate, SourceSalinity, OptodeCh, InocpH, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ...44, ...45, Description, Motivation, EndDate,  ExpCul, ExpStartTime, Source, Optode, Range, Cdatetime, Project, "Calculated_µmolPhotons_m-2d-1", Temp_c, O2_Category, Filename.x, Filename.y, SumAb, SumAbNorm, CountsMean, PURNormSum, SumEmNormJaz439))

  OLISSpectraMetaAllPURClean1 <- OLISSpectraMetaAllPURClean %>%
  filter(Photoperiod != "24") %>% 
  mutate(PARPhotonDose =(Par_ue/2)*Photoperiod*3600)
  
  OLISSpectraMetaAllPURClean2 <- OLISSpectraMetaAllPURClean %>%
  filter(Photoperiod == "24") %>% 
  mutate(PARPhotonDose = Par_ue*Photoperiod*3600) 
  
  OLISAllPURLong <-rbind(OLISSpectraMetaAllPURClean1, OLISSpectraMetaAllPURClean2)
  
  rm(OLISSpectraMetaAllPURClean1,OLISSpectraMetaAllPURClean2, OLISSpectraMetaAllPURClean)
  rm(OLISSpectraMetaAll, OLISSpectraMetaAllPUR)
```












OLISSpectraMetaAllPURShort -> File choosen for spectra plot - 4 spectra only
Olis Plot
```{r fig.height = 6, fig.width = 8}

Par_ue.labs <- c("Phase of growth")
names(Par_ue.labs) <- c("300")

Photoperiod.labs <- c("Photoperiod: 12 h")
names(Photoperiod.labs) <- c("12")

E_days.labs <- c("Exponential", "Exponential", "Pre-stationary")
names(E_days.labs) <- c("2", "3", "7")

Strain.labs <- c("PE-rich_127", "PC-rich_077")
names(Strain.labs) <- c("PE-rich_127", "PC-rich_077")

# data_textPUR0 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PAR = 300 µE', 'PAR = 300 µE'))
# 
# data_textPUR1 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PUR (PE-rich) = 176 µE', 'PUR (PE-rich) = 129 µE'))
# 
# data_textPUR2 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PUR (PC-rich) = 139 µE', 'PUR (PC-rich) = 128 µE'))

data_textpigment1 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Chl a 440 nm'))
data_textpigment2 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PE 570 nm'))
data_textpigment3 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Chl a 680 nm'))
data_textpigment4 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PC 620 nm'))
data_textpigment5 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Car 480 nm'))
data_textpigment6 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PUB 500 nm'))

arrowdf1 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf2 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf3 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf4 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf5 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf6 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)


OLISSpectraShort3 %>%
  # filter(Photoperiod == "12") %>%
  # filter(Strain == "PE-rich_127" | Strain == "PC-rich_077") %>%
  # filter(Par_ue == 300) %>%
  # filter(E_days == "3" | E_days == "7") %>%
  ggplot() +
  # geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
  # geom_area(aes(x = nm, y = PURNormBA127R, fill = "brown4"), alpha = 0.5, show.legend = F) +
  # geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, size = 0.7) +

  # geom_text(data=data_textPUR0, aes(x=435, y=1.26, label=label), size=3.5) +
  # geom_text(data=data_textPUR1, aes(x=462, y=1.21, label=label), size=3.5) +
  # geom_text(data=data_textPUR2, aes(x=462, y=1.16, label=label), size=3.5) +

  geom_text(data=data_textpigment1, aes(x=450, y=1.07, label=label), size=4, colour = "darkgreen") + #chla440
  geom_text(data=data_textpigment5, aes(x=430, y=0.36, label=label), size=4, colour = "coral3") + #Car
  geom_text(data=data_textpigment2, aes(x=520, y=0.92, label=label), size=4, colour = "darkmagenta") + #PE
  geom_text(data=data_textpigment3, aes(x=660, y=1.08, label=label), size=4, colour = "darkgreen") +#chla680
  geom_text(data=data_textpigment4, aes(x=605, y=1.0, label=label), size=4, colour = "deepskyblue4") + #PC
  geom_text(data=data_textpigment6, aes(x=485, y=0.08, label=label), size=4, colour = "sienna4") + #PUB

  geom_segment(data = arrowdf1,
               aes(x = 470, xend = 440, y = 1.04, yend = 1.02),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
    geom_segment(data = arrowdf5,
               aes(x = 450, xend = 470, y = 0.4, yend = 0.48),
               colour = "coral3", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
  geom_segment(data = arrowdf2,
               aes(x = 538, xend = 568, y = 0.88, yend = 0.86),
               colour = "darkmagenta", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PE
  geom_segment(data = arrowdf3,
               aes(x = 697, xend = 680, y = 1.05, yend = 0.92),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
  geom_segment(data = arrowdf4,
               aes(x = 632, xend = 630, y = 0.95, yend = 0.82),
               colour = "deepskyblue4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
  geom_segment(data = arrowdf4,
               aes(x = 465, xend = 500, y = 0.12, yend = 0.52),
               colour = "sienna4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
  
  # scale_color_manual(values = c("BA127R" ="black", "BA48R" ="brown1", "BA56G" ="palegreen4", "BA77G" ="black")) +
  scale_color_manual(values = c("PE-rich_127" ="brown4", "PC-rich_077" ="palegreen3")) +
  scale_linetype_manual(values = c("PE-rich_127" ="longdash", "PC-rich_077" ="solid")) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) + 
  scale_fill_identity() +
  
  labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c (-0.01, 1.25)) +

  
  ggh4x::facet_nested(cols = vars(Par_ue, E_days), labeller = labeller(Ex_WL = label_both, WL = label_both, E_days = E_days.labs, Photoperiod = Photoperiod.labs, Par_ue = Par_ue.labs, Strain = Strain.labs)) +
  
  theme_bw() +
      theme(panel.grid.minor = element_blank(),
          panel.grid.major = element_blank(),
          panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.direction="horizontal",
        legend.position = c(0.08,0.97),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text.align = 0,
        #legend.key.height= unit(0.005, 'cm'),
        legend.key.width= unit(0.3, 'cm'),
        #plot.background = element_rect(colour = "dodgerblue4", size = 3),
        legend.text = element_text(size=10))



```

Olis Plot
```{r fig.height = 10, fig.width = 8}
Par_ue.labs <- c("30 µE", "90 µE", "180 µE", "Phase of growth", "900 µE")
names(Par_ue.labs) <- c("30", "90", "180", "300", "900")

Photoperiod.labs <- c("8 h", "Photoperiod: 12 h", "16 h", "24 h")
names(Photoperiod.labs) <- c("8", "12", "16", "24")

E_days.labs <- c("Exponential", "Pre-stationary")
names(E_days.labs) <- c("3", "7")

Strain.labs <- c("PC-rich", "PE-rich")
names(Strain.labs) <- c("PC-rich_077", "PE-rich_127")

O2.labs <- c("Strain")
names(O2.labs) <- c(21)

data_textPUR0 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PAR = 300 µE', 'PAR = 300 µE'))

data_textPUR00 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PC-rich_077", "PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PAR = 300 µE', 'PAR = 300 µE'))

data_textPUR1 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PUR = 176 µE', 'PUR = 129 µE'))

data_textPUR2 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PC-rich_077", "PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PUR = 139 µE', 'PUR = 128 µE'))

data_textpigment1 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 440 nm'))
data_textpigment3 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 680 nm'))
data_textpigment4 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PCB-rich PC 620 nm'))
data_textpigment5 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Car 480 nm'))
data_textpigment6 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PUB-rich PC 500 nm'))

arrowdf1 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf3 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf4 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf5 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf6 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))


data_textpigment7 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 440 nm'))
data_textpigment8 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Car 480 nm'))
data_textpigment9 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PEB-rich PE 570 nm'))
data_textpigment10 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 680 nm'))
data_textpigment11 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PCB-rich PC 620 nm'))
data_textpigment12 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PUB-rich PE 500 nm'))

arrowdf7 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf8 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf9 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf10 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf11 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf12 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))


Plot <- OLISSpectraShort %>%
  filter(Photoperiod == "12") %>%
  filter(Strain == "PC-rich_077" | Strain == "PE-rich_127") %>%
  filter(Par_ue == 300) %>%
  filter(E_days == "3" | E_days == "7") %>%
  ggplot() +

  geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = PURNormBA127R, fill = "brown4"), alpha = 0.5, show.legend = F) +
  geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, size = 0.7) +

  geom_text(data=data_textPUR0, aes(x=446, y=1.26, label=label), size=3.7) +
  geom_text(data=data_textPUR00, aes(x=446, y=1.26, label=label), size=3.7) +
  geom_text(data=data_textPUR1, aes(x=446, y=1.21, label=label), size=3.7) +
  geom_text(data=data_textPUR2, aes(x=446, y=1.21, label=label), size=3.7) +

  geom_text(data=data_textpigment1, aes(x=500, y=1.1, label=label), size=4, colour = "darkgreen") + #chla440
  geom_text(data=data_textpigment5, aes(x=500, y=0.8, label=label), size=4, colour = "orange") + #Car
  geom_text(data=data_textpigment3, aes(x=650, y=1.2, label=label), size=4, colour = "darkgreen") +#chla680
  geom_text(data=data_textpigment4, aes(x=590, y=0.95, label=label), size=4, colour = "deepskyblue4") + #PC
  geom_text(data=data_textpigment6, aes(x=485, y=0.25, label=label), size=4, colour = "sienna4") + #PUB

  geom_segment(data = arrowdf1,
               aes(x = 480, xend = 445, y = 1.05, yend = 1),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
  geom_segment(data = arrowdf5,
               aes(x = 480, xend = 475, y = 0.75, yend = 0.54),
               colour = "orange", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
  geom_segment(data = arrowdf3,
               aes(x = 660, xend = 680, y = 1.14, yend = 0.95),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
  geom_segment(data = arrowdf4,
               aes(x = 610, xend = 630, y = 0.90, yend = 0.82),
               colour = "deepskyblue4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
  geom_segment(data = arrowdf4,
               aes(x = 480, xend = 494, y = 0.30, yend = 0.41),
               colour = "sienna4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB

  
  geom_text(data=data_textpigment7, aes(x=500, y=1.1, label=label), size=4, colour = "darkgreen") + #chla440
  geom_text(data=data_textpigment8, aes(x=500, y=0.8, label=label), size=4, colour = "orange") + #Car
  geom_text(data=data_textpigment9, aes(x=580, y=1.0, label=label), size=4, colour = "darkmagenta") + #PE
  geom_text(data=data_textpigment10, aes(x=650, y=1.2, label=label), size=4, colour = "darkgreen") +#chla680
  geom_text(data=data_textpigment11, aes(x=600, y=0.17, label=label), size=4, colour = "deepskyblue4") + #PC
  geom_text(data=data_textpigment12, aes(x=495, y=0.30, label=label), size=4, colour = "sienna4") + #PUB

  geom_segment(data = arrowdf7,
               aes(x = 480, xend = 445, y = 1.05, yend = 1),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
  geom_segment(data = arrowdf8,
               aes(x = 480, xend = 475, y = 0.75, yend = 0.55),
               colour = "orange", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
  geom_segment(data = arrowdf9,
               aes(x = 590, xend = 575, y = 0.95, yend = 0.85),
               colour = "darkmagenta", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PE
  geom_segment(data = arrowdf10,
               aes(x = 660, xend = 680, y = 1.14, yend = 0.85),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
  geom_segment(data = arrowdf11,
               aes(x = 610, xend = 630, y = 0.2, yend = 0.3),
               colour = "deepskyblue4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
  geom_segment(data = arrowdf12,
               aes(x = 490, xend = 500, y = 0.35, yend = 0.52),
               colour = "sienna4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
  
  
  
  scale_color_manual(values = c("PC-rich_077" ="palegreen3", "PE-rich_127" ="brown4")) +
  scale_linetype_manual(values = c("PC-rich_077" ="solid", "PE-rich_127" ="longdash")) +

  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +

  labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c (-0.01, 1.25)) +
  ggh4x::facet_nested(cols = vars(Par_ue, E_days), rows = vars(O2, Strain),labeller = labeller(Ex_WL = label_both, WL = label_both, E_days = E_days.labs, Photoperiod = Photoperiod.labs, Par_ue = Par_ue.labs, Strain = Strain.labs, O2 = O2.labs, )) +
  theme_bw() +
      theme(panel.grid.minor = element_blank(),
          panel.grid.major = element_blank(),
          panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.direction="horizontal",
        legend.position = c(0.08,0.97),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text.align = 0,
        #legend.key.height= unit(0.005, 'cm'),
        legend.key.width= unit(0.3, 'cm'),
        #plot.background = element_rect(colour = "dodgerblue4", size = 3),
        legend.text = element_text(size=10))
Plot


```

```{r Delete unused stuff from the environment}

rm(data_textpigment1,data_textpigment2,data_textpigment3,data_textpigment4,data_textpigment5,data_textpigment6, data_textpigment7, data_textpigment8, data_textpigment9, data_textpigment10, data_textpigment11, data_textpigment12, arrowdf1,arrowdf2,arrowdf3,arrowdf4,arrowdf5,arrowdf6, arrowdf7, arrowdf8, arrowdf9, arrowdf10, arrowdf11, arrowdf12, data_textPUR0, data_textPUR00, data_textPUR1,data_textPUR2)

```




PUR, PIGMENTS, GROWTH RATE












Clean OLISSpectraMetaAllPUR for WW photoperiod manuscript - without absorbance and all nm - smaller df
```{r}
#colnames(OLISSpectraMetaAllPURClean)

OLISAllPURShort<-OLISAllPURLong %>% 
  select(-c(Absorbance, nm, Abs440, AbsNorm440, EmJaz439, EmNormJaz439, PURNorm)) %>% 
  unique()

OLISAllPURShort<-OLISAllPURShort %>% 
  
  group_by(Strain, Par_ue, Photoperiod, E_days, MC, Run) %>%
  mutate(PURPARRatio = PUR/Par_ue) %>% 
ungroup()

OLISAllPURShort <- OLISAllPURShort %>% 
  mutate(E_hours = E_days*24) 
  
OLISAllPURShort <- OLISAllPURShort %>% 
  filter(PURPARRatio<=1) %>% 
  filter(PURPARRatio>0)
  
```


Prepare OLISAllPURShort for nice plot
```{r}
OLISAllPURShort <- OLISAllPURShort %>%
      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))

OLISAllPURShort$facetsPar_ue = factor(OLISAllPURShort$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))

OLISAllPURShort$facetsPhotoperiod = factor(OLISAllPURShort$WL, labels = c("Photoperiod~(h)"))

OLISAllPURShort$facetsStrain = factor(OLISAllPURShort$WL, labels = c("Strain"))

OLISAllPURShort$facetsPhase = factor(OLISAllPURShort$WL, labels = c("Phase~of~growth"))

```


PUR/PAR ratio - photoperiod and PAR
```{r fig.height = 8, fig.width = 8}


lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))

lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

Plot <- OLISAllPURShort %>%
  filter(Par_ue !=600) %>% 
  ggplot() +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  # ggh4x::facet_nested(cols = vars(facets2, Photoperiod), rows = vars(facets, Par_ue), labeller = labeller(Photoperiod = Photoperiod.labs,  Strain = label_value, Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs)) +
  theme_bw() 
Plot


```

Load tmaxAG
```{r}
gs4_deauth()

tmaxAG<- read_sheet("https://docs.google.com/spreadsheets/d/1WyB4jonJGW9uFzKHp1Z6DnkMv-CP1PerwQ6sSLK7O8I/edit#gid=0")

as.data.frame(tmaxAG)
tmaxAG <- tmaxAG

tmaxAG<-tmaxAG %>% 

  mutate(Par_ue = as.numeric(Par_ue)) %>%
  mutate(Photoperiod = as.numeric(Photoperiod)) %>%
  mutate(dayRound_tmaxAG = as.numeric(dayRound_tmaxAG)) %>%
  mutate(hRound_tmaxAG = as.numeric(hRound_tmaxAG)) %>% 
  mutate(day_tmaxAG = as.numeric(day_tmaxAG)) %>% 
  mutate(h_tmaxAG = as.numeric(h_tmaxAG)) %>%

  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))

```
Combine OLISAllPURShort with tmaxAG data from google sheet

OLISAllPURShortPhase -> Divided PAR, PUR and PUR/PAR Ratio data to Exponential and Pre-stationary phase according to tmaxAG from google sheet
```{r}

OLISAllPURShortPhase <- OLISAllPURShort %>%
  left_join(., tmaxAG, by = c("Strain"="Strain","Par_ue"="Par_ue","Photoperiod"="Photoperiod")) 

OLISAllPURShortPhase <- OLISAllPURShortPhase %>%
  #filter(Par_ue!= 600) %>% 
  mutate(Phase = O2) %>% 
  mutate(Phase=case_when(E_days<=dayRound_tmaxAG~"Exponential",
         E_days>dayRound_tmaxAG~"Pre-stationary"))

```


Plot -> PUR/PAR ratio - photoperiod and PAR or PAR PhotonDose
```{r fig.height = 8, fig.width = 8}


lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


Plot <- OLISAllPURShortPhase %>%
  filter(Par_ue!= 600) %>% 
  filter(PURPARRatio>0.05) %>% 
  ggplot() +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3, show.legend = T) +
  geom_smooth(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Par_ue)), size = 0.7, alpha = 0, show.legend = F, method = lm) +
  # geom_line(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Par_ue)), alpha = 0.9, size = 0.7, show.legend = F) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab2) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab3) +
  # scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.2)) +
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw()
Plot


Plot <- OLISAllPURShortPhase %>%
  filter(Par_ue!= 600) %>% 
  filter(PURPARRatio>0.05) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose, y = PURPARRatio, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3, show.legend = T) +
  # geom_line(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Par_ue)), alpha = 0.9, size = 0.7, show.legend = F) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab2) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab3) +
  # scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  #labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.2)) +
  ggh4x::facet_nested(rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  theme_bw() 
Plot


Plot <- OLISAllPURShortPhase %>%
  #filter(Photoperiod != "24") %>%
  #filter(Par_ue != 900) %>%
  filter(PURPARRatio<=1) %>%
  filter(PARPhotonDose == 432000|
  PARPhotonDose == 864000|
  PARPhotonDose == 1944000|
  PARPhotonDose == 3888000|
  PARPhotonDose == 6480000|
  PARPhotonDose == 8640000|
  PARPhotonDose == 77760000) %>%
  #filter(E_days != "1") %>%
  ggplot() +
  # geom_smooth(aes(x = Time_h, y = PURPARRatio, colour = as.factor(Strain)),  alpha = 0, size = 0.2, linetype = "solid", show.legend = T) +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  # geom_vline(data = data_vline5, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  # geom_vline(data = data_vline6, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  # geom_vline(data = data_vline7, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  # geom_vline(data = data_vline8, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.5)) +
  ggh4x::facet_nested(cols = vars(PARPhotonDose), labeller = label_parsed) +
  # ggh4x::facet_nested(cols = vars(facets, PhotonDose), labeller = labeller(Photoperiod = Photoperiod.labs,  Strain = label_value, Par_ue = Par_ue.labs, WL = label_parsed, O2 = O2.labs)) +
  theme_bw() 
Plot



```


