---
title: "Process_GrowthRate"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

This RMD process MC data and generate growth rate plot.

# Load Libraries and set Project Variables

```{r load libraries} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggspectra)
library(ggpubr)
library(caret)
library(photobiologyWavebands)
library(reshape2)
library(photobiology)
library(gcookbook)
library(scales)
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessesGrowthRateData")
DataIn <- file.path("..", "Data", "CleanData", "CleanedMCData", fsep = .Platform$file.sep)

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read files

```{r Exported Rmd only first time in session}
list.files(path = DataIn, full.names = TRUE)
```

```{r read file}
MultiCultiGrowthFile <- "../Data/CleanData/CleanedMCData/PICO_NestedFitsData.Rds"

MultiCultiGrowthFileName <- str_split(string = MultiCultiGrowthFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 

MultiCultiGrowth <- readRDS(MultiCultiGrowthFile)  %>%
  ungroup()
```




Because I have a few growth data as replica I made mean to get one value of deltaOD_Lmu_corr
```{r}
MultiCultiGrowthClean <- MultiCultiGrowth %>%
  summarize(Filename, Run, SampleID, Strain, MC, Tube, Par_ue, Photoperiod, O2, WL, ExpDate, LightShape, OD720_Lmu_corr, deltaOD_Lmu_corr, OD720_LseGrowthFlag, deltaOD_LseGrowthFlag, GrowthAmpOD720Flag_14days, GrowthAmpdeltaODFlag_14days, OD720_Lmu_se, deltaOD_Lmu_se)


MultiCultiGrowthAll<-MultiCultiGrowthClean %>% 
  group_by(Strain,Photoperiod,Par_ue) %>% 
    summarize(Filename, Run, SampleID, Strain, MC, Tube, Par_ue, Photoperiod, O2, WL, ExpDate, LightShape, OD720_Lmu_corr, deltaOD_Lmu_corr, OD720_LseGrowthFlag, deltaOD_LseGrowthFlag, GrowthAmpOD720Flag_14days, GrowthAmpdeltaODFlag_14days, OD720_Lmu_se, deltaOD_Lmu_se,
              meandeltaOD_Lmu_corr=mean(deltaOD_Lmu_corr),
              sddeltaOD_Lmu_corr=sd(deltaOD_Lmu_corr)) %>% 
  ungroup()


```

Add PAR PhotonDose and correct name of strains
```{r}

MultiCultiGrowthAll<-MultiCultiGrowthAll %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))

```

NEED TO ADD SHORT/TIDY OLIS
Combine growth rate and all PUR
```{r}
#colnames(OLISSpectraMetaAllPURPARRatioCleanExpPUR)

#All PUR (divided to Phase) and growth rate
MultiCultiGrowthRate <- OLISAllPURShortPhase %>% 
  left_join(., MultiCultiGrowthAll, by = c("Run" = "Run", "SampleID" = "SampleID","Strain" = "Strain", "Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod",  "O2" = "O2", "WL" = "WL",  "MC" = "MC", "Tube" = "Tube", "ExpDate" = "ExpDate", "LightShape" = "LightShape", "PARPhotonDose_day" = "PARPhotonDose_day")) 


```



Combine growth rate and exp PUR
```{r}
MultiCultiDataCleanGrowthAll2<-MultiCultiGrowthRate 
  
O1 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 30 | Par_ue == 300 | Par_ue == 90 | Par_ue == 180) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days < 4)

O2 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 4)

O3 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 6)

O4 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 12)

O5 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 900 | Par_ue == 600) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 4)

O6 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days == 12| E_days == 13)
  
O7 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days == 12 | E_days ==13)

O8 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 8 | E_days ==9)

O9 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PC-rich_056") %>% 
  filter(E_days == 11)

O10 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 180) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days == 8 | E_days == 9)

O11 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 180) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days == 6 | E_days == 7)

O12 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 8) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 6 | E_days ==7)

O13 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 8) %>% 
  filter(Strain == "PC-rich_056") %>% 
  filter(E_days == 9)

O14 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PE-rich_127" | Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  filter(E_days == 4 | E_days ==5)

O15 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PC-rich_056") %>%  
  filter(E_days == 7)

O16 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12)

O17 <- MultiCultiDataCleanGrowthAll2 %>%
  filter(Par_ue == 900 | Par_ue == 600) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_hours < 100 & E_hours > 48)

MultiCultiDataCleanGrowthAll3 <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10, O11, O12, O13, O14, O15, O16, O17)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10, O11, O12, O13, O14, O15, O16, O17)

  
```

Because I have replica in growt rate - I combine one choosen PUR exp to all growth rate data
```{r}
#colnames(MultiCultiDataCleanGrowthAll4)
MultiCultiDataCleanGrowthAll4<-MultiCultiDataCleanGrowthAll3 %>% 
  mutate(PURExp = PUR) %>% 
  mutate(PURPhotonDoseExp = PURPhotonDose_day) %>% 
  mutate(PURPARRatioExp = PURPARRatio) %>% 
  mutate(E_hoursExp = E_hours) %>% 
  mutate(E_daysExp = E_days) %>% 
  select(c(Strain, Par_ue, Photoperiod, PURExp, PURPhotonDoseExp, PURPARRatioExp, E_hoursExp, E_daysExp))
  
MultiCultiGrowthRatePURExp <- MultiCultiGrowthRate %>%
  full_join(., MultiCultiDataCleanGrowthAll4, by = c("Strain"="Strain", "Par_ue"="Par_ue","Photoperiod"="Photoperiod"))


```



PUR/PAR ratio - all data and only exp
```{r fig.height = 8, fig.width = 8}


lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))

Plot <- MultiCultiGrowthRatePURExp %>%
  filter(Par_ue!=600) %>% 
  ggplot() +
  # geom_smooth(aes(x = Time_h, y = PURPARRatio, colour = as.factor(Strain)),  alpha = 0, size = 0.2, linetype = "solid", show.legend = T) +
  geom_point(aes(x = E_hoursExp, y = PURPARRatioExp, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  # geom_errorbar(aes(x = Photoperiod, ymin = OD720_Lmu_corr - OD720_Lmu_se, ymax = OD720_Lmu_corr + OD720_Lmu_se), size = 0.3, width=3, color = '#3C3B53', data = . %>% filter(GrowthAmpOD720Flag_14days  == 1)) +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() 
Plot





lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))

Plot <- MultiCultiGrowthRatePURExp %>%
  filter(Par_ue!=600) %>% 
  filter(PURPARRatio>0.05) %>% 
  ggplot() +
  # geom_smooth(aes(x = Time_h, y = PURPARRatio, colour = as.factor(Strain)),  alpha = 0, size = 0.2, linetype = "solid", show.legend = T) +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  geom_vline(data = data_vline1, aes(xintercept = value), linetype="dotdash", colour = "brown4") +
  geom_vline(data = data_vline2, aes(xintercept = value), linetype="dotdash", colour = "brown1") +
  geom_vline(data = data_vline3, aes(xintercept = value), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = data_vline4, aes(xintercept = value), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  # geom_errorbar(aes(x = Photoperiod, ymin = OD720_Lmu_corr - OD720_Lmu_se, ymax = OD720_Lmu_corr + OD720_Lmu_se), size = 0.3, width=3, color = '#3C3B53', data = . %>% filter(GrowthAmpOD720Flag_14days  == 1)) +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.7)) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  # ggh4x::facet_nested(cols = vars(facets2, Photoperiod), rows = vars(facets, Par_ue), labeller = labeller(Photoperiod = Photoperiod.labs,  Strain = label_value, Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs)) +
  theme_bw() 
Plot


```


```{r fig.height = 5.5, fig.width = 8, warning = FALSE}

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))


O2.labs <- c("Strain")
names(O2.labs) <- c(21)
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

Plot <- MultiCultiGrowthRatePURExp %>%
  filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = deltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "PAR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # labs(shape="Photoperiod (h)", colour="Strain") +
   geom_errorbar(aes(x = PARPhotonDose_day, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  #geom_text(data=data_textA, aes(x=78000000, y=0.25, label=label), size=5) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), labeller = labeller(O2 = O2.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw() 
Plot



Plot <- MultiCultiGrowthRate %>%
  filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "PUR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # labs(shape="Photoperiod (h)", colour="Strain") +
   geom_errorbar(aes(x = PURPhotonDose_day, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), labeller = labeller(O2 = O2.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw() 
Plot

Plot <- MultiCultiGrowthRatePURExp %>%
  filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDoseExp, y = deltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "PUR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # labs(shape="Photoperiod (h)", colour="Strain") +
   geom_errorbar(aes(x = PURPhotonDoseExp, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), labeller = labeller(O2 = O2.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw()
Plot

Plot <- MultiCultiGrowthRatePURExp %>%
  #filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDoseExp, y = meandeltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "PUR photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  # labs(shape="Photoperiod (h)", colour="Strain") +
   geom_errorbar(aes(x = PURPhotonDoseExp, ymin = meandeltaOD_Lmu_corr - sddeltaOD_Lmu_corr, ymax = meandeltaOD_Lmu_corr + sddeltaOD_Lmu_corr), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), labeller = labeller(O2 = O2.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw()
Plot



```



Added column PhotonDose_value and combine data to to PAR and PUR - long format (MultiCultiGrowthRatePURExpFit)
```{r}
MultiCultiGrowthRatePURExpFitPAR<-MultiCultiGrowthRatePURExp %>% 
  select(-c(PURPhotonDose_day)) %>% 
  mutate(PhotonDose_value = PARPhotonDose_day) %>% 
  mutate(PhotonDose = O2) %>% 
  mutate(PhotonDose = case_when(PhotonDose==21~"PAR")) %>% 
  select(-c(PARPhotonDose_day, PURPhotonDoseExp))
  
MultiCultiGrowthRatePURExpFitPUR<-MultiCultiGrowthRatePURExp %>% 
  select(-c(PARPhotonDose_day)) %>% 
  mutate(PhotonDose_value = PURPhotonDoseExp) %>% 
  mutate(PhotonDose = O2) %>% 
  mutate(PhotonDose = case_when(PhotonDose==21~"PUR")) %>% 
  select(-c(PURPhotonDose_day, PURPhotonDoseExp))

MultiCultiGrowthRatePURExpFit<-rbind(MultiCultiGrowthRatePURExpFitPAR, MultiCultiGrowthRatePURExpFitPUR)
rm(MultiCultiGrowthRatePURExpFitPAR, MultiCultiGrowthRatePURExpFitPUR)

```


```{r fig.height = 8, fig.width = 8, warning = FALSE}

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))


O2.labs <- c("Strain")
names(O2.labs) <- c(21)
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

Plot <- MultiCultiGrowthRatePURExpFit %>%
  filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PhotonDose_value, y = deltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
   # geom_errorbar(aes(x = PARPhotonDose_day, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(PhotonDose), labeller = labeller(O2 = O2.labs)) +
    # ggh4x::facet_nested(cols = vars(Strain), labeller = labeller(Photoperiod = Photoperiod.labs,  Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs, Strain = Strain.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12, angle = 45, vjust = 1, hjust = 1),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.91,0.88),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        # legend.spacing.x = unit(0.01, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=9))
Plot


Plot <- MultiCultiGrowthRatePURExpFit %>%
  #filter(deltaOD_Lmu_corr == 0 | deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  # filter(OD720_Lmu_corr == 0 | OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = PhotonDose_value, y = meandeltaOD_Lmu_corr, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.9, show.legend = T) +
labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
   # geom_errorbar(aes(x = PARPhotonDose_day, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), alpha = 0.5, width=2000000, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 80000000, by = 20000000)) +
  coord_cartesian(xlim = c(-100, 83000000)) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2) +
  ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(PhotonDose), labeller = labeller(O2 = O2.labs)) +
    # ggh4x::facet_nested(cols = vars(Strain), labeller = labeller(Photoperiod = Photoperiod.labs,  Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs, Strain = Strain.labs)) +
  scale_x_continuous(label=scientific_10) +
  guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12, angle = 45, vjust = 1, hjust = 1),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.91,0.88),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        # legend.spacing.x = unit(0.01, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=9))
Plot

```

FIT curve

```{r test inhibition plot}

#Harrison & Platt, 1986
grcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}

```



Harrison & Platt, 1986 
```{r platt fit}

CleanGrowthPARPURfit <- MultiCultiGrowthRatePURExpFit |>   
  filter(Par_ue !=900 & Par_ue !=600) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth <- CleanGrowthPARPURfit |>
  unnest(GRCplatt_Predict)

```


Harrison & Platt, 1986 
```{r platt fit}


CleanGrowthPARPURfit900 <- MultiCultiGrowthRatePURExpFit |>   
  filter(Par_ue !=30 & Par_ue !=90 & Par_ue !=180 & Par_ue !=300) |> 
  # filter(Par_ue == 900) |>
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth900 <- CleanGrowthPARPURfit900 |>
  unnest(GRCplatt_Predict)

```


add columns to get nice facet
```{r}

GRCplatt_PredictGrowth$facetsStrain = factor(GRCplatt_PredictGrowth$PhotonDose, labels = c("Strain", "Strain"))

GRCplatt_PredictGrowth900$facetsStrain = factor(GRCplatt_PredictGrowth900$PhotonDose, labels = c("Strain", "Strain"))

```


```{r}
# CleanGrowthPARPURfitbez900 <- CleanGrowthPARPUR %>%    
#   filter(Par_ue !=900) 
# 
# CleanGrowthPARPURfittylko900 <- CleanGrowthPARPUR %>%    
#   filter(Par_ue ==900) %>% 
#   filter(deltaOD_Lmu_se<8.057558e-03)
```



```{r fig.height = 8, fig.width = 8, warning = FALSE}

# O2.labs <- c("Strain")
# names(O2.labs) <- c(21)

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


ggplot(MultiCultiGrowthRatePURExpFit, aes(PhotonDose_value, meandeltaOD_Lmu_corr)) +
  geom_point(aes(PhotonDose_value, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
# 
#   geom_errorbar(aes(x = PhotonDose_value, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Par_ue)), width=4000000, data = . %>% filter(deltaOD_Lmu_se<8.057558e-03), show.legend = F) +
  geom_line(aes(PhotonDose_value, .fitted), show.legend = F, GRCplatt_PredictGrowth) +
  geom_line(aes(PhotonDose_value, .fitted), show.legend = F, GRCplatt_PredictGrowth900) +
  scale_y_continuous(breaks=seq(0, 0.25, by = 0.1)) +
  coord_cartesian(ylim = c(0, 0.25)) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1", "yellow"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "600", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  #geom_hline(aes(yintercept = 0), linetype = 2) +
    ggh4x::facet_nested(cols = vars(PhotonDose), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  #ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(PhotonDose), labeller = labeller(O2 = O2.labs)) +
  # ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Photoperiod), labeller = labeller(Photoperiod = Photoperiod.labs,  Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs)) +
  theme_bw() 

```


Fit for every Par_ue

Harrison & Platt, 1986 
```{r platt fit}

#Harrison & Platt, 1986
grcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}

MultiCultiGrowthRatePURExpFitok<-MultiCultiGrowthRatePURExpFit %>% 
  #filter(deltaOD_Lmu_corr<0.21) %>% 
  filter(Par_ue !=600)

MultiCultiGrowthRatePURExpFit30 <- MultiCultiGrowthRatePURExpFitok |>   
  filter(Par_ue ==30) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth30 <- MultiCultiGrowthRatePURExpFit30 |>
  unnest(GRCplatt_Predict)




MultiCultiGrowthRatePURExpFit90 <- MultiCultiGrowthRatePURExpFitok |>   
  filter(Par_ue ==90) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth90 <- MultiCultiGrowthRatePURExpFit90 |>
  unnest(GRCplatt_Predict)


MultiCultiGrowthRatePURExpFit180 <- MultiCultiGrowthRatePURExpFitok |>   
  filter(Par_ue ==180) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth180 <- MultiCultiGrowthRatePURExpFit180 |>
  unnest(GRCplatt_Predict)



MultiCultiGrowthRatePURExpFit300 <- MultiCultiGrowthRatePURExpFitok |>   
  filter(Par_ue ==300) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth300 <- MultiCultiGrowthRatePURExpFit300 |>
  unnest(GRCplatt_Predict)


MultiCultiGrowthRatePURExpFit900 <- MultiCultiGrowthRatePURExpFitok |>   
  filter(Par_ue ==900) |> 
  #filter(PhotonDose == "PAR") |>
  nest(data = -c("Strain", "PhotonDose")) |> 
  mutate(GRCplatt_Model = map(data, ~nlsLM(deltaOD_Lmu_corr ~ grcplatt(I = PhotonDose_value, a, b, Pmax),
                                                    data = .x,
                                                    start = list(a = 0.1/2e7, b = 0.01/2e7, Pmax = 0.2),
                                                    lower = c(0, 0, 0)))
                                                    #upper = c(1,1,100)), 
                                                    #0))
         ) |>   
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )

GRCplatt_PredictGrowth900 <- MultiCultiGrowthRatePURExpFit900 |>
  unnest(GRCplatt_Predict)


```


add columns to get nice facet
```{r}

GRCplatt_PredictGrowth30$facetsStrain = factor(GRCplatt_PredictGrowth30$PhotonDose, labels = c("Strain", "Strain"))
GRCplatt_PredictGrowth90$facetsStrain = factor(GRCplatt_PredictGrowth90$PhotonDose, labels = c("Strain", "Strain"))
GRCplatt_PredictGrowth180$facetsStrain = factor(GRCplatt_PredictGrowth180$PhotonDose, labels = c("Strain", "Strain"))
GRCplatt_PredictGrowth300$facetsStrain = factor(GRCplatt_PredictGrowth300$PhotonDose, labels = c("Strain", "Strain"))
GRCplatt_PredictGrowth900$facetsStrain = factor(GRCplatt_PredictGrowth900$PhotonDose, labels = c("Strain", "Strain"))
```


Nice plot
```{r fig.height = 8, fig.width = 8, warning = FALSE}

# O2.labs <- c("Strain")
# names(O2.labs) <- c(21)

lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("1 µE"), expression("2 µE"), expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }


ggplot(MultiCultiGrowthRatePURExpFitok, aes(PhotonDose_value, deltaOD_Lmu_corr)) +
  geom_point(aes(PhotonDose_value, deltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
# 
#   geom_errorbar(aes(x = PhotonDose_value, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Par_ue)), width=4000000, data = . %>% filter(deltaOD_Lmu_se<8.057558e-03), show.legend = F) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "darkslategray", show.legend = F, GRCplatt_PredictGrowth30) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "lightblue4", show.legend = F, GRCplatt_PredictGrowth90) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "hotpink4", show.legend = F, GRCplatt_PredictGrowth180) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "indianred3", show.legend = F, GRCplatt_PredictGrowth300) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "orange1", show.legend = F, GRCplatt_PredictGrowth900) +
  scale_y_continuous(breaks=seq(0, 0.25, by = 0.1)) +
  coord_cartesian(ylim = c(0, 0.25)) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  #geom_hline(aes(yintercept = 0), linetype = 2) +
    ggh4x::facet_nested(cols = vars(PhotonDose), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  #ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(PhotonDose), labeller = labeller(O2 = O2.labs)) +
  # ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Photoperiod), labeller = labeller(Photoperiod = Photoperiod.labs,  Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12, angle = 45, vjust = 1, hjust = 1),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.92,0.88),
        #legend.position = c(0.06,0.85),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.15, "cm"),
        # legend.spacing.x = unit(0.01, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=10))



ggplot(MultiCultiGrowthRatePURExpFitok, aes(PhotonDose_value, meandeltaOD_Lmu_corr)) +
  geom_point(aes(PhotonDose_value, meandeltaOD_Lmu_corr, colour=as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.9, size = 3.5, show.legend = T) +
# 
#   geom_errorbar(aes(x = PhotonDose_value, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Par_ue)), width=4000000, data = . %>% filter(deltaOD_Lmu_se<8.057558e-03), show.legend = F) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "darkslategray", show.legend = F, GRCplatt_PredictGrowth30) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "lightblue4", show.legend = F, GRCplatt_PredictGrowth90) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "hotpink4", show.legend = F, GRCplatt_PredictGrowth180) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "indianred3", show.legend = F, GRCplatt_PredictGrowth300) +
  geom_line(aes(PhotonDose_value, .fitted), colour = "orange1", show.legend = F, GRCplatt_PredictGrowth900) +
  scale_y_continuous(breaks=seq(0, 0.25, by = 0.1)) +
  coord_cartesian(ylim = c(0, 0.25)) +
  scale_x_continuous(label=scientific_10) +
  scale_linetype_manual(values=c("equal900" = "dotted", "less900" = "solid"), breaks=c('8', '12', '16', "24", "", "")) +
  scale_colour_manual(values = c("", "", "darkslategray", "lightblue4", "hotpink4", "indianred3", "orange1"), name="", labels = lab2, breaks=c('', '', '30', "90", "180", "300", "900")) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  scale_shape_manual(values = c(15, 16, 17, 18), name="", labels = lab1) +
  labs(y = "Logistic growth rate " ~ "("~h^-1~")", x = "Photon dose ( µmol photons "~m^-2~""~d^-1~")") +
  #geom_hline(aes(yintercept = 0), linetype = 2) +
    ggh4x::facet_nested(cols = vars(PhotonDose), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  #ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(PhotonDose), labeller = labeller(O2 = O2.labs)) +
  # ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Photoperiod), labeller = labeller(Photoperiod = Photoperiod.labs,  Par_ue = Par_ue.labs, WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12, angle = 45, vjust = 1, hjust = 1),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.92,0.88),
        #legend.position = c(0.06,0.85),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.15, "cm"),
        # legend.spacing.x = unit(0.01, 'cm'),
        # legend.direction = "vertical", legend.box = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(size=10))

```

```{r}
rm(MultiCultiGrowthRatePURExpFit30, MultiCultiGrowthRatePURExpFit90, MultiCultiGrowthRatePURExpFit180, MultiCultiGrowthRatePURExpFit300, MultiCultiGrowthRatePURExpFit900)
```



od720 from Multiculti - mean from day
```{r}
# colnames(MultiCultiDataAllStrainsok)
#group_by(ID, Strain, Par_ue, Day, Run, ExpDate, Photoperiod, Tube) %>% 
MultiCultiOD750 <- MultiCultiDataAllStrainsok %>% 

group_by(SampleID, Day, ExpDate) %>% 
summarize(SampleID, timeRound, Filename, Tube, Day, ExpDate, Run,  Strain, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par, meanOD680, meanOD720, meanActinic_parDay = mean(meanActinic_par), meanOD680Day = mean(meanOD680),  meanOD720Day = mean(meanOD720)) %>%
ungroup()

MultiCultiOD750Small <- MultiCultiOD750 %>%
  select(-c(timeRound, meanActinic_par, meanOD680, meanOD720)) %>% 
  unique()
```










